### 2022-02-17 paper/shabby.tex
add working code and rough draft without competition or clustering

% This is the TeX source for the Shabby Pages paper, using the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 from 2017/10/04

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\begin{document}

\title{Shabby Pages\thanks{Supported by Sparkfish LLC.}}

\author{Alexander Groleau\inst{1} \and
  Stefan Larson\inst{2}}

\institute{Sparkfish, Austin TX, USA\\
  \email{agroleau@sparkfish.com}\and
  SkySync, Ann Arbor MI, USA\\
  \email{slarson@skysync.com}}
\maketitle

\begin{abstract}
This paper presents the ‘ShabbyPages’ database, consisting of images of documents with realistic noise properties that result from standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings. We designed this corpus to help train and evaluate machine learning methods -- denoising, character recognition, and so on -- with text documents. The dataset is publicly available online, alongside scripts to reproduce the dataset.

\keywords{optical character recognition \and image processing \and denoising \and machine learning \and image degradation \and model training}
\end{abstract}

\section{Introduction}
Scholars generally agree that humans invented writing around 5500 years ago in Mesopotamia, what is now present-day Iraq. Unfortunately, we're still far from achieving full literacy globally, with 16 percent of adults still unable to read and write fluently ~\cite{ref_url1}. This situation is closely mirrored by developments in electronic language systems: we've been able to produce digital text for decades, but are only recently able to automatically read text back out of images of documents. Even now, this is not ubiquitous, with only carefully trained models able to do so under limited circumstances. \\

Inspired by the NoisyOffice dataset ~\cite{ref_url2}, we produced Shabby Pages as a way to help train, test, and calibrate computer vision machine learning algorithms designed for working with documents. We were particularly interested in producing a dataset more appropriate for training general denoising models, so we built and leveraged the Augraphy ~\cite{ref_url3} document image augmentation tool to produce noise for these images.

\section{Methodology}
The formation of the dataset occurred gradually, in stages. A team of researchers scoured the open internet for "born-digital" documents - PDFs that were created entirely electronically, rather than scans of existing printed documents. 600 documents were collected for review, representing categories such as government press releases, corporate financial communiques, informational brochures, and many others.\\

The \textit{pdftoppm} tool was used to separate each document into its constituent pages, converting these to PNGs in the process.

\begin{lstlisting}
  ls | grep pdf | time parallel pdftoppm {} 600dpi/{} -png -r 600
\end{lstlisting}

took 15 minutes and 7 seconds to process 6175 pages on a Ryzen 9 5950x, with the 1200 DPI version taking 44 minutes 49 seconds.\\

From there, we used Python's \textit{cv2} library to convert each document's color channels to grayscale, and once color data was removed, we generated and applied an Augraphy pipeline. After augmenting the images, we fit each to a standard 8.5''x11'' Letter document at various DPI levels, cropping to fit where necessary. There were several possible resizing methods, but we opted to use one which simulates using a document scanner to capture an image. Code for all of these processes is available on GitHub.

\section{Shabby Pages - An Augraphy Project}
In our investigations, we came across precious few sources of ground-truthed document images. We're releasing this corpus and the code we used to produce it, to aid the research community in making more. Training denoising models requires a large quantity of noisy data and the original clean sources, and producing this is exactly what the Augraphy library was designed to facilitate. The Augraphy team has been hard at work for several months, improving the reliability, performance, and flexibility of the project, and we're proud that it's now mature enough to produce useful datasets.\\

Writing the augmentation pipeline was straightforward: we took the default Augraphy pipeline and parametrized all the augmentations within it, keeping the parameters at the top of a file for easy tuning. Supporting scripts were written to coordinate passing images through the Augraphy pipeline and saving them to new locations, deal with different image resolutions, and so on. It was then possible to reproduce the noising process, so a cycle of testing was conducted where we produced noised images from the pipeline, determined effects in the output we didn't want to include in the published set, and tweaked the pipeline accordingly. The Augraphy API enabled a tight feedback loop here, and made it possible to iteratively narrow in on the data we wanted.\\

The default pipeline has already been tuned over several months to produce realistic output, but the parameters required some careful tweaking to achieve the dataset we wanted. Even so, there wasn't a great deal of work to do here beyond fiddling with constants to add more sources of variation, and to reduce the probability of certain augmentations being applied together. Driving Augraphy is largely a matter of developing some heuristics for unacceptable data and then telling Augraphy how to avoid producing that, so this part was largely minor edits to the build script and re-running the rendering job -- a familiar workflow for practitioners and researchers in this field.\\

%% TODO Clustering
%% With the standardized images in hand, we used the Apricot submodular optimization tool (3. Apricot) to cluster the images by visual similarity, and then select representatives from each cluster. Armed with these, we determined a radius of similarity around each representative, outside of which documents would be eliminated from consideration. For each representative, we removed from the dataset all the documents that were more than 15% dissimilar. We then took the union of all the sets produced in this manner, which had the effect of removing interstitial noise images (images that are somewhere between the clusters) that complicate analysis.

%% * TODO Denoising Dirty Documents, Again
%% We were deeply inspired by the Kaggle competition "Denoising Dirty Documents" (5. Kaggle), where the NoisyOffice dataset was used, and wanted to try something similar with the Shabby Pages set. A competition was devised in which teams would use the Shabby Pages set to train a denoising model of their choice, which would then be tested on a set of images we reserved for this purpose.

\bibliographystyle{splncs04}

\begin{thebibliography}{8}

\bibitem{ref_url1}
  UNESCO News, \url{https://en.unesco.org/news/literacy-all-remains-elusive-goal-new-unesco-data-shows}. Last accessed 17 Feb 2022

\bibitem{ref_url2}
  UCI Machine Learning Repository, \url{https://archive.ics.uci.edu/ml/datasets/NoisyOffice}

\bibitem{ref_url3}
  Augraphy, An augmentation pipeline for rendering synthetic paper printing, faxing, scanning and copy machine processes, \url{https://github.com/sparkfish/augraphy}

\bibitem{ref_url4}
  Denoising Dirty Documents | Kaggle, \url{https://www.kaggle.com/c/denoising-dirty-documents}

\bibitem{ref_url5}
  DocCreator, \url{https://doc-creator.labri.fr}

\bibitem{ref_url6}
  Apricot, submodular optimization for machine learning, \url{https://github.com/jmschrei/apricot}

\end{thebibliography}
\end{document}

### 2022-02-17 build/build_multi.py

@@ -1,0 +1,31 @@
+import time
+import os
+import cv2
+
+from multiprocessing import Pool
+from crappify import gen_pipeline
+
+directories = ["150dpi", "300dpi", "600dpi", "1200dpi"]
+
+dir_files = dict()
+
+for imdir in directories:
+    dir_files[imdir] = sorted(os.listdir(imdir))
+
+for i in range(100):
+    pipeline = gen_pipeline()
+
+    output = str(i) + " "
+
+    for imdir in directories:
+        imname = dir_files[imdir][i]
+        img = cv2.imread(imdir + "/" + imname)
+        start = time.time()
+        crappified = pipeline.augment(img)["output"]
+        stop = time.time()
+        duration = stop - start
+        save_name = ("crappified/" + imdir + "/" + imname[:-4] + "-augraphy-" + imdir + ".png")
+        cv2.imwrite(save_name, crappified)
+        output += (imdir + ": " + str(duration) + " ")
+
+    print(output)

### 2022-02-17 build/build_single.py

@@ -1,0 +1,17 @@
+from shabbypipeline import get_pipeline
+
+files = random.sample(os.listdir(), 100)
+
+def shabbify(f):
+    if "png" in f:
+        img = cv2.imread(f)
+        pipeline = get_pipeline()
+        out_path = "out/" + f[:-4] + "-augraphy.png"
+        augmented = pipeline.augment(img)["output"]
+        # make it all grayscale again in case we used a paper texture
+        crappified = cv2.cvtColor(crappified, cv2.COLOR_BGR2GRAY)
+        cv2.imwrite(crappified_path, crappified)
+
+p = Pool(32)
+
+p.map(crappify, files)

### 2022-02-17 build/fit.py

@@ -1,0 +1,21 @@
+import os
+import cv2
+
+from multiprocessing import Pool
+from samplegenerator import SampleGenerator
+
+
+sg = SampleGenerator(150)
+
+files = os.listdir()
+
+def genfit(f):
+    if "png" in f:
+        img = cv2.imread(f)
+        fit = sg.fit(img)
+        filename = "fits/" + f[:-4] + "-fit.png"
+        cv2.imwrite(filename, fit)
+
+p = Pool(32)
+
+p.map(genfit, files)

### 2022-02-17 build/grayscale.py

@@ -1,0 +1,17 @@
+import cv2
+import os
+from multiprocessing import Pool
+
+def make_grayscale(filename):
+    if "png" in filename:
+        img = cv2.imread(filename)
+        gray = cv2.cvtColor(img, cv2.COLOR_BGR2GRAY)
+        save_name = f[:-4] + "-gray.png"
+        cv2.imwrite(save_name, gray)
+
+if __name__ = "__main__":
+    files = os.listdir()
+
+    p = Pool(32)
+
+    p.map(make_grayscale, files)

### 2022-02-17 build/samplegenerator.py

@@ -1,0 +1,42 @@
+import cv2
+import numpy as np
+
+class SampleGenerator():
+    """Given a target DPI, a SampleGenerator's `fit` method resizes or cuts
+    a given image to fit a Letter page of that resolution.
+    """
+
+    def __init__(self, DPI=150):
+        self.DPI = DPI
+        self.xres = int(self.DPI*8.5)
+        self.yres = int(self.DPI*11)
+
+    def fit(self, fg):
+        y,x,z = fg.shape
+
+        if x > self.xres or y > self.yres:
+            return self.crop_overlay(fg)
+        else:
+            return self.fit_overlay(fg)
+
+    def crop_overlay(self, fg):
+        y,x,z = fg.shape
+
+        if y > self.yres:
+            if x > self.xres:
+                return fg[0:self.yres, 0:self.xres]
+            else:
+                img = np.zeros(shape=(self.yres,self.xres,3))
+                img[0:self.yres,0:x] = fg[0:self.yres,0:x]
+                return img
+        else:
+            img = np.zeros(shape=(self.yres,self.xres,3))
+            img[0:y,0:self.xres] = fg[0:y,0:self.xres]
+            return img
+
+    def fit_overlay(self, fg):
+        y,x,z = fg.shape
+
+        scan = np.zeros(shape=(self.yres,self.xres,3))
+        scan[0:y, 0:x] = fg
+        return scan

### 2022-02-17 build/shabbypipeline.py

@@ -1,0 +1,309 @@
+from augraphy import *
+import os
+import random
+import cv2
+
+
+################################################################################
+# EXPRESSING VARIATION
+#
+# We can control the outputs of the pipeline by setting values here.
+################################################################################
+
+# Dithering.dither can be 'ordered' for ordered dithering or another string for floyd-steinberg dithering
+# Dithering.order determines the dimensions of the threshold map
+dithering_dither_type = random.choice(["ordered", "floyd-steinberg"])
+dithering_order = random.choice(range(1,10))
+
+# InkBleed.intensity_range is a tuple with bounds for bleed intensity to be selected from
+# InkBleed.color_range is a tuple with bounds for color noise
+# InkBleed.kernel_size determines the radius of the bleed effect
+# InkBleed.severity determines significance of bleed effect
+inkbleed_intensity_range = (0.1, 0.2)
+inkbleed_color_range = (0, 224)
+inkbleed_kernel_size = (5, 5)
+inkbleed_severity=(0.4, 0.6)
+
+# BleedThrough.intensity_range is a tuple with bounds for bleed intensity to be selected from
+# BleedThrough.color_range is a tuple with bounds for color noise
+# BleedThrough.ksize is a tuple of height/width pairs for sampling kernel size
+# BleedThrough.sigmaX is the standard deviation of the kernel along the x-axis
+# BleedThrough.alpha is the intensity of the bleeding effect, recommended 0.1-0.5
+# BleedThrough.offsets is a pair of x and y distances to shift the bleed with
+bleedthrough_intensity_range=(0.1, 0.2)
+bleedthrough_color_range=(0, 224)
+bleedthrough_ksize=(17, 17)
+bleedthrough_sigmaX=0
+bleedthrough_alpha=0.3
+bleedthrough_offsets=(10, 20)
+
+# Letterpress.n_samples is a tuple determining how many points to generate per cluster
+# Letterpress.n_clusters is a tuple determining how many clusters to generate
+# Letterpress.std_range is a pair of ints determining the std deviation range in each blob
+# Letterpress.value_range determines values that points in the blob are sampled from
+# Letterpress.value_threshold_range is the minimum pixel value to enable the effect (e.g. 128)
+# Letterpress.blur enables blur in the noise mask
+letterpress_n_samples=(100, 200)
+letterpress_n_clusters=(500, 1000)
+letterpress_std_range=(500, 500)
+letterpress_value_range=(200, 255)
+letterpress_value_threshold_range=(128, 128)
+letterpress_blur=1
+
[…]

### 2022-03-12 paper/shabby.tex
update references

@@
 
-From there, we used Python's \textit{cv2} library to convert each document's color channels to grayscale, and once color data was removed, we generated and applied an Augraphy pipeline.
+From there, we used Python's \textit{cv2} library ~\cite{ref_url4} to convert each document's color channels to grayscale, and once color data was removed, we generated and applied an Augraphy pipeline.
 After augmenting the images, we fit each to a standard 8.5''x11'' Letter document at various DPI levels, cropping to fit where necessary.
@@
 \bibitem{ref_url4}
-  Denoising Dirty Documents | Kaggle, \url{https://www.kaggle.com/c/denoising-dirty-documents}
+  OpenCV, \url{https://opencv.org}
+%% \bibitem{ref_url4}
+%%   Denoising Dirty Documents | Kaggle, \url{https://www.kaggle.com/c/denoising-dirty-documents}
 
-\bibitem{ref_url5}
-  DocCreator, \url{https://doc-creator.labri.fr}
+%% \bibitem{ref_url5}
+%%   DocCreator, \url{https://doc-creator.labri.fr}
 
-\bibitem{ref_url6}
-  Apricot, submodular optimization for machine learning, \url{https://github.com/jmschrei/apricot}
+%% \bibitem{ref_url6}
+%%   Apricot, submodular optimization for machine learning, \url{https://github.com/jmschrei/apricot}
 

### 2022-03-15 paper/shabby.tex
restylize as ShabbyPages, update tex source and pdf, add image

--- 2022-02-17 paper/shabby.tex
@@
-% This is the TeX source for the Shabby Pages paper, using the
+% This is the TeX source for the ShabbyPages paper, using the
 % LLNCS macro package for Springer Computer Science proceedings;
@@
 \usepackage{listings}
-\usepackage{color}
-
-\definecolor{dkgreen}{rgb}{0,0.6,0}
-\definecolor{gray}{rgb}{0.5,0.5,0.5}
-\definecolor{mauve}{rgb}{0.58,0,0.82}
-
-\lstset{frame=tb,
-  language=Java,
-  aboveskip=3mm,
-  belowskip=3mm,
+\usepackage{xcolor}
+\lstset{basicstyle=\ttfamily,
   showstringspaces=false,
-  columns=flexible,
-  basicstyle={\small\ttfamily},
-  numbers=none,
-  numberstyle=\tiny\color{gray},
-  keywordstyle=\color{blue},
-  commentstyle=\color{dkgreen},
-  stringstyle=\color{mauve},
-  breaklines=true,
-  breakatwhitespace=true,
-  tabsize=3
+  commentstyle=\color{red},
+  keywordstyle=\color{blue}
 }
@@
 
-\title{Shabby Pages\thanks{Supported by Sparkfish LLC.}}
+\title{ShabbyPages, a Robust Corpus for Training Document Image Models\thanks{Supported by Sparkfish LLC.}}
 
 \author{Alexander Groleau\inst{1} \and
-  Stefan Larson\inst{2}}
+  Stefan Larson\inst{2} \and
+  Kok Wei Chee\inst{3}}
 
-\institute{Sparkfish, Austin TX, USA\\
-  \email{agroleau@sparkfish.com}\and
+\institute{Sparkfish, Addison TX, USA\\\and
   SkySync, Ann Arbor MI, USA\\
-  \email{slarson@skysync.com}}
+  \and
+  \email{ck91wei@gmail.com}}
 \maketitle
@@
 \begin{abstract}
-This paper presents the ‘ShabbyPages’ database, consisting of images of documents with realistic noise properties that result from standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
+This paper presents the ‘ShabbyPages’ dataset, consisting of images of documents with realistic noise properties that result from standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
 We designed this corpus to help train and evaluate machine learning methods -- denoising, character recognition, and so on -- with text documents.
-The dataset is publicly available online, alongside scripts to reproduce the dataset.
+The dataset and scripts to reproduce it are available on GitHub.
+The dataset construction process is described, with attention paid to the decisions made.
 
-\keywords{optical character recognition \and image processing \and denoising \and machine learning \and image degradation \and model training}
+\keywords{optical character recognition \and image processing \and denoising}
 \end{abstract}
@@
 \section{Introduction}
-Scholars generally agree that humans invented writing around 5500 years ago in Mesopotamia, what is now present-day Iraq.
-Unfortunately, we're still far from achieving full literacy globally, with 16 percent of adults still unable to read and write fluently ~\cite{ref_url1}.
-This situation is closely mirrored by developments in electronic language systems: we've been able to produce digital text for decades, but are only recently able to automatically read text back out of images of documents.
-Even now, this is not ubiquitous, with only carefully trained models able to do so under limited circumstances.
-\\
+Inspired by the NoisyOffice dataset~\cite{ref_url1}, we produced ShabbyPages as a way to help train, test, and calibrate computer vision machine learning algorithms designed for working with documents.
+We observed several limitations to the NoisyOffice dataset (namely, lack of diversity in font sizes and noise augmentations, as well as a lack of tables, graphics, form lines, etc.).
+Therefore, we were particularly interested in producing a dataset more appropriate for training general denoising models, so we built and leveraged the Augraphy~\cite{ref_url2} document image augmentation tool to produce noise for these images.
+ShabbyPages consists of  clean-noisy document image pairs.
 
-Inspired by the NoisyOffice dataset ~\cite{ref_url2}, we produced Shabby Pages as a way to help train, test, and calibrate computer vision machine learning algorithms designed for working with documents.
-We were particularly interested in producing a dataset more appropriate for training general denoising models, so we built and leveraged the Augraphy ~\cite{ref_url3} document image augmentation tool to produce noise for these images.
-
-\section{Methodology}
-The formation of the dataset occurred gradually, in stages.
-A team of researchers scoured the open internet for "born-digital" documents - PDFs that were created entirely electronically, rather than scans of existing printed documents.
+\section{Creation}
+Development of the dataset occurred in stages.
+A team of researchers scoured the open internet for ``born-digital" documents - PDFs that were created entirely electronically, rather than scans of existing printed documents.
 600 documents were collected for review, representing categories such as government press releases, corporate financial communiques, informational brochures, and many others.\\
 
-The \textit{pdftoppm} tool was used to separate each document into its constituent pages, converting these to PNGs in the process.
+The \textit{pdftoppm} tool was used to separate each document into its constituent pages, converting these to PNGs in the process, using GNU Parallel ~\cite{ref_parallel} to distribute the job across all available cores.
+\texttt{parallel pdftoppm pdfs/{} pages/{} -png -r 150} took 2 minutes to process 6202 pages on a Ryzen 9 5950x.\\
 
-\begin{lstlisting}
-  ls | grep pdf | time parallel pdftoppm {} 600dpi/{} -png -r 600
-\end{lstlisting}
-
-took 15 minutes and 7 seconds to process 6175 pages on a Ryzen 9 5950x, with the 1200 DPI version taking 44 minutes 49 seconds.\\
-
-From there, we used Python's \textit{cv2} library to convert each document's color channels to grayscale, and once color data was removed, we generated and applied an Augraphy pipeline.
+From there, we used Python's \textit{cv2} library ~\cite{ref_url3} to convert each document's color channels to grayscale, and once color data was removed, we generated and applied an Augraphy pipeline.
 After augmenting the images, we fit each to a standard 8.5''x11'' Letter document at various DPI levels, cropping to fit where necessary.
 There were several possible resizing methods, but we opted to use one which simulates using a document scanner to capture an image.
-Code for all of these processes is available on GitHub.
+Code for all of these processes is available on GitHub~\cite{ref_shabby}.
 
-\section{Shabby Pages - An Augraphy Project}
+\section{ShabbyPages - An Augraphy Project}
 In our investigations, we came across precious few sources of ground-truthed document images.
-We're releasing this corpus and the code we used to produce it, to aid the research community in making more.
+To aid the research community in making more, we're releasing this corpus and the code we used to produce it.
 Training denoising models requires a large quantity of noisy data and the original clean sources, and producing this is exactly what the Augraphy library was designed to facilitate.
@@
 
-Writing the augmentation pipeline was straightforward: we took the default Augraphy pipeline and parametrized all the augmentations within it, keeping the parameters at the top of a file for easy tuning.
-Supporting scripts were written to coordinate passing images through the Augraphy pipeline and saving them to new locations, deal with different image resolutions, and so on.
-It was then possible to reproduce the noising process, so a cycle of testing was conducted where we produced noised images from the pipeline, determined effects in the output we didn't want to include in the published set, and tweaked the pipeline accordingly.
-The Augraphy API enabled a tight feedback loop here, and made it possible to iteratively narrow in on the data we wanted.\\
+Building the augmentation pipeline was straightforward: we took the default Augraphy pipeline and parametrized all the augmentations within it, keeping the parameters at the top of a file for easy adjustment.
+Supporting scripts were written to coordinate passing images through the Augraphy pipeline and saving them to new locations, dealing with different image resolutions, and so on.
+It was then possible to reproduce the noising process, so a cycle of testing was conducted where we generated noised images from the pipeline, determined properties of the output we didn't want to include in a published set, and accordingly tweaked the pipeline to no longer produce those effects.
+We wanted the ShabbyPages corpus to serve multiple functions -- denoising, OCR, and so on -- which constrained the degree of variation tolerated in the generating code.\\
 
-The default pipeline has already been tuned over several months to produce realistic output, but the parameters required some careful tweaking to achieve the dataset we wanted.
-Even so, there wasn't a great deal of work to do here beyond fiddling with constants to add more sources of variation, and to reduce the probability of certain augmentations being applied together.
-Driving Augraphy is largely a matter of developing some heuristics for unacceptable data and then telling Augraphy how to avoid producing that, so this part was largely minor edits to the build script and re-running the rendering job -- a familiar workflow for practitioners and researchers in this field.\\
+Two primary classes of modifications to this code were considered, corresponding to a change in input constants and a restriction on certain combinations of augmentations.
+The Augraphy API enabled a tight feedback loop here, and made it possible to iteratively narrow in on a pipeline that generated the data we wanted.
+Driving Augraphy is largely a matter of developing some heuristics for unacceptable data and then telling Augraphy how to avoid producing that.
+This enables a workflow familiar to practitioners and researchers in this field, where edits are made to a build script and the rendering job is run, in a cycle.
 
-%% TODO Clustering
-%% With the standardized images in hand, we used the Apricot submodular optimization tool (3.
-Apricot) to cluster the images by visual similarity, and then select representatives from each cluster.
-Armed with these, we determined a radius of similarity around each representative, outside of which documents would be eliminated from consideration.
-For each representative, we removed from the dataset all the documents that were more than 15% dissimilar.
-We then took the union of all the sets produced in this manner, which had the effect of removing interstitial noise images (images that are somewhere between the clusters) that complicate analysis.
+\section{Tuning the Pipeline}
+The default augmentation pipeline has already been tuned to produce realistic output, but the parameters required some careful tweaking to achieve our goals.
+Even so, there wasn't a great deal of work to do here beyond fiddling with constants to add or remove sources of variation, and to reduce the probability of certain augmentations being applied together.\\
 
-%% * TODO Denoising Dirty Documents, Again
-%% We were deeply inspired by the Kaggle competition "Denoising Dirty Documents" (5.
-Kaggle), where the NoisyOffice dataset was used, and wanted to try something similar with the Shabby Pages set.
-A competition was devised in which teams would use the Shabby Pages set to train a denoising model of their choice, which would then be tested on a set of images we reserved for this purpose.
+Each augmentation in the Augraphy library was designed to reliably produce a specific effect on a document image, but care must be taken to ensure the effect is appropriate to the intended use.
+We intend for the first release of the ShabbyPages set to see use in training denoising models, so augmentation effects that make text impossible to read were rejected.
+Over a period of several weeks, we adjusted inputs to bring augmentations into the Goldilocks zone: not too heavy, not too noisy, just right.
+As an example, here's part of the diff between pipelines built on successive days:
+
+\noindent\fbox{\begin{minipage}{\textwidth}
+{\color{red}{$\leftarrow$ bleedthrough\_intensity\_range=(0.1, 0.2)}}
+
+{\color{blue}{$\rightarrow$   bleedthrough\_intensity\_range=(0.05, 0.15)}}\\
+
+{\color{red}{$\leftarrow$ bleedthrough\_color\_range=(0, 224)}}
+
+{\color{blue}{$\rightarrow$ bleedthrough\_color\_range=(32, 224)}}\\
+
+{\color{red}{$\leftarrow$ bleedthrough\_alpha=random.uniform(0.1,0.2)}}
+
+{\color{blue}{$\rightarrow$    bleedthrough\_alpha=random.uniform(0.05,0.1)}}
+\end{minipage}}
+\hspace{1cm}\\\\
+\indent Augmentations in the Augraphy project are designed to produce changes mimicking those resulting from real-world processing of documents.
+A diverse array of effects are possible, including the incomplete deposit of ink on paper by a stamp or typeblock, staining on the page from a dirty print drum, the reduction in quality and artifacts introduced by faxing, and the shadow produced when scanning a book of a page curling away towards the binding.
+Several of these transformations are pairwise mutually incompatible, depending on the intended outcomes of the produced documents, and determining these pairs is a large part of the process when using Augraphy.\\
+
+Here are a few bad pairings we found:
+
+\begin{itemize}
+\item BadPhotoCopy turns transparent clusters of noise into opaque black patches, and cannot be used with DirtyDrum.
+\item Bleedthrough can produce large dark regions which Letterpress interprets as text, applying unnatural blobs of noise.
+\item The combination of dithering, thresholding, and Gaussian noise makes BadPhotoCopy and Faxify destructively interact to produce unreadable text.
+\end{itemize}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{beforeafter.png}
+    \caption{Example input image (left) and Augraphy-augmented output (right).}
+    \label{fig:3panel}
+\end{figure}
+
+\section{Conclusion}
+Compilation and production of a collection of realistically noised document images with the Augraphy tool was straightforward.
+The resulting dataset contains a much broader variety of noise types, font sizes, document formats, and languages than the NoisyOffice set, and the initial release is publicly available for use in denoising, recognition, and classification tasks.
+Scripts to facilitate dataset production with Augraphy are published on GitHub, and both these scripts and the Augraphy project itself are being actively developed.
 
@@
 \bibitem{ref_url1}
-  UNESCO News, \url{https://en.unesco.org/news/literacy-all-remains-elusive-goal-new-unesco-data-shows}. Last accessed 17 Feb 2022
+  UCI Machine Learning Repository, \url{https://archive.ics.uci.edu/ml/datasets/NoisyOffice}
 
 \bibitem{ref_url2}
-  UCI Machine Learning Repository, \url{https://archive.ics.uci.edu/ml/datasets/NoisyOffice}
+  Augraphy, An augmentation pipeline for rendering synthetic paper printing, faxing, scanning and copy machine processes, \url{https://github.com/sparkfish/augraphy}
 
 \bibitem{ref_url3}
-  Augraphy, An augmentation pipeline for rendering synthetic paper printing, faxing, scanning and copy machine processes, \url{https://github.com/sparkfish/augraphy}
+  OpenCV, \url{https://opencv.org}
 
-\bibitem{ref_url4}
-  Denoising Dirty Documents | Kaggle, \url{https://www.kaggle.com/c/denoising-dirty-documents}
+\bibitem{ref_parallel}
+  Tange, O. (2021, July 22). GNU Parallel 20210722 ('Blue Unity').
+  Zenodo. https://doi.org/10.5281/zenodo.5123056
 
-\bibitem{ref_url5}
-  DocCreator, \url{https://doc-creator.labri.fr}
-
-\bibitem{ref_url6}
-  Apricot, submodular optimization for machine learning, \url{https://github.com/jmschrei/apricot}
-
+\bibitem{ref_shabby}
+ShabbyPages, \url{https://github.com/sparkfish/shabby-pages}
 \end{thebibliography}

### 2022-04-07 paper/shabby.tex
add author running header
update references

@@
 
+\authorrunning{A. Groleau et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
 \institute{Sparkfish, Addison TX, USA\\\and
@@
 \section{Introduction}
-Inspired by the NoisyOffice dataset~\cite{ref_url1}, we produced ShabbyPages as a way to help train, test, and calibrate computer vision machine learning algorithms designed for working with documents.
+Inspired by the NoisyOffice dataset~\cite{ref_noisy}, we produced ShabbyPages as a way to help train, test, and calibrate computer vision machine learning algorithms designed for working with documents.
 We observed several limitations to the NoisyOffice dataset (namely, lack of diversity in font sizes and noise augmentations, as well as a lack of tables, graphics, form lines, etc.).
-Therefore, we were particularly interested in producing a dataset more appropriate for training general denoising models, so we built and leveraged the Augraphy~\cite{ref_url2} document image augmentation tool to produce noise for these images.
+Therefore, we were particularly interested in producing a dataset more appropriate for training general denoising models, so we built and leveraged the Augraphy~\cite{ref_augraphy} document image augmentation tool to produce noise for these images.
 ShabbyPages consists of  clean-noisy document image pairs.
@@
 
-The \textit{pdftoppm} tool was used to separate each document into its constituent pages, converting these to PNGs in the process, using GNU Parallel ~\cite{ref_parallel} to distribute the job across all available cores.
+The \textit{pdftoppm} tool was used to separate each document into its constituent pages, converting these to PNGs in the process, using GNU Parallel~\cite{ref_parallel} to distribute the job across all available cores.
 \texttt{parallel pdftoppm pdfs/{} pages/{} -png -r 150} took 2 minutes to process 6202 pages on a Ryzen 9 5950x.\\
 
-From there, we used Python's \textit{cv2} library ~\cite{ref_url3} to convert each document's color channels to grayscale, and once color data was removed, we generated and applied an Augraphy pipeline.
+From there, we used Python's \textit{cv2} library~\cite{ref_opencv} to convert each document's color channels to grayscale, and once color data was removed, we generated and applied an Augraphy pipeline.
 After augmenting the images, we fit each to a standard 8.5''x11'' Letter document at various DPI levels, cropping to fit where necessary.
@@
 
-\begin{thebibliography}{8}
-
-\bibitem{ref_url1}
+\begin{thebibliography}{5}
+\bibitem{ref_noisy}
   UCI Machine Learning Repository, \url{https://archive.ics.uci.edu/ml/datasets/NoisyOffice}
 
-\bibitem{ref_url2}
+\bibitem{ref_augraphy}
   Augraphy, An augmentation pipeline for rendering synthetic paper printing, faxing, scanning and copy machine processes, \url{https://github.com/sparkfish/augraphy}
-
-\bibitem{ref_url3}
-  OpenCV, \url{https://opencv.org}
 
@@
 
+\bibitem{ref_opencv}
+  OpenCV, \url{https://opencv.org}
+
 \bibitem{ref_shabby}

### 2023-01-12 paper.tex
move to latex source, substantial updates

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\renewcommand{\floatpagefraction}{.8}
%
\begin{document}

\title{ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images}
\author{Alexander Groleau\inst{1,2} \and
  Kok Wei Chee\inst{1} \and
  Jonathan Boarman\inst{1} \and
  Samay Maini\inst{1}}

\authorrunning{A. Groleau et al.}

\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
  \and
  Left Associates LLC (\email{research@left.associates})}

\maketitle

\begin{abstract}
The ShabbyPages document image dataset is produced using the Augraphy document image augmentation tool. The development of the computation pipeline used to generate the corpus is discussed, and the results presented. The final corpus contains over 6000 "born-digital" ground truth document images, sourced on the Web, with synthetically-noised counterparts (``shabby pages'') that appear to have been printed and faxed, photocopied, or otherwise altered through physical processes. The release of this dataset and the recipe for its production attempts to address a growing need for labeled training document images for supervised learning tasks. The results of several experiments are discussed, in which the corpus trains performant convolutional denoisers, which remove real noise features with a high degree of human-perceptible fidelity, establishing baseline performance for a new ShabbyPages benchmark.
\end{abstract}

\section{Introduction}
Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, ree of noise or other degradations. ShabbyPages is a large dataset composed of 6153 clean/noisy pairs of images taken from 600 digital documents. Information about the set's contents and its relation to other datasets are explored in the next section. The noisy images were created from their clean origins by the application of a pipeline developed with the Augraphy library; the production of ShabbyPages is detailed in the third section, with all source code and input materials made openly available. The final dataset is used to train several denoising models which are compared directly and whose prediction results are compared together in the final section.

\section{The Dataset}
ShabbyPages joins a rapidly growing number of open-source datasets freely available online. Human activity today generates a tremendous amount of data, with many people choosing to publish theirs on websites like Kaggle \cite{ref_Kaggle}, Hugging Face Hub \cite{ref_HuggingFaceHub}, and many more. All of this data is arranged into categories: sets exist which contain text, images, audio, and data from other modalities, with each set often collected and designed for a purpose. Of the many image datasets available, the authors understand few to have been designed for groundtruthed supervised learning of document-specific tasks like binarization or denoising. In fact, we could find only one other set compiled for doing so with images of \textit{modern} documents: NoisyOffice \cite{ref_NoisyOffice}.

\begin{figure}
\includegraphics[width=\textwidth]{Article_Hero_Picture_Shadow.png}
\caption{Example ShabbyPages image, with the groundtruth partially augmented on the right.} \label{fig1}
\end{figure}

\subsection{Features}
Modern artificial neural networks produce a latent representation of their training data, a space from which outputs are sampled. In deep networks, these representations live within multiple layers, each of which corresponds to a feature of the input data. Document images are a particularly interesting category, as the data within the documents each picture represents is itself frequently multi-modal; the document may contain an image and its description, a table with statistics, multiple regions of structured and formatted text, and even other documents.\\

Table 1 below contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.

\begin{table}
\centering
\caption{Document Image Dataset Feature Comparison}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Feature & ShabbyPages & NoisyOffice & RVL-CDIP & Tobacco800 \\
\hline
Images & 6153 & 72 & 400000 & 1290\\
Document-specific & Yes & Yes & Yes & Yes\\
Synthetic & Yes & Yes & No & No\\
Groundtruthed? & Yes & Yes & No & No\\
Font size & Multiple & 16pt & Multiple & Multiple\\
Paper styles & Multiple & 1 & Multiple & Multiple\\
Multilingual & Yes & No & No & No\\
Documents contain images? & Yes & No & Yes & Yes\\
Pre-categorized & No & No & Yes & Yes\\
\hline
\end{tabular}
\end{table}

\subsubsection{NoisyOffice}
The NoisyOffice database \cite{ref_NoisyOffice} contains a very low 4 base images, 2 types of font, 3 font sizes, and 4 types of noise, for a total of 72 unique images. The groundtruth images were produced in a standard word processor, with the simulated noisy images produced by first adding noise to a blank sheet of paper, storing that as a background image after digital scanning, then overlaying the foreground text onto the noisy background texture. An additional set of real NoisyOffice images was produced, where the foreground text was printed on blank white sheets, the results of which were physically augmented by the introduction of footprints, coffee stains, wrinkles, and folds.\\

ShabbyPages began with 600 documents sourced from the Internet from culturally-important sources. A manifest is included in the dataset which contains an ordered table of the filenames, the languages present in the document, the download URL for the file, and an English name or acronym for the source organization or person. These documents were split into their constituent pages, which were then passed through an Augraphy pipeline we tuned over a month or two. This tuning amounted to tweaking numerical parameters for each of the 24 different augmentations from the Augraphy library. All or none of these may have applied to each input image, and only one pipeline run was completed per image. Each augmentation has a high degree of internal variability due to several calls to a pseudorandom number generator on which several transforms depend. The conjunction of all these factors implies ShabbyPages is a sample from a massive space. Indeed, the cosine similarity computed over OpenAI's CLIP representations of each output image averages to 0.49, much higher than NoisyOffice's 0.31. Augraphy does not yet have augmentations for footprints or coffee stains, so the dark regions and edges of the stains and prints were simulated with features introduced by other augmentations, but Augraphy does contain the PaperFactory transformation which selects and crops a texture from a local directory of paper images. The result of a PaperFactory application is the foreground text ``printed'' onto the background texture, similar to NoisyOffice's construction.

\subsection{RVL-CDIP}
The RVL-CDIP dataset \cite{ref_RVL-CDIP} consists of 400,000 grayscale images divided into 16 document classes, each with a similar number of elements. The dataset is pre-segmented into 320,000 training, 40,000 test, and 40,000 validation images, facilitating immediate use in machine learning applications. The classes represented are the following:

\begin{center}
letter, form, email, handwritten, advertisement, scientific report,
scientific publication, specification, file folder, news article,
budget, invoice, presentation, questionnaire, resume, memo.
\end{center}

The images exhibit poor fidelity with what we can imagine their originals to have been, contain substantial noise, and many were scanned at around 100 pixels per inch, quite a low resolution for documents. None of the images in the CDIP set come with groundtruths.\\

The collection of RVL-CDIP is an impressive feat in its own right: nearly half a million scanned documents with real noise, already categorized. Augraphy makes synthetic documents, intended to simulate real noise without the need to physically produce it. One of the augmentations used in the ShabbyPages set is BadPhotoCopy, which mimics low-fidelity noisy or damaged scans.

\subsection{Tobacco800}
Tobacco800, like RVL-CDIP, is a subset of the Complex Document Image Processing collection, containing images of documents originally internal to tobacco companies, and released under the Tobacco Master Settlement Agreement. The corpus is composed of 1290 images, gathered and scanned at different times and by different devices. Several of the images in this set are consecutively-numbered pages, increasing the set's utility for certain image analysis tasks \cite{ref_Tobacco800}. Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.

\subsection{Statistics}
ShabbyPages contains documents from multiple classes, which contain many types of information.

Table 2 below contains some statistics for the dataset, in grayscale, at a standard resolution of 150 ppi.

\begin{table}
\centering
\caption{ShabbyPages Statistics}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Statistic & Value \\
\hline
Images & 6153 \\
DPI & 150 \\
Max image size & \_ \\
\hline
\end{tabular}
\end{table}

\subsection{Limitations}
The ShabbyPages collection is a comprehensive entrant to the public datasphere, but with a relatively low starting document volume, makes some important omissions.

First, we arbitrarily selected 600 as the number of source documents. The number of final images of pages depends on this, and so is similarly arbitrary.

There are only a few languages represented, which reflects a number of biases, including the following:
\begin{itemize}
\item The native languages of the document-searchers
\item The locations from which the document-searchers searched
\item The search techniques used by each document-searcher
\end{itemize}

This work does not account for them, but these biases are significant determiners on the set of input documents. We hoped to overcome this somewhat by picking a suitably large number of input documents, and settled at 600.

\section{Motivation for Denoising}
TODO

\section{Construction}
This section describes the dataset generation methodology; code for all of this is available on GitHub.

\subsection{Data Gathering}
A team of workers searched the public internet for PDFs of many different kinds. 600 unique documents were retrieved, totaling 6153 pages. A similar process was completed to collect paper textures on which to "print" the documents: 300 unique textures were gathered, all of which are either in the public domain or carry CC-0, CC-BY, or CC-BY-SA licenses. Care was taken to retrieve freely-available and attributable documents; a CSV file containing document and paper texture links (as of time of download), with their sources, is available and distributed with the dataset. We also manually reviewed the gathered documents to verify that no personal identity information was present within the corpus.

\subsection{PDF to PNG}
The ~pdftoppm~ tool from the ~poppler-utils~ package was used to split the PDF documents into individual pages. Each page was converted to a PNG image at 150dpi, a common printing resolution. Because the majority of these documents were created with the standard US Letter dimensions, this resulted in the most common image dimension being 1275 pixels wide by 1650 pixels tall.

\begin{lstlisting}[language=bash]
  pdftoppm document_name.pdf document_name -png -r 150
\end{lstlisting}

\subsection{Developing the Pipeline}
The Augraphy library presents an easy-to-use API for constructing feature pipelines, which has been designed for interoperability with other augmentation tools, and within the broader data ecosystem. While Augraphy's default pipeline has what we believe to be quite realistic defaults, we wanted a broader range of features from this dataset than those the default pipeline could produce. To address this, we broke all of the parameters for every augmentation constructor out into separate variables, tweaking these and committing the new pipeline to GitHub. We created an automated daily build in GitHub Actions to render a random selection of ground-truth images with the updated pipeline, then our team met frequently to discuss the output and make adjustments to the pipeline.

\subsection{Processing Augraphy on a multicore system}
Execution time is dependent on which augmentations are executed at runtime; an Augraphy pipeline can take several seconds to process large images. The library is under active development with performance enhancements underway, but the time cost to generate large datasets sequentially is prohibitive when dealing with thousands of files, so we use a multi-process pooling technique to distribute the workload across many processor execution threads. For each process, we generate a new pipeline, run the pipeline object on an image, and save the output, using the code below:

\begin{lstlisting}[language=Python]
    import os
    import cv2
    from multiprocessing import Pool
    from pathlib import Path

    input_path = Path("/path/to/input/images")
    filenames = [(input_path / name) for name in os.listdir(input_path)]

    pool = Pool(os.cpu_count())

    def run_pipeline(filename):
        image = cv2.imread(filename)
        pipeline = get_pipeline() # returns the current Shabby Pages pipeline
        data = pipeline.augment(image)
        shabby_image = data["output"]
        cv2.imwrite(filename.parent / f"{filename.stem}-shabby{filename.suffix}")

    pool.map(run_pipeline, filenames)

\end{lstlisting}

Processing all 6153 images took TODO:TIME on the 64 cores of a Graviton3 c7g.16xlarge instance on AWS.

\section{Experimentation with the ShabbyPages Set}
Binarization and denoising are two important techniques for the removal of unwanted data from images. Both approaches can be achieved by supervised learning of relationships between features of the input and output data. In this section, we train and compare several denoising models and their predictions on both the NoisyOffice and ShabbyPages datasets.

\

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_Kaggle}
  https://www.kaggle.com/datasets
\bibitem{ref_HuggingFaceHub}
  {https://huggingface.co/datasets}
\bibitem{ref_RDCL2019}
{Christian Clausner, RDCL2019 Competition Dataset (Recognition of Documents with Complex Layouts) (RDCL2019) ,1,ID:RDCL2019\_1,URL:https://tc11.cvc.uab.es/datasets/RDCL2019_1}

\bibitem{ref_Tobacco800}
{David Doermann, Tobacco 800 Dataset (Tobacco800) ,1,ID:Tobacco800_1,URL:https://tc11.cvc.uab.es/datasets/Tobacco800_1}

\bibitem{ref_icdar}
{Harold Mouchère, ICDAR 2019 Competition on Recognition of Handwritten Mathematical Expressions and Typeset Formula Detection (ICDAR2019-CROHME-TDF) ,1,ID:ICDAR2019-CROHME-TDF\_1,URL:https://tc11.cvc.uab.es/datasets/ICDAR2019-CROHME-TDF_1}

\bibitem{ref_NoisyOffice}
{Castro-Bleda, MJ.; España Boquera, S.; Pastor Pellicer, J.; Zamora Martínez, FJ. (2020). The NoisyOffice Database: A Corpus To Train Supervised Machine Learning Filters For Image Processing. The Computer Journal. 63(11):1658-1667. https://doi.org/10.1093/comjnl/bxz098}

\bibitem{ref_RVL-CDIP}
  @article{DBLP:journals/corr/HarleyUD15,
  author    = {Adam W. Harley and
               Alex Ufkes and
               Konstantinos G. Derpanis},
  title     = {Evaluation of Deep Convolutional Nets for Document Image Classification
               and Retrieval},
  journal   = {CoRR},
  volume    = {abs/1502.07058},
  year      = {2015},
  url       = {http://arxiv.org/abs/1502.07058},
  eprinttype = {arXiv},
  eprint    = {1502.07058},
  timestamp = {Mon, 13 Aug 2018 16:48:54 +0200},
  biburl    = {https://dblp.org/rec/journals/corr/HarleyUD15.bib},
  bibsource = {dblp computer science bibliography, https://dblp.org}
}

\bibitem{ref_NoisyOfficeDatabase}
{F. Zamora-Martinez, S. España-Boquera and M. J. Castro-Bleda, Behaviour-based Clustering of Neural Networks applied to Document Enhancement, in: Computational and Ambient Intelligence, pages 144-151, Springer, 2007.}

\bibitem{ref_UCIMLR}
{Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.}

\bibitem{ref_DocCreator}
  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
\bibitem{ref_fastai}
\end{thebibliography}
\end{document}

### 2023-01-12 paper.tex
more additions about features and dataset comparisons

@@
   Kok Wei Chee\inst{1} \and
+  Stefan Larson\inst{3} \and
   Jonathan Boarman\inst{1} \and
@@
   \and
-  Left Associates LLC (\email{research@left.associates})}
+  Left Associates LLC (\email{research@left.associates})
+  \and
+  Vanderbilt University}
 
@@
 \section{Introduction}
-Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, ree of noise or other degradations.
-ShabbyPages is a large dataset composed of 6153 clean/noisy pairs of images taken from 600 digital documents.
+Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, free of noise or other degradations.
+ShabbyPages is a large dataset composed of 6202 clean/noisy pairs of images taken from 600 digital documents.
 Information about the set's contents and its relation to other datasets are explored in the next section.
@@
 \includegraphics[width=\textwidth]{Article_Hero_Picture_Shadow.png}
-\caption{Example ShabbyPages image, with the groundtruth partially augmented on the right.} \label{fig1}
+\caption{Example ShabbyPages image, before and after augmentation.} \label{fig1}
 \end{figure}
@@
 In deep networks, these representations live within multiple layers, each of which corresponds to a feature of the input data.
-Document images are a particularly interesting category, as the data within the documents each picture represents is itself frequently multi-modal; the document may contain an image and its description, a table with statistics, multiple regions of structured and formatted text, and even other documents.\\
+Document images are a particularly interesting category, as the data within the documents each picture represents is itself frequently multi-modal; the document may contain an image and its description, a table with statistics, multiple regions of structured and formatted text, and even other documents, making their internal representations by neural networks often quite complicated.\\
 
-Table 1 below contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.
+Networks with a wider variety of latent representations frequently perform better when generalizing their learned functions to other tasks.
+Procuring a large-enough volume of robust-enough training data is paramount.
+Several sets of such images exist, many intended for processing by deep neural nets; Table 1 below contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.\\
 
@@
 \caption{Document Image Dataset Feature Comparison}\label{tab1}
-\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
+\begin{tabular}{|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|}
 \hline
@@
 \hline
-Images & 6153 & 72 & 400000 & 1290\\
+Images & 6202 & 72 & 400000 & 1290\\
 Document-specific & Yes & Yes & Yes & Yes\\
@@
 Several of the images in this set are consecutively-numbered pages, increasing the set's utility for certain image analysis tasks \cite{ref_Tobacco800}.
-Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.
+Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.\\
+
+Every document in the ShabbyPages groundtruth set is a multi-page document.
+The released set was exported at 150 DPI, but the original documents are also distributed, so re-exporting at a higher resolution is trivial.
+The smallest image is 532 by 532, with the largest 3336 wide by 12157 tall.
+6202 images are present in ShabbyPages, but this number could easily be increased by simply running another Augraphy pipeline to generate more.
+
+\subsection{ShabbyPages Compared}
+Supervised learning tasks require labeled training data, called the ground truth.
+Much of the world's data does not come with labels, which instead must be created by humans in some fashion.
+In Table 1, we indicated that NoisyOffice was the only other groundtruthed dataset we examined.
+This isn't strictly true: there are projects to add some types of groundtruth to RVL-CDIP \cite{ref_goldmann}, \cite{ref_zenodo} and Tobacco800 \cite{ref_tobacco800gt1}, \cite{ref_tobacco800gt2}, but the images in these sets were produced by real scans, without an accompanying original digital document.
+Conversely, NoisyOffice contains images of real scanned documents intended for validation, as well as their digital groundtruth and synthetic training image data.\\
+
+ShabbyPages includes not only the groundtruth images, but also the original digital documents used to produce them, and the software for fully reproducing the ShabbyPages set, allowing anyone to quickly produce a new set in the Shabby family, optionally re-exporting groundtruths at a different resolution beforehand.
+The 6202 images in the ShabbyPages release set are really just the first sample from the space of these documents; we encourage building your own.
+NoisyOffice is the only other set we examined that contains its digital provenance, but the released database materials lack a means of reproducing the simulated printing method used to create the NoisyOffice training data.
+Augraphy's PaperFactory augmentation is such a tool.
+The other sets are not even theoretically extensible in this way.
 
 \subsection{Statistics}
-ShabbyPages contains documents from multiple classes, which contain many types of information.
+ShabbyPages contains documents from multiple classes, which contain many types of information.\\
 
@@
 \hline
-Images & 6153 \\
+Images & 6202 \\
 DPI & 150 \\
@@
 \subsection{Limitations}
-The ShabbyPages collection is a comprehensive entrant to the public datasphere, but with a relatively low starting document volume, makes some important omissions.
+The ShabbyPages collection is a comprehensive entrant to the public datasphere, but with a relatively low starting document volume, makes some important omissions.\\
 
-First, we arbitrarily selected 600 as the number of source documents. The number of final images of pages depends on this, and so is similarly arbitrary.
+First, we arbitrarily selected 600 as the number of source documents. The number of final images of pages depends on this, and so is similarly arbitrary.\\
 
@@
 
-\section{Motivation for Denoising}
-TODO
-
 \section{Construction}
@@
 A team of workers searched the public internet for PDFs of many different kinds.
-600 unique documents were retrieved, totaling 6153 pages.
+600 unique documents were retrieved, totaling 6202 pages.
 A similar process was completed to collect paper textures on which to "print" the documents: 300 unique textures were gathered, all of which are either in the public domain or carry CC-0, CC-BY, or CC-BY-SA licenses.
@@
 
-Processing all 6153 images took TODO:TIME on the 64 cores of a Graviton3 c7g.16xlarge instance on AWS.
+Processing all 6202 images took TODO:TIME on the 64 cores of a Graviton3 c7g.16xlarge instance on AWS.
 
@@
 
-\
+\section{Motivation for Denoising}
+Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it.
+Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, or when our aesthetic sensibilities aren't injured.\\
 
@@
   {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
-\bibitem{ref_fastai}
+\bibitem{ref_goldmann}
+  {Pau Riba, Anjan Dutta, Lutz Goldmann, Alicia Fornes, Oriol Ramos, Josep LLados: "Table Detection in Invoice Documents by Graph Neural Networks", ICDAR, 2019.}
+\bibitem{ref_zenodo}
+  {Layout Analysis Groundtruth for the RVL-CDIP Dataset. Goldmann, Lutz. 10.5281/zenodo.3257319}
+\bibitem{ref_tobacco800gt1}
+  {Guangyu Zhu, Yefeng Zheng, David Doermann,and Stefan Jaeger.
+Multi-scale Structural Saliency for Signature Detection.
+In Proc.
+IEEE Conf.
+Computer Vision and Pattern Recognition (CVPR 2007), pp.
+1‐8, 2007.}
+\bibitem{ref_tobacco800gt2}
+  {Guangyu Zhu and David Doermann. Automatic Document Logo Detection. In Proc. 9th Int. Conf. Document Analysis and Recognition (ICDAR 2007), pp. 864‐868, 2007.}
+
 \end{thebibliography}

### 2023-01-23 paper/paper.tex
add binarization results and move to subdir

--- 2023-01-12 paper.tex
@@
     input_path = Path("/path/to/input/images")
-    filenames = [(input_path / name) for name in os.listdir(input_path)]
+    filenames = [(input_path / name)
+      for name
+      in os.listdir(input_path)]
 
@@
         image = cv2.imread(filename)
-        pipeline = get_pipeline() # returns the current Shabby Pages pipeline
+        # returns the current Shabby Pages pipeline
+        pipeline = get_pipeline()
         data = pipeline.augment(image)
@@
 
-Processing all 6202 images took TODO:TIME on the 64 cores of a Graviton3 c7g.16xlarge instance on AWS.
+Processing all 6202 images took less than half an hour on the 64 cores of a Graviton3 c7g.16xlarge instance on AWS.
 
@@
 Both approaches can be achieved by supervised learning of relationships between features of the input and output data.
-In this section, we train and compare several denoising models and their predictions on both the NoisyOffice and ShabbyPages datasets.
+In this section, we train and compare several instances of the NAFNet \cite{ref_NAFNet} architecture as denoisers and binarizers, and evaluate these models' predictions on both the NoisyOffice and ShabbyPages datasets.
+The model was ``off-the-shelf'' — besides rigging up the training inputs, we made no alterations to the
 
-\section{Motivation for Denoising}
+\subsection{Motivation for Denoising}
 Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it.
 Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, or when our aesthetic sensibilities aren't injured.\\
+
+\subsection{Binarization}
+In this section, we discuss results obtained by training a binarizing denoiser to both restore augmented images to their ground truths and to classify pixels as foreground.\\
+
+We first performed an ensemble binarization preprocessing step on the clean groundtruth images.
+For each image, we computed the Niblack, Sauvola, and Otsu thresholds, using these to binarize three copies of the input.
+The average over the resulting matrices was taken elementwise, producing the final binarized groundtruth.
+
+One instance of the model was trained on the SimulatedNoisyOffice corpus, while the other was trained on a subset of ShabbyPages, in both cases using the relevant ensemble-binarized groundtruths.
+As a test, these models were used to denoise and binarize both the NoisyOfficeReal dataset and a testing subset taken from ShabbyPages which does not overlap the training subset.
+Common image processing metrics were applied to the predictions made by each model, comparing these to the (preprocessed) groundtruths.
+The averages of each metric over all such predictions was taken; these are presented in Table 2.
+\begin{table}[]
+    \centering
+    \caption{Image restoration performance between NoisyOffice-trained and ShabbyPages-trained NAFNet binarizing denoisers on cross-validation task}
+    \scalebox{0.81}{
+    \begin{tabular}{llll}
+    \toprule
+    \textbf{Training Set} & \textbf{Test Set} & \textbf{SSIM} & \textbf{RMSE} & \textbf{PSNR} \\
+        \midrule
+        \textsf{ShabbyPages} & \textsf{ShabbyPages} & \textsf{0.9255905809319086} & \textsf{2.987994328426575} & \textsf{39.29266235129017}\\
+        \textsf{SimulatedNoisyOffice} & \textsf{RealNoisyOffice} & \textsf{0.9866020337197627} & \textsf{3.8045857559449296} & \textsf{36.73658388839052}\\
+        \textsf{ShabbyPages} & \textsf{RealNoisyOffice} & \textsf{0.9465069385860134} & \textsf{3.2046770685272117} & \textsf{38.097843772060855}\\
+        \textsf{SimulatedNoisyOffice} & \textsf{ShabbyPages} & \textsf{0.8105023745816482} & \textsf{5.38408321532059} & \textsf{34.56195157529838}\\
+        \bottomrule
+    \end{tabular}}
+    \label{tab:binarization_results}
+\end{table}
+
+\subsubsection{Interpretation}
+As a baseline, we first evaluated the models against test sets associated with their training databases; the model trained on SimulatedNoisyOffice was used to enhance the RealNoisyOffice set, while the ShabbyPages-trained model cleaned a testing subset drawn from the full ShabbyPages set.
+
+We considered three common image processing metrics: structural similarity index, root mean squared error, and peak signal-to-noise ratio.
+
+Although the ShabbyPages-trained NAFNet predicted cleaned ShabbyPages images with a lower structural similarity score than the NoisyOffice-trained model predicted cleaned RealNoisyOffice images, the ShabbyPages model achieved superior performance on RMSE and PSNR.
+The ShabbyPages corpus contains a much higher feature diversity than NoisyOffice, so the lower SSIM score was not unexpected; local relationships between pixels were easier to encode for the NoisyOffice model, possibly because there are simply fewer relationships.
+The RMSE and PSNR results on the other hand indicate that the ShabbyPages-trained model learned to remove more noise with higher fidelity, and more accurately predicted foreground pixels than the NoisyOffice model.
+This discrepancy can partly be explained by the RealNoisyOffice corpus having been physically-noised as opposed to ShabbyPages' purely synthetic noise; small-scale features in the RealNoisyOffice testing data are not quite identical to the SimulatedNoisyOffice training inputs, while both the training and testing data taken from ShabbyPages was constructed by the same means.
+In the latter case, the \textit{diversity} of the ShabbyPages data is much higher (TODO: add diversity score info), and this instance of the NAFNet may have been able to generalize over noise types better than the NoisyOffice-trained network with its lower training diversity.\\
+
+The second stage of the binarization experiment was to cross-validate these models by predicting cleaned images using the other testing set as inputs.
+Here, the ShabbyPages-trained model achieved all-around better performance than the NoisyOffice-trained model, with a much higher structural similarity score (0.947 vs.
+0.811), lower RMSE, and higher PSNR.
+This is a strong indicator that neural networks trained on ShabbyPages can outperform those trained on NoisyOffice when generalizing to other datasets.
+
+Interestingly, the NoisyOffice-trained model RMSE and PSNR scores were lower when cleaning RealNoisyOffice than the Shabby-trained model: we were able to achieve a 3.5 decibel improvement in peak signal-to-noise ratio over the SimulatedNoisyOffice-trained model.
 
@@
 
+\bibitem{ref_NAFNet}
+  @misc{https://doi.org/10.48550/arxiv.2204.04676,
+  doi = {10.48550/ARXIV.2204.04676},
+  url = {https://arxiv.org/abs/2204.04676},
+  author = {Chen, Liangyu and Chu, Xiaojie and Zhang, Xiangyu and Sun, Jian},
+  keywords = {Computer Vision and Pattern Recognition (cs.CV), FOS: Computer and information sciences, FOS: Computer and information sciences},
+  title = {Simple Baselines for Image Restoration},
+  publisher = {arXiv},
+  year = {2022},
+  copyright = {arXiv.org perpetual, non-exclusive license}
+}
+
 \end{thebibliography}

### 2023-01-23 paper/paper.tex
add diversity metric

@@
 
+\textbf{Diversity.} We use the diversity metric as defined in \cite{kang-etal-2018-data,larson-etal-2019-outlier} to help us measure how diverse a dataset is.
+This metric is defined as 
+$$
+Diversity(X) = \frac{1}{|X|^2} \sum_{a\in X} \sum_{b\in X} \|f(a)-f(b)\|_2
+$$
+where $f(\cdot)$ is an embedding function mapping the input image into an \emph{n}-dimensional vector space.
+Here, we use CLIP's ViT model \cite{clip}, which embeds each image into a 512-dimensional embedding space.
+The intuition behind the diversity metric is that datasets where images are highly similar will have lower diversity scores, and datasets where images share less visual similarity will have higher diversity scores.
+A dataset with low diversity might not be representative enough of the real world, and low diversity may often correlate with task easiness.
+
 \begin{table}
@@
 Images & 6202 & 72 & 400000 & 1290\\
+Diversity & 0.488 & 0.317 & & \\
 Document-specific & Yes & Yes & Yes & Yes\\

### 2023-01-23 paper/paper.tex

--- 2023-01-23 paper/paper.tex
@@
 \title{ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images}
-\author{Alexander Groleau\inst{1,2} \and
-  Kok Wei Chee\inst{1} \and
-  Stefan Larson\inst{3} \and
-  Jonathan Boarman\inst{1} \and
-  Samay Maini\inst{1}}
+%\author{Alexander Groleau\inst{1,2} \and
+%  Kok Wei Chee\inst{1} \and
+%  Stefan Larson\inst{3} \and
+%  Jonathan Boarman\inst{1} \and
+%  Samay Maini\inst{1}}
+%
+%\authorrunning{A. Groleau et al.}
+%
+%\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
+%  \and
+%  Left Associates LLC (\email{research@left.associates})
+%  \and
+%  Vanderbilt University}
 
-\authorrunning{A. Groleau et al.}
-
-\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
-  \and
-  Left Associates LLC (\email{research@left.associates})
-  \and
-  Vanderbilt University}
+\author{Anonymous ICDAR 2023 submission}
 
@@
 In deep networks, these representations live within multiple layers, each of which corresponds to a feature of the input data.
-Document images are a particularly interesting category, as the data within the documents each picture represents is itself frequently multi-modal; the document may contain an image and its description, a table with statistics, multiple regions of structured and formatted text, and even other documents, making their internal representations by neural networks often quite complicated.\\
+Document images are a particularly interesting category, as the data within the documents each picture represents is itself frequently multi-modal; the document may contain an image and its description, a table with statistics, multiple regions of structured and formatted text, and even other documents, making their internal representations by neural networks often quite complicated.
 
@@
 Procuring a large-enough volume of robust-enough training data is paramount.
-Several sets of such images exist, many intended for processing by deep neural nets; Table 1 below contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.\\
+Several sets of such images exist, many intended for processing by deep neural nets; Table 1 below contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.
 
@@
 The groundtruth images were produced in a standard word processor, with the simulated noisy images produced by first adding noise to a blank sheet of paper, storing that as a background image after digital scanning, then overlaying the foreground text onto the noisy background texture.
-An additional set of real NoisyOffice images was produced, where the foreground text was printed on blank white sheets, the results of which were physically augmented by the introduction of footprints, coffee stains, wrinkles, and folds.\\
+An additional set of real NoisyOffice images was produced, where the foreground text was printed on blank white sheets, the results of which were physically augmented by the introduction of footprints, coffee stains, wrinkles, and folds.
 
@@
 The images exhibit poor fidelity with what we can imagine their originals to have been, contain substantial noise, and many were scanned at around 100 pixels per inch, quite a low resolution for documents.
-None of the images in the CDIP set come with groundtruths.\\
+None of the images in the CDIP set come with groundtruths.
 
@@
 Several of the images in this set are consecutively-numbered pages, increasing the set's utility for certain image analysis tasks \cite{ref_Tobacco800}.
-Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.\\
+Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.
 
@@
 In Table 1, we indicated that NoisyOffice was the only other groundtruthed dataset we examined.
-This isn't strictly true: there are projects to add some types of groundtruth to RVL-CDIP \cite{ref_goldmann}, \cite{ref_zenodo} and Tobacco800 \cite{ref_tobacco800gt1}, \cite{ref_tobacco800gt2}, but the images in these sets were produced by real scans, without an accompanying original digital document.
-Conversely, NoisyOffice contains images of real scanned documents intended for validation, as well as their digital groundtruth and synthetic training image data.\\
+This isn't strictly true: there are projects to add some types of groundtruth to RVL-CDIP \cite{ref_zenodo,ref_goldmann} and Tobacco800 \cite{ref_tobacco800gt2,ref_tobacco800gt1}, but the images in these sets were produced by real scans, without an accompanying original digital document.
+Conversely, NoisyOffice contains images of real scanned documents intended for validation, as well as their digital groundtruth and synthetic training image data.
 
@@
 \subsection{Statistics}
-ShabbyPages contains documents from multiple classes, which contain many types of information.\\
+ShabbyPages contains documents from multiple classes, which contain many types of information.
 
@@
 \subsection{Limitations}
-The ShabbyPages collection is a comprehensive entrant to the public datasphere, but with a relatively low starting document volume, makes some important omissions.\\
+The ShabbyPages collection is a comprehensive entrant to the public datasphere, but with a relatively low starting document volume, makes some important omissions.
 
-First, we arbitrarily selected 600 as the number of source documents. The number of final images of pages depends on this, and so is similarly arbitrary.\\
+First, we arbitrarily selected 600 as the number of source documents.
+The number of final images of pages depends on this, and so is similarly arbitrary.
 
@@
 Both approaches can be achieved by supervised learning of relationships between features of the input and output data.
-In this section, we train and compare several instances of the NAFNet \cite{ref_NAFNet} architecture as denoisers and binarizers, and evaluate these models' predictions on both the NoisyOffice and ShabbyPages datasets.
-The model was ``off-the-shelf'' — besides rigging up the training inputs, we made no alterations to the
+In this section, we train and compare several instances of the NAFNet \cite{ref_nafnet} architecture as denoisers and binarizers, and evaluate these models' predictions on both the NoisyOffice and ShabbyPages datasets.
+The model was ``off-the-shelf''; besides rigging up the training inputs, we made no alterations to the
 
@@
 Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it.
-Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, or when our aesthetic sensibilities aren't injured.\\
+Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, or when our aesthetic sensibilities aren't injured.
 
 \subsection{Binarization}
-In this section, we discuss results obtained by training a binarizing denoiser to both restore augmented images to their ground truths and to classify pixels as foreground.\\
+In this section, we discuss results obtained by training a binarizing denoiser to both restore augmented images to their ground truths and to classify pixels as foreground.
 
@@
 The averages of each metric over all such predictions was taken; these are presented in Table 2.
+
 \begin{table}[]
@@
 This discrepancy can partly be explained by the RealNoisyOffice corpus having been physically-noised as opposed to ShabbyPages' purely synthetic noise; small-scale features in the RealNoisyOffice testing data are not quite identical to the SimulatedNoisyOffice training inputs, while both the training and testing data taken from ShabbyPages was constructed by the same means.
-In the latter case, the \textit{diversity} of the ShabbyPages data is much higher (TODO: add diversity score info), and this instance of the NAFNet may have been able to generalize over noise types better than the NoisyOffice-trained network with its lower training diversity.\\
+In the latter case, the \textit{diversity} of the ShabbyPages data is much higher (TODO: add diversity score info), and this instance of the NAFNet may have been able to generalize over noise types better than the NoisyOffice-trained network with its lower training diversity.
 
@@
 %
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
+ \bibliographystyle{splncs04}
+ \bibliography{paper}
+
+%\begin{thebibliography}{8}
+%\bibitem{ref_Kaggle}
+%  https://www.kaggle.com/datasets
+%\bibitem{ref_HuggingFaceHub}
+%  {https://huggingface.co/datasets}
+%\bibitem{ref_RDCL2019}
+%{Christian Clausner, RDCL2019 Competition Dataset (Recognition of Documents with Complex Layouts) (RDCL2019) ,1,ID:RDCL2019\_1,URL:https://tc11.cvc.uab.es/datasets/RDCL2019_1}
 %
-\begin{thebibliography}{8}
-\bibitem{ref_Kaggle}
-  https://www.kaggle.com/datasets
-\bibitem{ref_HuggingFaceHub}
-  {https://huggingface.co/datasets}
-\bibitem{ref_RDCL2019}
-{Christian Clausner, RDCL2019 Competition Dataset (Recognition of Documents with Complex Layouts) (RDCL2019) ,1,ID:RDCL2019\_1,URL:https://tc11.cvc.uab.es/datasets/RDCL2019_1}
-
-\bibitem{ref_Tobacco800}
-{David Doermann, Tobacco 800 Dataset (Tobacco800) ,1,ID:Tobacco800_1,URL:https://tc11.cvc.uab.es/datasets/Tobacco800_1}
-
-\bibitem{ref_icdar}
-{Harold Mouchère, ICDAR 2019 Competition on Recognition of Handwritten Mathematical Expressions and Typeset Formula Detection (ICDAR2019-CROHME-TDF) ,1,ID:ICDAR2019-CROHME-TDF\_1,URL:https://tc11.cvc.uab.es/datasets/ICDAR2019-CROHME-TDF_1}
-
-\bibitem{ref_NoisyOffice}
-{Castro-Bleda, MJ.; España Boquera, S.; Pastor Pellicer, J.; Zamora Martínez, FJ.
+%\bibitem{ref_Tobacco800}
+%{David Doermann, Tobacco 800 Dataset (Tobacco800) ,1,ID:Tobacco800_1,URL:https://tc11.cvc.uab.es/datasets/Tobacco800_1}
+%
+%\bibitem{ref_icdar}
+%{Harold Mouchère, ICDAR 2019 Competition on Recognition of Handwritten Mathematical Expressions and Typeset Formula Detection (ICDAR2019-CROHME-TDF) ,1,ID:ICDAR2019-CROHME-TDF\_1,URL:https://tc11.cvc.uab.es/datasets/ICDAR2019-CROHME-TDF_1}
+%
+%\bibitem{ref_NoisyOffice}
+%{Castro-Bleda, MJ.; España Boquera, S.; Pastor Pellicer, J.; Zamora Martínez, FJ.
 (2020).
@@
 https://doi.org/10.1093/comjnl/bxz098}
-
-\bibitem{ref_RVL-CDIP}
-  @article{DBLP:journals/corr/HarleyUD15,
-  author    = {Adam W. Harley and
-               Alex Ufkes and
-               Konstantinos G. Derpanis},
-  title     = {Evaluation of Deep Convolutional Nets for Document Image Classification
-               and Retrieval},
-  journal   = {CoRR},
-  volume    = {abs/1502.07058},
-  year      = {2015},
-  url       = {http://arxiv.org/abs/1502.07058},
-  eprinttype = {arXiv},
-  eprint    = {1502.07058},
-  timestamp = {Mon, 13 Aug 2018 16:48:54 +0200},
-  biburl    = {https://dblp.org/rec/journals/corr/HarleyUD15.bib},
-  bibsource = {dblp computer science bibliography, https://dblp.org}
-}
-
-\bibitem{ref_NoisyOfficeDatabase}
-{F.
+%
+%\bibitem{ref_RVL-CDIP}
+%  @article{DBLP:journals/corr/HarleyUD15,
+%  author    = {Adam W. Harley and
+%               Alex Ufkes and
+%               Konstantinos G. Derpanis},
+%  title     = {Evaluation of Deep Convolutional Nets for Document Image Classification
+%               and Retrieval},
+%  journal   = {CoRR},
+%  volume    = {abs/1502.07058},
+%  year      = {2015},
+%  url       = {http://arxiv.org/abs/1502.07058},
+%  eprinttype = {arXiv},
+%  eprint    = {1502.07058},
+%  timestamp = {Mon, 13 Aug 2018 16:48:54 +0200},
+%  biburl    = {https://dblp.org/rec/journals/corr/HarleyUD15.bib},
+%  bibsource = {dblp computer science bibliography, https://dblp.org}
+%}
+%
+%\bibitem{ref_NoisyOfficeDatabase}
+%{F.
 Zamora-Martinez, S.
@@
 Castro-Bleda, Behaviour-based Clustering of Neural Networks applied to Document Enhancement, in: Computational and Ambient Intelligence, pages 144-151, Springer, 2007.}
-
-\bibitem{ref_UCIMLR}
-{Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.}
-
-\bibitem{ref_DocCreator}
-  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
-\bibitem{ref_goldmann}
-  {Pau Riba, Anjan Dutta, Lutz Goldmann, Alicia Fornes, Oriol Ramos, Josep LLados: "Table Detection in Invoice Documents by Graph Neural Networks", ICDAR, 2019.}
-\bibitem{ref_zenodo}
-  {Layout Analysis Groundtruth for the RVL-CDIP Dataset. Goldmann, Lutz. 10.5281/zenodo.3257319}
-\bibitem{ref_tobacco800gt1}
-  {Guangyu Zhu, Yefeng Zheng, David Doermann,and Stefan Jaeger.
+%
+%\bibitem{ref_UCIMLR}
+%{Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.}
+%
+%\bibitem{ref_DocCreator}
+%  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
+%\bibitem{ref_goldmann}
+%  {Pau Riba, Anjan Dutta, Lutz Goldmann, Alicia Fornes, Oriol Ramos, Josep LLados: "Table Detection in Invoice Documents by Graph Neural Networks", ICDAR, 2019.}
+%\bibitem{ref_zenodo}
+%  {Layout Analysis Groundtruth for the RVL-CDIP Dataset. Goldmann, Lutz. 10.5281/zenodo.3257319}
+%\bibitem{ref_tobacco800gt1}
+%  {Guangyu Zhu, Yefeng Zheng, David Doermann,and Stefan Jaeger.
 Multi-scale Structural Saliency for Signature Detection.
@@
 1‐8, 2007.}
-\bibitem{ref_tobacco800gt2}
-  {Guangyu Zhu and David Doermann. Automatic Document Logo Detection. In Proc. 9th Int. Conf. Document Analysis and Recognition (ICDAR 2007), pp. 864‐868, 2007.}
-
-\bibitem{ref_NAFNet}
-  @misc{https://doi.org/10.48550/arxiv.2204.04676,
-  doi = {10.48550/ARXIV.2204.04676},
-  url = {https://arxiv.org/abs/2204.04676},
-  author = {Chen, Liangyu and Chu, Xiaojie and Zhang, Xiangyu and Sun, Jian},
-  keywords = {Computer Vision and Pattern Recognition (cs.CV), FOS: Computer and information sciences, FOS: Computer and information sciences},
-  title = {Simple Baselines for Image Restoration},
-  publisher = {arXiv},
-  year = {2022},
-  copyright = {arXiv.org perpetual, non-exclusive license}
-}
-
-\end{thebibliography}
+%\bibitem{ref_tobacco800gt2}
+%  {Guangyu Zhu and David Doermann. Automatic Document Logo Detection. In Proc. 9th Int. Conf. Document Analysis and Recognition (ICDAR 2007), pp. 864‐868, 2007.}
+%
+%\bibitem{ref_NAFNet}
+%  @misc{https://doi.org/10.48550/arxiv.2204.04676,
+%  doi = {10.48550/ARXIV.2204.04676},
+%  url = {https://arxiv.org/abs/2204.04676},
+%  author = {Chen, Liangyu and Chu, Xiaojie and Zhang, Xiangyu and Sun, Jian},
+%  keywords = {Computer Vision and Pattern Recognition (cs.CV), FOS: Computer and information sciences, FOS: Computer and information sciences},
+%  title = {Simple Baselines for Image Restoration},
+%  publisher = {arXiv},
+%  year = {2022},
+%  copyright = {arXiv.org perpetual, non-exclusive license}
+%}
+%
+%
+%\end{thebibliography}
 \end{document}

### 2023-01-24 paper/paper.tex

@@
 \begin{figure}
-\includegraphics[width=\textwidth]{Article_Hero_Picture_Shadow.png}
-\caption{Example ShabbyPages image, before and after augmentation.} \label{fig1}
+\centering
+\includegraphics[width=0.98\columnwidth, frame]{Article_Hero_Picture_Shadow.png}
+\caption{Example ShabbyPages image, before (left side) and after augmentationi (right side).} \label{fig1}
 \end{figure}
@@
     \centering
-\caption{ShabbyPages Statistics}\label{tab1}
-\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
-\hline
-Statistic & Value \\
-\hline
-Images & 6202 \\
+    \caption{ShabbyPages dataset statistics.}\label{tab1}
+    \begin{tabular}{@{\hspace{2em}}l@{\qquad}@{\hspace{2em}}l@{\qquad}}
+        \toprule
+        \textbf{Statistic} & \textbf{Value} \\
+        \midrule
+        Num. Images & 6202 \\
         DPI & 150 \\
-Max image size & \_ \\
-\hline
+        Max image size & --- \\
+    \bottomrule
     \end{tabular}
@@
     \centering
-    \caption{Image restoration performance between NoisyOffice-trained and ShabbyPages-trained NAFNet binarizing denoisers on cross-validation task}
-    \scalebox{0.81}{
-    \begin{tabular}{llll}
+    \caption{Document image binarization performance of a NAFNet model trained and tested on ShabbyPages and NoisyOffice.}
+    %\caption{Document image binarization performance between NoisyOffice-trained and ShabbyPages-trained NAFNet binarizing de    noisers on cross-validation task}
+    \scalebox{0.9}{
+    \begin{tabular}{lllll}
     \toprule
-    \textbf{Training Set} & \textbf{Test Set} & \textbf{SSIM} & \textbf{RMSE} & \textbf{PSNR} \\
+    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{RMSE$\downarrow$~} & \textbf{PSNR$\uparrow$} \\
         \midrule
-        \textsf{ShabbyPages} & \textsf{ShabbyPages} & \textsf{0.9255905809319086} & \textsf{2.987994328426575} & \textsf{39.29266235129017}\\
-        \textsf{SimulatedNoisyOffice} & \textsf{RealNoisyOffice} & \textsf{0.9866020337197627} & \textsf{3.8045857559449296} & \textsf{36.73658388839052}\\
-        \textsf{ShabbyPages} & \textsf{RealNoisyOffice} & \textsf{0.9465069385860134} & \textsf{3.2046770685272117} & \textsf{38.097843772060855}\\
-        \textsf{SimulatedNoisyOffice} & \textsf{ShabbyPages} & \textsf{0.8105023745816482} & \textsf{5.38408321532059} & \textsf{34.56195157529838}\\
+        \textsf{ShabbyPages} & \textsf{ShabbyPages} & 0.926 & 2.99 & 39.3\\
+        \textsf{NoisyOffice-sim} & \textsf{NoisyOffice-real~} & 0.987 & 3.80 & 36.7\\
+        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & 0.947 & 3.20 & 38.1\\
+        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811 & 5.38 & 34.6\\
         \bottomrule

### 2023-01-25 generate_shabby.py
add shabby build script

@@ -1,0 +1,34 @@
+import os
+import cv2
+from multiprocessing import Pool
+from pathlib import Path
+from augraphy import *
+from PIL import Image
+import os
+import random
+import cv2
+from glob import glob
+import numpy as np
+from daily_pipeline import get_pipeline
+
+def run_pipeline(filename):
+    image = cv2.imread(filename.as_posix())
+    print(f"Processing {filename.stem}")
+    # returns the current Shabby Pages pipeline
+    pipeline = get_pipeline()
+    data = pipeline.augment(image)
+    shabby_image = data["output"]
+    output_filename = f"clean150/{filename.stem}-shabby.png"
+    cv2.imwrite(output_filename, shabby_image)
+
+
+if __name__ == "__main__":
+    input_path = Path("clean150")
+    filenames = [(input_path / name) for name in os.listdir(input_path)]
+
+    pool = Pool(os.cpu_count())
+
+    pool.imap_unordered(run_pipeline, filenames)
+    # wait for everything to finish
+    pool.close()
+    pool.join()

### 2023-02-04 paper/paper.tex
add patch matrix image
fix paper riding

@@
 \usepackage{graphicx}
+\usepackage{booktabs}
+\usepackage{pifont}
 \usepackage[colorlinks]{hyperref}
+\usepackage[dvipsnames]{xcolor}
 \hypersetup{
@@
 \usepackage{courier}
+
+% check mark and x for table
+\newcommand{\cmark}{{\color{ForestGreen}\ding{51}}}%
+\newcommand{\xmark}{{\color{Maroon}\ding{55}}}%
+
+\def\rot{\rotatebox}
+
 \renewcommand{\floatpagefraction}{.8}
@@
 \author{Anonymous ICDAR 2023 submission}
+\titlerunning{ShabbyPages}
 
@@
 \centering
-\includegraphics[width=0.98\columnwidth, frame]{Article_Hero_Picture_Shadow.png}
-\caption{Example ShabbyPages image, before (left side) and after augmentationi (right side).} \label{fig1}
+\includegraphics[width=0.98\columnwidth, frame]{matrix.png}
+\caption{Sample patches from ShabbyPages.} \label{fig1}
 \end{figure}
@@
 \hline
+\end{tabular}
+\end{table}
+
+% WIP: this table is a work-in-progress
+\begin{table}[]
+    \centering
+    \caption{Summary of datasets for document denoising and document binarization tasks.}
+    \label{tab:datasets}
+    \begin{tabular}{lcllllllll}
+        \textbf{Dataset} &
+        \rot{80}{\textbf{Dataset Size}}
+            & \rot{80}{\textbf{Synthetic Noise}}
+            & \rot{80}{\textbf{Ground-Truths}}
+            & \rot{80}{\textbf{Diversity}}
+            & \rot{80}{\textbf{Font size}}
+            & \rot{80}{\textbf{Paper styles}}
+            & \rot{80}{\textbf{Multilingual}}
+            & \rot{80}{\textbf{Contains graphics}}
+            & \rot{80}{\textbf{Pre-categorized}} \\
+            \midrule
+         ShabbyPages (ours) & 6,202 & \cmark & \cmark & 0.488 & Multi & Multi & \cmark & \cmark & \xmark \\
+         NoisyOffice \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & 16pt & 1 & \xmark & \xmark & \xmark \\
+         DocCreator & & & & & & & & & \\
+         DIBCO-9 \cite{dibco-09} & & & & & & & & & \\
+         DIBCO-10 \cite{dibco-10} & & & & & & & & & \\
+         DIBCO-11 \cite{dibco-11} & & \xmark & \cmark & & multi & Multi & \cmark & \xmark & \xmark \\
+         DIBCO-12 \cite{dibco-12} & & \xmark & & & & & & & \\
+         DIBCO-13 \cite{dibco-13} & & \xmark & & & & & & & \\
+         H-DIBCO-14 \cite{dibco-14} & & \xmark & & & & & & & \\
+         H-DIBCO-16 \cite{dibco-16} & & \xmark & & & & & & & \\
+         DIBCO-17 \cite{dibco-17} & & \xmark & & & & & & & \\
+         H-DIBCO-18 \cite{dibco-18} & & \xmark & & & & & & & \\
+         DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & \\
+         Bickley Diary \cite{bickley-diary} & & & & & & & & & \\
+         LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
+         \bottomrule
     \end{tabular}

### 2023-02-07 paper/paper.tex
remove commented bibliography, trim denoising results table

@@
 \section{Introduction}
-Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, free of noise or other degradations.
-ShabbyPages is a large dataset composed of 6202 clean/noisy pairs of images taken from 600 digital documents.
-Information about the set's contents and its relation to other datasets are explored in the next section.
-The noisy images were created from their clean origins by the application of a pipeline developed with the Augraphy library; the production of ShabbyPages is detailed in the third section, with all source code and input materials made openly available.
-The final dataset is used to train several denoising models which are compared directly and whose prediction results are compared together in the final section.
+%Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, free of noise or other degradations.
+%ShabbyPages is a large dataset composed of 6202 clean/noisy pairs of images taken from 600 digital documents.
+%Information about the set's contents and its relation to other datasets are explored in the next section.
+%The noisy images were created from their clean origins by the application of a pipeline developed with the Augraphy library; the production of ShabbyPages is detailed in the third section, with all source code and input materials made openly available.
+%The final dataset is used to train several denoising models which are compared directly and whose prediction results are compared together in the final section.
+
+Denoising is an important task in many document processing workflows, wherein unwanted artifacts introduced to a document image via noisy processes like scanning are removed.
+The effectiveness of the denoising stage of document processing pipelines has implications for downstream tasks like optical character recognition (OCR) and layout parsing [need to cite].
+Furthermore, recent work has found that supervised machine learning methods yield promising results at the denoising task [need to cite].
+Therefore, it is critical to have access to large-scale, high-quality training and evaluation data for document denoising.
+
+Prior work has introduced denoising and binarization datasets, but these are often small in scale, limited in the types of noise, or not diverse enough to train robust denoising models.
+For instance, the DIBCO datasets are far too small for large-scale training; each DIBCO dataset ranges between 10-20 images total.
+The NoisyOffice denoising dataset \cite{ref_NoisyOfficeDatabase} is small in scale (having \emph{n} training samples), and limited in the types of noise.
+NoisyOffice consists of artificial wrinkles and stains, but these only scratch the surface with regards to the plethora of noise types that occur in the real world.
+The DDI-100 corpus \cite{ddi-100-2019} is larger in scale than NoisyOffice and the DIBCO datasets, but is again limited in the amount of noise and diversity \cite{detection-masking-2022}.
+
+In this paper, we introduce a new dataset designed for the document denoising task.
+This new dataset, \emph{ShabbyPages}, is large-scale, having \emph{nnn} training and \emph{mmm} testing samples.
+\emph{ShabbyPages} is more diverse than alternatives like NoisyOffice, as it contains documents from various language groups and contains documents with graphical elements like tables and figures.
+We discuss \emph{ShabbyPages} in this paper, providing motivation and context for its creation.
+We also demonstrate its utility by benchmarking document denoising models.
 
@@
     \scalebox{0.9}{
-    \begin{tabular}{lllll}
+    \begin{tabular}{lll}
     \toprule
-    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{RMSE$\downarrow$~} & \textbf{PSNR$\uparrow$} \\
+    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~}\\
         \midrule
-        \textsf{ShabbyPages} & \textsf{ShabbyPages} & 0.926 & 2.99 & 39.3\\
-        \textsf{NoisyOffice-sim} & \textsf{NoisyOffice-real~} & 0.987 & 3.80 & 36.7\\
-        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & 0.947 & 3.20 & 38.1\\
-        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811 & 5.38 & 34.6\\
+        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & 0.947\\
+        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811\\
         \bottomrule
@@
 
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
 \bibliographystyle{splncs04}
 \bibliography{paper}
-
-%\begin{thebibliography}{8}
-%\bibitem{ref_Kaggle}
-%  https://www.kaggle.com/datasets
-%\bibitem{ref_HuggingFaceHub}
-%  {https://huggingface.co/datasets}
-%\bibitem{ref_RDCL2019}
-%{Christian Clausner, RDCL2019 Competition Dataset (Recognition of Documents with Complex Layouts) (RDCL2019) ,1,ID:RDCL2019\_1,URL:https://tc11.cvc.uab.es/datasets/RDCL2019_1}
-%
-%\bibitem{ref_Tobacco800}
-%{David Doermann, Tobacco 800 Dataset (Tobacco800) ,1,ID:Tobacco800_1,URL:https://tc11.cvc.uab.es/datasets/Tobacco800_1}
-%
-%\bibitem{ref_icdar}
-%{Harold Mouchère, ICDAR 2019 Competition on Recognition of Handwritten Mathematical Expressions and Typeset Formula Detection (ICDAR2019-CROHME-TDF) ,1,ID:ICDAR2019-CROHME-TDF\_1,URL:https://tc11.cvc.uab.es/datasets/ICDAR2019-CROHME-TDF_1}
-%
-%\bibitem{ref_NoisyOffice}
-%{Castro-Bleda, MJ.; España Boquera, S.; Pastor Pellicer, J.; Zamora Martínez, FJ.
-(2020).
-The NoisyOffice Database: A Corpus To Train Supervised Machine Learning Filters For Image Processing.
-The Computer Journal.
-63(11):1658-1667.
-https://doi.org/10.1093/comjnl/bxz098}
-%
-%\bibitem{ref_RVL-CDIP}
-%  @article{DBLP:journals/corr/HarleyUD15,
-%  author    = {Adam W. Harley and
-%               Alex Ufkes and
-%               Konstantinos G. Derpanis},
-%  title     = {Evaluation of Deep Convolutional Nets for Document Image Classification
-%               and Retrieval},
-%  journal   = {CoRR},
-%  volume    = {abs/1502.07058},
-%  year      = {2015},
-%  url       = {http://arxiv.org/abs/1502.07058},
-%  eprinttype = {arXiv},
-%  eprint    = {1502.07058},
-%  timestamp = {Mon, 13 Aug 2018 16:48:54 +0200},
-%  biburl    = {https://dblp.org/rec/journals/corr/HarleyUD15.bib},
-%  bibsource = {dblp computer science bibliography, https://dblp.org}
-%}
-%
-%\bibitem{ref_NoisyOfficeDatabase}
-%{F.
-Zamora-Martinez, S.
-España-Boquera and M.
-J.
-Castro-Bleda, Behaviour-based Clustering of Neural Networks applied to Document Enhancement, in: Computational and Ambient Intelligence, pages 144-151, Springer, 2007.}
-%
-%\bibitem{ref_UCIMLR}
-%{Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.}
-%
-%\bibitem{ref_DocCreator}
-%  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
-%\bibitem{ref_goldmann}
-%  {Pau Riba, Anjan Dutta, Lutz Goldmann, Alicia Fornes, Oriol Ramos, Josep LLados: "Table Detection in Invoice Documents by Graph Neural Networks", ICDAR, 2019.}
-%\bibitem{ref_zenodo}
-%  {Layout Analysis Groundtruth for the RVL-CDIP Dataset. Goldmann, Lutz. 10.5281/zenodo.3257319}
-%\bibitem{ref_tobacco800gt1}
-%  {Guangyu Zhu, Yefeng Zheng, David Doermann,and Stefan Jaeger.
-Multi-scale Structural Saliency for Signature Detection.
-In Proc.
-IEEE Conf.
-Computer Vision and Pattern Recognition (CVPR 2007), pp.
-1‐8, 2007.}
-%\bibitem{ref_tobacco800gt2}
-%  {Guangyu Zhu and David Doermann. Automatic Document Logo Detection. In Proc. 9th Int. Conf. Document Analysis and Recognition (ICDAR 2007), pp. 864‐868, 2007.}
-%
-%\bibitem{ref_NAFNet}
-%  @misc{https://doi.org/10.48550/arxiv.2204.04676,
-%  doi = {10.48550/ARXIV.2204.04676},
-%  url = {https://arxiv.org/abs/2204.04676},
-%  author = {Chen, Liangyu and Chu, Xiaojie and Zhang, Xiangyu and Sun, Jian},
-%  keywords = {Computer Vision and Pattern Recognition (cs.CV), FOS: Computer and information sciences, FOS: Computer and information sciences},
-%  title = {Simple Baselines for Image Restoration},
-%  publisher = {arXiv},
-%  year = {2022},
-%  copyright = {arXiv.org perpetual, non-exclusive license}
-%}
-%
-%
-%\end{thebibliography}
 \end{document}

### 2023-02-07 generate_shabby.py
fix shabby output path, which also fixes cv2.imwrite libpng error

@@ -18,7 +18,7 @@ def run_pipeline(filename):
     pipeline = get_pipeline()
     data = pipeline.augment(image)
     shabby_image = data["output"]
-    output_filename = f"clean150/{filename.stem}-shabby.png"
+    output_filename = f"shabby150/{filename.stem}.png"
     cv2.imwrite(output_filename, shabby_image)
 
 

### 2023-02-07 generate_patches.py
add patch generation & split scripts, organize repo better

@@ -1,0 +1,62 @@
+import os
+from pathlib import Path
+import cv2
+import random
+from multiprocessing import Pool
+import sys
+import numpy
+import time
+
+def generate_random_patch_coordinates(image):
+    y,x,channels = image.shape
+    patch_width = 400
+    x_min = 0
+    x_max = x - patch_width
+    y_min = 0
+    y_max = y - patch_width
+
+    x1 = random.randint(x_min, x_max)
+    y1 = random.randint(y_min, y_max)
+    x2 = x1 + patch_width
+    y2 = y1 + patch_width
+
+    return x1,x2,y1,y2
+
+def generate_ten_patches(filename_pair):
+    print(f"Processing {filename_pair[0].as_posix()}")
+    for i in range(10):
+        clean_image = cv2.imread(filename_pair[0].as_posix())
+        shabby_image = cv2.imread(filename_pair[1].as_posix())
+
+        x_low,x_high,y_low,y_high = generate_random_patch_coordinates(clean_image)
+
+        clean_patch = clean_image[x_low:x_high,y_low:y_high,:]
+        shabby_patch = shabby_image[x_low:x_high,y_low:y_high,:]
+
+        shabby_output_filename = 'patches/shabby_patches/' + filename_pair[0].stem + f'-patch-{i}.png'
+        cv2.imwrite(shabby_output_filename, shabby_patch)
+
+        clean_output_filename = 'patches/clean_patches/' + filename_pair[1].stem + f'-patch-{i}.png'
+        cv2.imwrite(clean_output_filename, clean_patch)
+
+if __name__ == '__main__':
+    base_directory = Path('patches')
+    base_directory.mkdir()
+    shabby_full_directory = base_directory / 'shabby150'
+    clean_full_directory = base_directory / 'clean150'
+
+    shabby_patches_path = base_directory / 'shabby_patches'
+    shabby_patches_path.mkdir()
+    clean_patches_path = base_directory / 'clean_patches'
+    clean_patches_path.mkdir()
+
+    shabby_full_pages = [shabby_full_directory / filename for filename in sorted(os.listdir(shabby_full_directory))]
+    clean_full_pages = [clean_full_directory / filename for filename in sorted(os.listdir(clean_full_directory))]
+
+    filepath_pairs = zip(clean_full_pages, shabby_full_pages)
+
+    process_pool = Pool(os.cpu_count())
+    process_pool.imap_unordered(generate_ten_patches, filepath_pairs)
[…]

### 2023-02-07 train-test-split.py

@@ -1,0 +1,68 @@
+import os
+import shutil
+from pathlib import Path
+import cv2
+import random
+from multiprocessing import Pool
+import sys
+import math
+
+random.seed(0)
+train_percent = 0.7
+validate_percent = 0.2
+test_percent = 0.1
+
+clean_patch_path = Path("patches/clean_patches")
+shabby_patch_path = Path("patches/shabby_patches")
+train_clean_path = Path("patches/train_clean")
+train_clean_path.mkdir()
+train_path = Path("patches/train")
+train_path.mkdir()
+validate_clean_path = Path("patches/validate_clean")
+validate_clean_path.mkdir()
+validate_path = Path("patches/validate")
+validate_path.mkdir()
+test_clean_path = Path("patches/test_clean")
+test_clean_path.mkdir()
+test_path = Path("patches/test")
+test_path.mkdir()
+
+
+clean_patches = sorted(os.listdir("patches/clean_patches"))
+shabby_patches = sorted(os.listdir("patches/shabby_patches"))
+
+num_patches = len(train_clean_patches)
+indices = range(num_patches)
+
+train_count = math.floor(train_percent * num_patches)
+train_sample = random.sample(indices, train_count)
+
+validate_count = math.floor(validate_percent * num_patches)
+indices_not_train = list(set(indices).difference(set(train_sample)))
+validate_sample = random.sample(indices_not_train, validate_count)
+
+test_count = num_patches - train_count - validate_count
+indices_not_train_validate = list(set(indices).difference(set(train_sample)).difference(set(validate_sample)))
+test_sample = indices_not_train_validate
+
+for i in train_sample:
+    shutil.copyfile(clean_patch_path / clean_patches[i], train_clean_path / clean_patches[i])
+    shutil.copyfile(shabby_patch_path / shabby_patches[i], train_path / shabby_patches[i])
+
+for i in validate_sample:
+    shutil.copyfile(clean_patch_path / clean_patches[i], validate_clean_path / clean_patches[i])
+    shutil.copyfile(shabby_patch_path / shabby_patches[i], validate_path / shabby_patches[i])
+
+for i in test_sample:
+    shutil.copyfile(clean_patch_path / clean_patches[i], test_clean_path / clean_patches[i])
+    shutil.copyfile(shabby_patch_path / shabby_patches[i], test_path / shabby_patches[i])
+
+# check that all went according to plan
[…]

### 2023-02-09 paper/paper.tex
add patch generation & split scripts, organize repo better
substantial changes to narrative organization and authorial voice

@@
 The release of this dataset and the recipe for its production attempts to address a growing need for labeled training document images for supervised learning tasks.
-The results of several experiments are discussed, in which the corpus trains performant convolutional denoisers, which remove real noise features with a high degree of human-perceptible fidelity, establishing baseline performance for a new ShabbyPages benchmark.
+The results of initial experiments are discussed, in which the corpus is used to train performant convolutional denoisers which remove real noise features with a high degree of human-perceptible fidelity, establishing baseline performance for a new ShabbyPages benchmark.
 \end{abstract}
@@
 
-Denoising is an important task in many document processing workflows, wherein unwanted artifacts introduced to a document image via noisy processes like scanning are removed.
+Denoising is a fundamental concern for many document processing workflows, wherein unwanted artifacts introduced to a document image via noisy processes like scanning are removed.
 The effectiveness of the denoising stage of document processing pipelines has implications for downstream tasks like optical character recognition (OCR) and layout parsing [need to cite].
-Furthermore, recent work has found that supervised machine learning methods yield promising results at the denoising task [need to cite].
-Therefore, it is critical to have access to large-scale, high-quality training and evaluation data for document denoising.
+Recent work in supervised machine learning has yielded promising results at the denoising task [need to cite], increasing the importance of access to large volumes of high-quality training and evaluation data.
 
-Prior work has introduced denoising and binarization datasets, but these are often small in scale, limited in the types of noise, or not diverse enough to train robust denoising models.
-For instance, the DIBCO datasets are far too small for large-scale training; each DIBCO dataset ranges between 10-20 images total.
-The NoisyOffice denoising dataset \cite{ref_NoisyOfficeDatabase} is small in scale (having \emph{n} training samples), and limited in the types of noise.
-NoisyOffice consists of artificial wrinkles and stains, but these only scratch the surface with regards to the plethora of noise types that occur in the real world.
-The DDI-100 corpus \cite{ddi-100-2019} is larger in scale than NoisyOffice and the DIBCO datasets, but is again limited in the amount of noise and diversity \cite{detection-masking-2022}.
+Prior work has introduced denoising and binarization datasets, but these are often small in scale, limited in the types of noise features present, not diverse enough to train robust models, and impossible to recreate.
+\begin{itemize}
+\item The DIBCO datasets — widely recognized as critical data for document denoising and binarization — are far too small for large-scale training; each DIBCO dataset ranges between 10-20 images total.
+\item The NoisyOffice denoising dataset \cite{ref_NoisyOfficeDatabase} is also quite small, having \emph{72} training samples, and contains only a few types of noise — primarily artificial wrinkles and stains, with little variation.
+\item The DDI-100 corpus \cite{ddi-100-2019} is larger in scale than NoisyOffice and the DIBCO datasets, but is again limited in the degree of feature diversity \cite{detection-masking-2022}.
+\end{itemize}
 
-In this paper, we introduce a new dataset designed for the document denoising task.
-This new dataset, \emph{ShabbyPages}, is large-scale, having \emph{nnn} training and \emph{mmm} testing samples.
+In this paper, we introduce a new dataset designed primarily for the document denoising task, which addresses each of the concerns listed above.
+This new dataset, \emph{ShabbyPages}, is large-scale, having \emph{6202} training and \emph{mmm} [TODO: do we need this?] testing samples.
 \emph{ShabbyPages} is more diverse than alternatives like NoisyOffice, as it contains documents from various language groups and contains documents with graphical elements like tables and figures.
-We discuss \emph{ShabbyPages} in this paper, providing motivation and context for its creation.
-We also demonstrate its utility by benchmarking document denoising models.
+In the next sections, we provide motivation and context for ShabbyPages' creation, compare it at length to other important datasets in the same space, describe the corpus construction process, and finally demonstrate its utility by benchmarking document denoising models trained on the dataset.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.98\columnwidth, frame]{figures/matrix.png}
+\caption{Sample patches from ShabbyPages.} \label{fig1}
+\end{figure}
 
@@
 Of the many image datasets available, the authors understand few to have been designed for groundtruthed supervised learning of document-specific tasks like binarization or denoising.
-In fact, we could find only one other set compiled for doing so with images of \textit{modern} documents: NoisyOffice \cite{ref_NoisyOffice}.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.98\columnwidth, frame]{matrix.png}
-\caption{Sample patches from ShabbyPages.} \label{fig1}
-\end{figure}
+In fact, we could find only one other set compiled specifically for doing so with images of \textit{modern} documents: NoisyOffice \cite{ref_NoisyOffice}.
 
@@
 Networks with a wider variety of latent representations frequently perform better when generalizing their learned functions to other tasks.
-Procuring a large-enough volume of robust-enough training data is paramount.
+For this reason, procuring a large-enough volume of robust-enough training data is paramount.
 Several sets of such images exist, many intended for processing by deep neural nets; Table 1 below contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.
-
-\textbf{Diversity.} We use the diversity metric as defined in \cite{kang-etal-2018-data,larson-etal-2019-outlier} to help us measure how diverse a dataset is.
-This metric is defined as
-$$
-Diversity(X) = \frac{1}{|X|^2} \sum_{a\in X} \sum_{b\in X} \|f(a)-f(b)\|_2
-$$
-where $f(\cdot)$ is an embedding function mapping the input image into an \emph{n}-dimensional vector space.
-Here, we use CLIP's ViT model \cite{clip}, which embeds each image into a 512-dimensional embedding space.
-The intuition behind the diversity metric is that datasets where images are highly similar will have lower diversity scores, and datasets where images share less visual similarity will have higher diversity scores.
-A dataset with low diversity might not be representative enough of the real world, and low diversity may often correlate with task easiness.
 
@@
 
+\textbf{Diversity.} We use the diversity metric as defined in \cite{kang-etal-2018-data,larson-etal-2019-outlier} to help us measure intra-dataset variety.
+This metric is defined as
+$$
+Diversity(X) = \frac{1}{|X|^2} \sum_{a\in X} \sum_{b\in X} \|f(a)-f(b)\|_2
+$$
+where $f(\cdot)$ is an embedding function mapping the input image into an \emph{n}-dimensional vector space.
+Here, we use CLIP's ViT model \cite{clip}, which embeds each image into a 512-dimensional space.
+The intuition behind the diversity metric is that datasets where images are highly similar will have lower diversity scores, and datasets where images share less visual similarity will have higher diversity scores.
+A dataset with low diversity might not be representative enough of the real world, and low diversity may further correlate with task easiness.
+
+\subsection{Statistics}
+ShabbyPages contains documents from multiple classes, which contain many types of information.
+
+Table 2 below contains some statistics for the dataset, in grayscale, at a standard resolution of 150 ppi.
+
+\begin{table}
+    \centering
+    \caption{ShabbyPages dataset statistics.}\label{tab1}
+    \begin{tabular}{@{\hspace{2em}}l@{\qquad}@{\hspace{2em}}l@{\qquad}}
+        \toprule
+        \textbf{Statistic} & \textbf{Value} \\
+        \midrule
+        Num. Images & 6202 \\
+        DPI & 150 \\
+        Max image size & 3336x12157 \\
+        Min image size & 532x532\\
+    \bottomrule
+    \end{tabular}
+\end{table}
+
+\subsection{ShabbyPages Compared}
+Supervised learning tasks require labeled training data, called the ground truth.
+Much of the world's data does not come with labels, which instead must be created by humans in some fashion.
+In Table 1, we indicated that NoisyOffice was the only other groundtruthed dataset we examined.
+This isn't strictly true: there are projects to add some types of groundtruth to RVL-CDIP \cite{ref_zenodo,ref_goldmann} and Tobacco800 \cite{ref_tobacco800gt2,ref_tobacco800gt1}, but the images in these sets were produced by real scans, without an accompanying original digital document.
+Conversely, NoisyOffice contains images of real scanned documents intended for validation, as well as their digital groundtruth and synthetic training image data.
+
+ShabbyPages includes not only the groundtruth images, but also the original digital documents used to produce them, and the software for fully reproducing the ShabbyPages set, allowing anyone to quickly produce a new set in the Shabby family, optionally re-exporting groundtruths at a different resolution beforehand.
+The 6202 images in the ShabbyPages release set are really just the first sample from the space of these documents; we encourage readers to build their own.
+NoisyOffice is the only other set we examined that contains its digital provenance, but the released database materials lack a means of reproducing the simulated printing method used to create the NoisyOffice training data.
+Augraphy's PaperFactory augmentation is such a tool.
+The other sets are not even theoretically extensible in this way.
+
 \subsubsection{NoisyOffice}
@@
 The smallest image is 532 by 532, with the largest 3336 wide by 12157 tall.
-6202 images are present in ShabbyPages, but this number could easily be increased by simply running another Augraphy pipeline to generate more.
-
-\subsection{ShabbyPages Compared}
-Supervised learning tasks require labeled training data, called the ground truth.
-Much of the world's data does not come with labels, which instead must be created by humans in some fashion.
-In Table 1, we indicated that NoisyOffice was the only other groundtruthed dataset we examined.
-This isn't strictly true: there are projects to add some types of groundtruth to RVL-CDIP \cite{ref_zenodo,ref_goldmann} and Tobacco800 \cite{ref_tobacco800gt2,ref_tobacco800gt1}, but the images in these sets were produced by real scans, without an accompanying original digital document.
-Conversely, NoisyOffice contains images of real scanned documents intended for validation, as well as their digital groundtruth and synthetic training image data.
-
-ShabbyPages includes not only the groundtruth images, but also the original digital documents used to produce them, and the software for fully reproducing the ShabbyPages set, allowing anyone to quickly produce a new set in the Shabby family, optionally re-exporting groundtruths at a different resolution beforehand.
-The 6202 images in the ShabbyPages release set are really just the first sample from the space of these documents; we encourage building your own.
-NoisyOffice is the only other set we examined that contains its digital provenance, but the released database materials lack a means of reproducing the simulated printing method used to create the NoisyOffice training data.
-Augraphy's PaperFactory augmentation is such a tool.
-The other sets are not even theoretically extensible in this way.
-
-\subsection{Statistics}
-ShabbyPages contains documents from multiple classes, which contain many types of information.
-
-Table 2 below contains some statistics for the dataset, in grayscale, at a standard resolution of 150 ppi.
-
-\begin{table}
-    \centering
-    \caption{ShabbyPages dataset statistics.}\label{tab1}
-    \begin{tabular}{@{\hspace{2em}}l@{\qquad}@{\hspace{2em}}l@{\qquad}}
-        \toprule
-        \textbf{Statistic} & \textbf{Value} \\
-        \midrule
-        Num. Images & 6202 \\
-        DPI & 150 \\
-        Max image size & --- \\
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-\subsection{Limitations}
-The ShabbyPages collection is a comprehensive entrant to the public datasphere, but with a relatively low starting document volume, makes some important omissions.
-
-First, we arbitrarily selected 600 as the number of source documents.
-The number of final images of pages depends on this, and so is similarly arbitrary.
-
-There are only a few languages represented, which reflects a number of biases, including the following:
-\begin{itemize}
-\item The native languages of the document-searchers
-\item The locations from which the document-searchers searched
-\item The search techniques used by each document-searcher
-\end{itemize}
-
-This work does not account for them, but these biases are significant determiners on the set of input documents.
-We hoped to overcome this somewhat by picking a suitably large number of input documents, and settled at 600.
+6202 images are present in ShabbyPages, but this number could easily be increased by simply running another Augraphy pipeline to generate more; in testing, we rendered several tens of thousands of such images, with the cumulative computation time still less than one day due to Augraphy's efficiency.
 
@@
 To address this, we broke all of the parameters for every augmentation constructor out into separate variables, tweaking these and committing the new pipeline to GitHub.
-We created an automated daily build in GitHub Actions to render a random selection of ground-truth images with the updated pipeline, then our team met frequently to discuss the output and make adjustments to the pipeline.
+We created an automated daily build in GitHub Actions to render a random selection of ground-truth images with the updated pipeline, then our team met frequently to discuss the output and make adjustments to the augmentation parameters, until we were consistently satisfied with the results.
+
+The pipeline uses the following augmentations: [TODO: expand]
+BadPhotocopy
+BindingsAndfasteners
+BleedThrough
+DirtyDrum
+Dirtyrollers
+Dithering
+Faxify
+Gamma
+Geometric
+InkBleed
+Jpeg
+Letterpress
+LightingGradient
+LowInkPeriodicLines
+LowInkRandomLines
+Markup
+NoiseTexturize
+PageBorder
+PaperColor
+PaperFactory
+PencilScribbles
+SubtleNoise
+
+PaperFactory was used with 300 textures, dramatically increasing the possible variations in the final dataset.
+We did not use Brightness or BrightnessTexturize, because these can interact poorly with some of the paper textures we chose.
+We also omitted the BookBinding augmentation, which can alter the document image geometry by adding additional pixels, making the result unsuitable for analysis by many common metrics.
 
@@
 The library is under active development with performance enhancements underway, but the time cost to generate large datasets sequentially is prohibitive when dealing with thousands of files, so we use a multi-process pooling technique to distribute the workload across many processor execution threads.
-For each process, we generate a new pipeline, run the pipeline object on an image, and save the output, using the code below:
+For each process, we generate a new pipeline, run the pipeline object on an image, and save the output, using the code below: [TODO: can we cut this down to just the pipeline function?]
 
@@
 Both approaches can be achieved by supervised learning of relationships between features of the input and output data.
-In this section, we train and compare several instances of the NAFNet \cite{ref_nafnet} architecture as denoisers and binarizers, and evaluate these models' predictions on both the NoisyOffice and ShabbyPages datasets.
-The model was ``off-the-shelf''; besides rigging up the training inputs, we made no alterations to the
+In this section, we train two NAFNet \cite{ref_nafnet} instances as denoisers on both the NoisyOffice and the ShabbyPages datasets.
+We evaluate these models' predictions in a cross-validation test on both datasets, both by visual inspection and by metric computation.
+The model was ``off-the-shelf''; besides rigging up the training inputs and choosing a reasonable training epoch limit, we made no significant alterations to the provided hyperparameters.
 
-\subsection{Motivation for Denoising}
-Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it.
-Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, or when our aesthetic sensibilities aren't injured.
-
-\subsection{Binarization}
-In this section, we discuss results obtained by training a binarizing denoiser to both restore augmented images to their ground truths and to classify pixels as foreground.
+\subsection{Binarization} [TODO: do we want to throw this away? It's still an important part of the story]
+In this section, we discuss results obtained by training a denoiser to both restore augmented images to their ground truths and to classify pixels as foreground.
 
@@
 
-One instance of the model was trained on the SimulatedNoisyOffice corpus, while the other was trained on a subset of ShabbyPages, in both cases using the relevant ensemble-binarized groundtruths.
+One instance of the model was trained on the full SimulatedNoisyOffice corpus, while the other was trained on a 1050-image subset of ShabbyPages, cropped to a random 500x500 patch.
+In both cases, the prediction target was the relevant ensemble-binarized groundtruths, and each instance trained for 100 epochs.
 As a test, these models were used to denoise and binarize both the NoisyOfficeReal dataset and a testing subset taken from ShabbyPages which does not overlap the training subset.
+[TODO: Can we get the metrics for ShabbyReal instead?]
 Common image processing metrics were applied to the predictions made by each model, comparing these to the (preprocessed) groundtruths.
@@
     \centering
-    \caption{Document image binarization performance of a NAFNet model trained and tested on ShabbyPages and NoisyOffice.}
-    %\caption{Document image binarization performance between NoisyOffice-trained and ShabbyPages-trained NAFNet binarizing de    noisers on cross-validation task}
+    \caption{Document image *binarization* performance of a NAFNet model trained and tested on ShabbyPages and NoisyOffice.}
     \scalebox{0.9}{
@@
 
-\subsubsection{Interpretation}
+The ShabbyPages-trained model was able to classify foreground and background pixels with a substantially higher degree of accuracy than the NoisyOffice-trained model, even with arguably worse training data.
+
+\subsection{Denoising}
+Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it.
+Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, and when our aesthetic sensibilities are un-challenged.
+
+Denoising grayscale images is a considerably harder task than binarization, as the space of possible predictions for a pixel value increases from one to eight bits (black/white to 256 shades of gray).
+To offset this increased difficulty, we randomly selected ten patches of 400x400 pixels from each page, then trained another NAFNet instance on this data for 1000 epochs.
+The results of a denoising experiment are presented in the table below.
+
+\begin{table}[]
+    \centering
+    \caption{Document image *denoising* cross-test performance of NAFNet models trained on ShabbyPages and NoisyOffice.}
+    \scalebox{0.9}{
+    \begin{tabular}{lll}
+    \toprule
+    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~}\\
+        \midrule
+        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & 0.950\\
+        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.83\\
+        \bottomrule
+    \end{tabular}}
+    \label{tab:denoising_results}
+\end{table}
+
+As can be seen from Table \cite{tab:denoising_results}, the ShabbyPages-trained denoiser generalized to NoisyOffice far better than the NoisyOffice-trained model generalized to ShabbyPages.
+This result is consistent with the much higher diversity present within the ShabbyPages set, relative to features found in the NoisyOffice database.
+
+\subsubsection{Interpretation} [TODO: roll this into the previous section and/or delete most of it]
 As a baseline, we first evaluated the models against test sets associated with their training databases; the model trained on SimulatedNoisyOffice was used to enhance the RealNoisyOffice set, while the ShabbyPages-trained model cleaned a testing subset drawn from the full ShabbyPages set.
 
-We considered three common image processing metrics: structural similarity index, root mean squared error, and peak signal-to-noise ratio.
+We considered the structural similarity index, a common image processing metric.
 
@@
 
+\section{Real Shabby Pages}
+In keeping with the spirit of NoisyOffice, our original inspiration, and to provide out-of-distribution test data for other projects, we developed a separate but related dataset which we call Real ShabbyPages.
+To build this, we isolated reproduction steps for several physical operations, designed real-world augmentation pipelines with these, and then engaged a team of workers to use these instructions to produce several copies of printed born-digital documents with real noise.
+
+Several challenges arose in the construction of this dataset.
+Manually producing a database of noisy documents is a time-consuming and repetitive task; creating just 100 real-world documents with real noise features required the labor of several people.
+Old fax machines, faulty commercial printers, and other hardware suitable for inducing the intended effects were difficult to find.
+Environmental concerns like the volume of paper and ink used, or the energy expenditure, also factored into our decision to pursue synthetic augmentations for ShabbyPages.
+
 \bibliographystyle{splncs04}

### 2023-02-10 paper/paper.tex

@@
 
-\begin{table}
-\centering
-\caption{Document Image Dataset Feature Comparison}\label{tab1}
-\begin{tabular}{|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|}
-\hline
-Feature & ShabbyPages & NoisyOffice & RVL-CDIP & Tobacco800 \\
-\hline
-Images & 6202 & 72 & 400000 & 1290\\
-Diversity & 0.488 & 0.317 & & \\
-Document-specific & Yes & Yes & Yes & Yes\\
-Synthetic & Yes & Yes & No & No\\
-Groundtruthed? & Yes & Yes & No & No\\
-Font size & Multiple & 16pt & Multiple & Multiple\\
-Paper styles & Multiple & 1 & Multiple & Multiple\\
-Multilingual & Yes & No & No & No\\
-Documents contain images? & Yes & No & Yes & Yes\\
-Pre-categorized & No & No & Yes & Yes\\
-\hline
-\end{tabular}
-\end{table}
+%\begin{table}
+%\centering
+%\caption{Document Image Dataset Feature Comparison}\label{tab1}
+%\begin{tabular}{|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|}
+%\hline
+%Feature & ShabbyPages & NoisyOffice & RVL-CDIP & Tobacco800 \\
+%\hline
+%Images & 6202 & 72 & 400000 & 1290\\
+%Diversity & 0.488 & 0.317 & & \\
+%Document-specific & Yes & Yes & Yes & Yes\\
+%Synthetic & Yes & Yes & No & No\\
+%Groundtruthed? & Yes & Yes & No & No\\
+%Font size & Multiple & 16pt & Multiple & Multiple\\
+%Paper styles & Multiple & 1 & Multiple & Multiple\\
+%Multilingual & Yes & No & No & No\\
+%Documents contain images? & Yes & No & Yes & Yes\\
+%Pre-categorized & No & No & Yes & Yes\\
+%\hline
+%\end{tabular}
+%\end{table}
 
@@
             & \rot{80}{\textbf{Contains graphics}}
-            & \rot{80}{\textbf{Pre-categorized}} \\
+            & \rot{80}{\textbf{Reproducible}}\\
             \midrule
-         ShabbyPages (ours) & 6,202 & \cmark & \cmark & 0.488 & Multi & Multi & \cmark & \cmark & \xmark \\
+         ShabbyPages (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & multi~ & multi~ & \cmark & \cmark & \cmark \\
          NoisyOffice \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & 16pt & 1 & \xmark & \xmark & \xmark \\
-         DocCreator & & & & & & & & & \\
-         DIBCO-9 \cite{dibco-09} & & & & & & & & & \\
-         DIBCO-10 \cite{dibco-10} & & & & & & & & & \\
-         DIBCO-11 \cite{dibco-11} & & \xmark & \cmark & & multi & Multi & \cmark & \xmark & \xmark \\
-         DIBCO-12 \cite{dibco-12} & & \xmark & & & & & & & \\
-         DIBCO-13 \cite{dibco-13} & & \xmark & & & & & & & \\
-         H-DIBCO-14 \cite{dibco-14} & & \xmark & & & & & & & \\
-         H-DIBCO-16 \cite{dibco-16} & & \xmark & & & & & & & \\
-         DIBCO-17 \cite{dibco-17} & & \xmark & & & & & & & \\
-         H-DIBCO-18 \cite{dibco-18} & & \xmark & & & & & & & \\
-         DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & \\
-         Bickley Diary \cite{bickley-diary} & & & & & & & & & \\
-         LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
+         DocCreator \cite{ref_DocCreator} & & \cmark & \xmark & & & & & &\cmark\\
+         DIBCO-9 \cite{dibco-09} & & & & & & & & & n/a \\
+         DIBCO-10 \cite{dibco-10} & 10 & \xmark & \cmark & & multi & multi & \xmark & \xmark & n/a \\
+         DIBCO-11 \cite{dibco-11} & 16 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a\\
+         DIBCO-12 \cite{dibco-12} & 14 & \xmark & \cmark & & multi & multi & \xmark & \xmark & n/a \\
+         DIBCO-13 \cite{dibco-13} & 16 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
+         H-DIBCO-14 \cite{dibco-14} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
+         H-DIBCO-16 \cite{dibco-16} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
+         DIBCO-17 \cite{dibco-17} & 20 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
+         H-DIBCO-18 \cite{dibco-18} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a\\
+         DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & n/a\\
+         Bickley Diary \cite{bickley-diary} & & & & n/a & & & & & n/a\\
+         PHIBD & & & & & & & & & n/a\\
+         TQBC & & & & & & & & & n/a\\
+         %LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
+         DDI-100 \cite{ddi-100-2019} & & \cmark & \cmark & & & & & & \xmark\\
          \bottomrule
@@
 
-\subsection{ShabbyPages Compared}
-Supervised learning tasks require labeled training data, called the ground truth.
-Much of the world's data does not come with labels, which instead must be created by humans in some fashion.
-In Table 1, we indicated that NoisyOffice was the only other groundtruthed dataset we examined.
-This isn't strictly true: there are projects to add some types of groundtruth to RVL-CDIP \cite{ref_zenodo,ref_goldmann} and Tobacco800 \cite{ref_tobacco800gt2,ref_tobacco800gt1}, but the images in these sets were produced by real scans, without an accompanying original digital document.
-Conversely, NoisyOffice contains images of real scanned documents intended for validation, as well as their digital groundtruth and synthetic training image data.
+\subsection{Other Datasets}
+The most similar existing dataset to ShabbyPages for the tasks of document denoising include NoisyOffice \cite{ref_NoisyOfficeDatabase}.
+NoisyOffie is a very limited, however, consisting of two types of font and three font sizes of text across four base images.
+The NoisyOffice dataset was created by permuting these font/size/base combinations, and thus the dataset is feature-poor.
+NoisyOffice also lacks non-English and non-Latin texts, as well as graphical elements like images, logos, and tables.
+To add noise to NoisyOffice, the creators used four different types of noise backgrounds ([TODO: list them here]) and then overlayed generated text onto the noisy backgrounds.
+Overall, NoisyOffice consists of 72 document images.
+Another dataset, DDI-100 \cite{ddi-100-2019}, was constructed in a manner similar to NoisyOffice.
+DDI-100 is far larger than NoisyOffice, but has been criticized for not containing enough diversity or noise to be an effective benchmark \cite{detection-masking-2022}.
+Additionally, the pipeline code for creating the noisy versions of both NoisyOffice and DDI-100 is not available, and thus these datasets cannot be reproduced.
+
+Prior work includes several datasets for the related task of document image binarization, which seeks to convert a document image into a binary image (i.e., where text is black and background is white).
+These document binarization datasets include the DIBCO datasets \cite{dibco-09,dibco-10,dibco-11,dibco-12,dibco-13,dibco-14,dibco-16,dibco-17,dibco-18}.
+As summarized in Table~\ref{tab:datasets}, the DIBCO datasets are very small, ranging between 10 and 20 samples each (for a total of 106 images across DIBCO-9 through DIBCO-18).
+The DIBCO datasets do not contain graphical elements like images, tables, charts, etc.
+A dataset similar to the DIBCO benchmarks is the Persian Heritage Image Binarization Dataset (PHIBD) \cite{phibc-2012-nafchi,nafchi-2013-icdar}, which consists of a small number images of handwritten Persian writing.
+Still others like the Bickley Diary dataset \cite{bickley-diary} and the 2019 Time-Quality Binarization Competition datasets \cite{2019-time-quality-competition} have also been used for benchmarking document binarization approaches, but these do not appear to be publicly available \cite{tensmeyer-binarization-review-2020}.
+Ultimately, the sizes of these document binarization corpora severly limit the types of algorithms and models that can be used.
+
+Other popular document image datasets include large amounts of real noise: These datasets include RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, FUNSD [cite], but these datasets do not have corresponding clean ground-truth document images to train or evaluate document denoisiers.
+
+[TODO: the following could be moved to before this Prior Work section, or into the Construction section.]
+
+%Supervised learning tasks require labeled training data, called the ground truth.
+%Much of the world's data does not come with labels, which instead must be created by humans in some fashion.
+%In Table 1, we indicated that NoisyOffice was the only other groundtruthed dataset we examined.
+%This isn't strictly true: there are projects to add some types of groundtruth to RVL-CDIP \cite{ref_zenodo,ref_goldmann} and Tobacco800 \cite{ref_tobacco800gt2,ref_tobacco800gt1}, but the images in these sets were produced by real scans, without an accompanying original digital document.
+%Conversely, NoisyOffice contains images of real scanned documents intended for validation, as well as their digital groundtruth and synthetic training image data.
 
@@
 
-\subsubsection{NoisyOffice}
-The NoisyOffice database \cite{ref_NoisyOffice} contains a very low 4 base images, 2 types of font, 3 font sizes, and 4 types of noise, for a total of 72 unique images.
-The groundtruth images were produced in a standard word processor, with the simulated noisy images produced by first adding noise to a blank sheet of paper, storing that as a background image after digital scanning, then overlaying the foreground text onto the noisy background texture.
-An additional set of real NoisyOffice images was produced, where the foreground text was printed on blank white sheets, the results of which were physically augmented by the introduction of footprints, coffee stains, wrinkles, and folds.
+%\subsubsection{NoisyOffice}
+%The NoisyOffice database \cite{ref_NoisyOffice} contains a very low 4 base images, 2 types of font, 3 font sizes, and 4 types of noise, for a total of 72 unique images.
+%The groundtruth images were produced in a standard word processor, with the simulated noisy images produced by first adding noise to a blank sheet of paper, storing that as a background image after digital scanning, then overlaying the foreground text onto the noisy background texture.
+%An additional set of real NoisyOffice images was produced, where the foreground text was printed on blank white sheets, the results of which were physically augmented by the introduction of footprints, coffee stains, wrinkles, and folds.
 
@@
 
-\subsection{RVL-CDIP}
-The RVL-CDIP dataset \cite{ref_RVL-CDIP} consists of 400,000 grayscale images divided into 16 document classes, each with a similar number of elements.
-The dataset is pre-segmented into 320,000 training, 40,000 test, and 40,000 validation images, facilitating immediate use in machine learning applications.
-The classes represented are the following:
+%\subsection{RVL-CDIP}
+%The RVL-CDIP dataset \cite{ref_RVL-CDIP} consists of 400,000 grayscale images divided into 16 document classes, each with a similar number of elements.
+%The dataset is pre-segmented into 320,000 training, 40,000 test, and 40,000 validation images, facilitating immediate use in machine learning applications.
+%The classes represented are the following:
 
-\begin{center}
-letter, form, email, handwritten, advertisement, scientific report,
-scientific publication, specification, file folder, news article,
-budget, invoice, presentation, questionnaire, resume, memo.
-\end{center}
+%\begin{center}
+%letter, form, email, handwritten, advertisement, scientific report,
+%scientific publication, specification, file folder, news article,
+%budget, invoice, presentation, questionnaire, resume, memo.
+%\end{center}
 
-The images exhibit poor fidelity with what we can imagine their originals to have been, contain substantial noise, and many were scanned at around 100 pixels per inch, quite a low resolution for documents.
-None of the images in the CDIP set come with groundtruths.
+%The images exhibit poor fidelity with what we can imagine their originals to have been, contain substantial noise, and many were scanned at around 100 pixels per inch, quite a low resolution for documents.
+%None of the images in the CDIP set come with groundtruths.
 
-The collection of RVL-CDIP is an impressive feat in its own right: nearly half a million scanned documents with real noise, already categorized.
-Augraphy makes synthetic documents, intended to simulate real noise without the need to physically produce it.
-One of the augmentations used in the ShabbyPages set is BadPhotoCopy, which mimics low-fidelity noisy or damaged scans.
+%The collection of RVL-CDIP is an impressive feat in its own right: nearly half a million scanned documents with real noise, already categorized.
+%Augraphy makes synthetic documents, intended to simulate real noise without the need to physically produce it.
+%One of the augmentations used in the ShabbyPages set is BadPhotoCopy, which mimics low-fidelity noisy or damaged scans.
 
-\subsection{Tobacco800}
-Tobacco800, like RVL-CDIP, is a subset of the Complex Document Image Processing collection, containing images of documents originally internal to tobacco companies, and released under the Tobacco Master Settlement Agreement.
-The corpus is composed of 1290 images, gathered and scanned at different times and by different devices.
-Several of the images in this set are consecutively-numbered pages, increasing the set's utility for certain image analysis tasks \cite{ref_Tobacco800}.
-Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.
+%\subsection{Tobacco800}
+%Tobacco800, like RVL-CDIP, is a subset of the Complex Document Image Processing collection, containing images of documents originally internal to tobacco companies, and released under the Tobacco Master Settlement Agreement.
+%The corpus is composed of 1290 images, gathered and scanned at different times and by different devices.
+%Several of the images in this set are consecutively-numbered pages, increasing the set's utility for certain image analysis tasks \cite{ref_Tobacco800}.
+%Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.
 

### 2023-02-10 paper/paper.tex

@@
     \centering
-    \caption{Summary of datasets for document denoising and document binarization tasks.}
+    \caption{Summary of datasets for document binarization (above line) and document denoising (below line) tasks.}
     \label{tab:datasets}
@@
             & \rot{80}{\textbf{Diversity}}
-            & \rot{80}{\textbf{Font size}}
-            & \rot{80}{\textbf{Paper styles}}
+            & \rot{80}{\textbf{Mult. font sizes}}
+            & \rot{80}{\textbf{Mult. paper styles}}
             & \rot{80}{\textbf{Multilingual}}
@@
             \midrule
-         ShabbyPages (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & multi~ & multi~ & \cmark & \cmark & \cmark \\
-         NoisyOffice \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & 16pt & 1 & \xmark & \xmark & \xmark \\
-         DocCreator \cite{ref_DocCreator} & & \cmark & \xmark & & & & & &\cmark\\
-         DIBCO-9 \cite{dibco-09} & & & & & & & & & n/a \\
-         DIBCO-10 \cite{dibco-10} & 10 & \xmark & \cmark & & multi & multi & \xmark & \xmark & n/a \\
-         DIBCO-11 \cite{dibco-11} & 16 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a\\
-         DIBCO-12 \cite{dibco-12} & 14 & \xmark & \cmark & & multi & multi & \xmark & \xmark & n/a \\
-         DIBCO-13 \cite{dibco-13} & 16 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
-         H-DIBCO-14 \cite{dibco-14} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
-         H-DIBCO-16 \cite{dibco-16} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
-         DIBCO-17 \cite{dibco-17} & 20 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
-         H-DIBCO-18 \cite{dibco-18} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a\\
-         DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & n/a\\
-         Bickley Diary \cite{bickley-diary} & & & & n/a & & & & & n/a\\
-         PHIBD & & & & & & & & & n/a\\
-         TQBC & & & & & & & & & n/a\\
+         DIBCO-9 \cite{dibco-09} & 10 & \xmark & \cmark &  & \cmark & \cmark & \cmark & \xmark & n/a \\
+         DIBCO-10 \cite{dibco-10} & 10 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
+         DIBCO-11 \cite{dibco-11} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
+         DIBCO-12 \cite{dibco-12} & 14 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
+         DIBCO-13 \cite{dibco-13} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         H-DIBCO-14 \cite{dibco-14} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         H-DIBCO-16 \cite{dibco-16} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         DIBCO-17 \cite{dibco-17} & 20 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         H-DIBCO-18 \cite{dibco-18} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
+         %DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & n/a\\ % SL: I can't find this dataset online
+         Bickley Diary \cite{bickley-diary} & 7 & \xmark & \cmark &  & \xmark & \xmark & \xmark & \xmark & n/a\\
+         PHIBD \cite{nafchi-2013-icdar} & 15 & \xmark & \cmark &  & \cmark & \cmark & \xmark & \xmark & n/a\\
+         %TQBC & & & & & & & & & n/a\\ % SL: I can't find this dataset online
+         \midrule
+         NoisyOffice \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & \cmark & \xmark & \xmark & \xmark & \xmark \\
+         DocCreator \cite{ref_DocCreator} & 6,059 & \cmark & \cmark & & \cmark & \cmark & \cmark & \xmark &\cmark\\
          %LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
-         DDI-100 \cite{ddi-100-2019} & & \cmark & \cmark & & & & & & \xmark\\
+         DDI-100 \cite{ddi-100-2019} & 100k+~ & \cmark & \cmark & & & & & & \xmark\\
+         ShabbyPages (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & \cmark~ & \cmark~ & \cmark & \cmark & \cmark \\
          \bottomrule

### 2023-02-10 paper/paper.tex
other dataset figure
update patch image, narrative changes

--- 2023-02-09 paper/paper.tex
@@
 \section{Introduction}
-%Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, free of noise or other degradations.
-%ShabbyPages is a large dataset composed of 6202 clean/noisy pairs of images taken from 600 digital documents.
-%Information about the set's contents and its relation to other datasets are explored in the next section.
-%The noisy images were created from their clean origins by the application of a pipeline developed with the Augraphy library; the production of ShabbyPages is detailed in the third section, with all source code and input materials made openly available.
-%The final dataset is used to train several denoising models which are compared directly and whose prediction results are compared together in the final section.
-
 Denoising is a fundamental concern for many document processing workflows, wherein unwanted artifacts introduced to a document image via noisy processes like scanning are removed.
@@
 For this reason, procuring a large-enough volume of robust-enough training data is paramount.
-Several sets of such images exist, many intended for processing by deep neural nets; Table 1 below contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.
-
-\begin{table}
-\centering
-\caption{Document Image Dataset Feature Comparison}\label{tab1}
-\begin{tabular}{|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|}
-\hline
-Feature & ShabbyPages & NoisyOffice & RVL-CDIP & Tobacco800 \\
-\hline
-Images & 6202 & 72 & 400000 & 1290\\
-Diversity & 0.488 & 0.317 & & \\
-Document-specific & Yes & Yes & Yes & Yes\\
-Synthetic & Yes & Yes & No & No\\
-Groundtruthed? & Yes & Yes & No & No\\
-Font size & Multiple & 16pt & Multiple & Multiple\\
-Paper styles & Multiple & 1 & Multiple & Multiple\\
-Multilingual & Yes & No & No & No\\
-Documents contain images? & Yes & No & Yes & Yes\\
-Pre-categorized & No & No & Yes & Yes\\
-\hline
-\end{tabular}
-\end{table}
-
-% WIP: this table is a work-in-progress
-\begin{table}[]
-    \centering
-    \caption{Summary of datasets for document denoising and document binarization tasks.}
-    \label{tab:datasets}
-    \begin{tabular}{lcllllllll}
-        \textbf{Dataset} &
-        \rot{80}{\textbf{Dataset Size}}
-            & \rot{80}{\textbf{Synthetic Noise}}
-            & \rot{80}{\textbf{Ground-Truths}}
-            & \rot{80}{\textbf{Diversity}}
-            & \rot{80}{\textbf{Font size}}
-            & \rot{80}{\textbf{Paper styles}}
-            & \rot{80}{\textbf{Multilingual}}
-            & \rot{80}{\textbf{Contains graphics}}
-            & \rot{80}{\textbf{Pre-categorized}} \\
-            \midrule
-         ShabbyPages (ours) & 6,202 & \cmark & \cmark & 0.488 & Multi & Multi & \cmark & \cmark & \xmark \\
-         NoisyOffice \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & 16pt & 1 & \xmark & \xmark & \xmark \\
-         DocCreator & & & & & & & & & \\
-         DIBCO-9 \cite{dibco-09} & & & & & & & & & \\
-         DIBCO-10 \cite{dibco-10} & & & & & & & & & \\
-         DIBCO-11 \cite{dibco-11} & & \xmark & \cmark & & multi & Multi & \cmark & \xmark & \xmark \\
-         DIBCO-12 \cite{dibco-12} & & \xmark & & & & & & & \\
-         DIBCO-13 \cite{dibco-13} & & \xmark & & & & & & & \\
-         H-DIBCO-14 \cite{dibco-14} & & \xmark & & & & & & & \\
-         H-DIBCO-16 \cite{dibco-16} & & \xmark & & & & & & & \\
-         DIBCO-17 \cite{dibco-17} & & \xmark & & & & & & & \\
-         H-DIBCO-18 \cite{dibco-18} & & \xmark & & & & & & & \\
-         DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & \\
-         Bickley Diary \cite{bickley-diary} & & & & & & & & & \\
-         LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
-         \bottomrule
-    \end{tabular}
-\end{table}
+Several sets of such images exist, many intended for processing by deep neural nets; Table \cite{tab:datasets} contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.
 
@@
 
-Table 2 below contains some statistics for the dataset, in grayscale, at a standard resolution of 150 ppi.
+Table \cite{ref:tab1} contains some statistics for the dataset, in grayscale, at a standard resolution of 150 ppi.
 
@@
     \centering
-    \caption{ShabbyPages dataset statistics.}\label{tab1}
+    \caption{ShabbyPages dataset statistics.}
+    \label{tab1}
     \begin{tabular}{@{\hspace{2em}}l@{\qquad}@{\hspace{2em}}l@{\qquad}}
@@
 
-\subsection{ShabbyPages Compared}
-Supervised learning tasks require labeled training data, called the ground truth.
-Much of the world's data does not come with labels, which instead must be created by humans in some fashion.
-In Table 1, we indicated that NoisyOffice was the only other groundtruthed dataset we examined.
-This isn't strictly true: there are projects to add some types of groundtruth to RVL-CDIP \cite{ref_zenodo,ref_goldmann} and Tobacco800 \cite{ref_tobacco800gt2,ref_tobacco800gt1}, but the images in these sets were produced by real scans, without an accompanying original digital document.
-Conversely, NoisyOffice contains images of real scanned documents intended for validation, as well as their digital groundtruth and synthetic training image data.
+\subsection{Other Datasets}
+By now, hundreds of datasets exist for the document denoising task (several listed in \cite{tab:datasets}), the most similar to ShabbyPages being NoisyOffice \cite{ref_NoisyOfficeDatabase}.
+NoisyOffice is very limited, however, consisting of two font weights, three font sizes, three font types, and four noise types, for a total of just 72 unique images.
+The NoisyOffice collection was created by permuting these font/size/base combinations, and the resulting set is feature-poor.
+NoisyOffice also lacks non-English and non-Latin characters, as well as graphical elements like images, logos, and tables.
+To add noise, the creators produced four different types of background noise (folds, wrinkles, coffee stains, and footprints), and then overlayed digitally-generated text onto these.
 
-ShabbyPages includes not only the groundtruth images, but also the original digital documents used to produce them, and the software for fully reproducing the ShabbyPages set, allowing anyone to quickly produce a new set in the Shabby family, optionally re-exporting groundtruths at a different resolution beforehand.
-The 6202 images in the ShabbyPages release set are really just the first sample from the space of these documents; we encourage readers to build their own.
-NoisyOffice is the only other set we examined that contains its digital provenance, but the released database materials lack a means of reproducing the simulated printing method used to create the NoisyOffice training data.
-Augraphy's PaperFactory augmentation is such a tool.
-The other sets are not even theoretically extensible in this way.
+Another dataset, DDI-100 \cite{ddi-100-2019}, was constructed in a manner similar to NoisyOffice.
+DDI-100 is far larger than NoisyOffice, but has been criticized for not containing enough diversity or noise to be an effective benchmark \cite{detection-masking-2022}.
+Additionally, the pipeline code for creating the noisy versions of both NoisyOffice and DDI-100 is not available, and thus these datasets cannot be reproduced.
 
-\subsubsection{NoisyOffice}
-The NoisyOffice database \cite{ref_NoisyOffice} contains a very low 4 base images, 2 types of font, 3 font sizes, and 4 types of noise, for a total of 72 unique images.
-The groundtruth images were produced in a standard word processor, with the simulated noisy images produced by first adding noise to a blank sheet of paper, storing that as a background image after digital scanning, then overlaying the foreground text onto the noisy background texture.
-An additional set of real NoisyOffice images was produced, where the foreground text was printed on blank white sheets, the results of which were physically augmented by the introduction of footprints, coffee stains, wrinkles, and folds.
+\begin{figure}
+    \centering\scalebox{0.4}{
+    \includegraphics{figures/dataset_examples.pdf}}
+    \caption{Example noisy-clean pairs from PHIBD (top row), DIBCO-13 (middle row), and NoisyOffice (bottom row).}
+    \label{fig:other-dataset-examples}
+\end{figure}
 
-ShabbyPages began with 600 documents sourced from the Internet from culturally-important sources.
-A manifest is included in the dataset which contains an ordered table of the filenames, the languages present in the document, the download URL for the file, and an English name or acronym for the source organization or person.
-These documents were split into their constituent pages, which were then passed through an Augraphy pipeline we tuned over a month or two.
-This tuning amounted to tweaking numerical parameters for each of the 24 different augmentations from the Augraphy library.
-All or none of these may have applied to each input image, and only one pipeline run was completed per image.
-Each augmentation has a high degree of internal variability due to several calls to a pseudorandom number generator on which several transforms depend.
-The conjunction of all these factors implies ShabbyPages is a sample from a massive space.
-Indeed, the cosine similarity computed over OpenAI's CLIP representations of each output image averages to 0.49, much higher than NoisyOffice's 0.31.
-Augraphy does not yet have augmentations for footprints or coffee stains, so the dark regions and edges of the stains and prints were simulated with features introduced by other augmentations, but Augraphy does contain the PaperFactory transformation which selects and crops a texture from a local directory of paper images.
-The result of a PaperFactory application is the foreground text ``printed'' onto the background texture, similar to NoisyOffice's construction.
+Other prior work includes several datasets for the related task of document image binarization, which seeks to convert a document image into a binary image, where foreground text is black and background pixels are white.
+Among the most important in this class are the DIBCO collections \cite{dibco-09,dibco-10,dibco-11,dibco-12,dibco-13,dibco-14,dibco-16,dibco-17,dibco-18}.
+As summarized in Table~\ref{tab:datasets}, the DIBCO family of datasets is very small, ranging between 10 and 20 samples each (for a total of 106 images across DIBCO-9 through DIBCO-18).
+Similar to NoisyOffice, the DIBCO datasets do not contain graphical elements like images, tables, charts, etc.
+The Persian Heritage Image Binarization Dataset (PHIBD) \cite{phibc-2012-nafchi,nafchi-2013-icdar} is similar to the DIBCO benchmarks, consisting of a small number of images of handwritten Persian writing.
+Others, like the Bickley Diary set \cite{bickley-diary} and the 2019 Time-Quality Binarization Competition set \cite{2019-time-quality-competition} have also been used for benchmarking document binarization approaches, but these do not appear to be publicly available \cite{tensmeyer-binarization-review-2020}.
+Ultimately, the sizes of these document binarization corpora severly limit the types of algorithms and models that can be used.
+Examples of noisy-clean image pairs from some of these collections are displayed in Figure~\ref{fig:other-dataset-examples}.
 
-\subsection{RVL-CDIP}
-The RVL-CDIP dataset \cite{ref_RVL-CDIP} consists of 400,000 grayscale images divided into 16 document classes, each with a similar number of elements.
-The dataset is pre-segmented into 320,000 training, 40,000 test, and 40,000 validation images, facilitating immediate use in machine learning applications.
-The classes represented are the following:
+Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean ground-truth document images to train or evaluate document denoisiers and binarizers.
 
-\begin{center}
-letter, form, email, handwritten, advertisement, scientific report,
-scientific publication, specification, file folder, news article,
-budget, invoice, presentation, questionnaire, resume, memo.
-\end{center}
-
-The images exhibit poor fidelity with what we can imagine their originals to have been, contain substantial noise, and many were scanned at around 100 pixels per inch, quite a low resolution for documents.
-None of the images in the CDIP set come with groundtruths.
-
-The collection of RVL-CDIP is an impressive feat in its own right: nearly half a million scanned documents with real noise, already categorized.
-Augraphy makes synthetic documents, intended to simulate real noise without the need to physically produce it.
-One of the augmentations used in the ShabbyPages set is BadPhotoCopy, which mimics low-fidelity noisy or damaged scans.
-
-\subsection{Tobacco800}
-Tobacco800, like RVL-CDIP, is a subset of the Complex Document Image Processing collection, containing images of documents originally internal to tobacco companies, and released under the Tobacco Master Settlement Agreement.
-The corpus is composed of 1290 images, gathered and scanned at different times and by different devices.
-Several of the images in this set are consecutively-numbered pages, increasing the set's utility for certain image analysis tasks \cite{ref_Tobacco800}.
-Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.
-
-Every document in the ShabbyPages groundtruth set is a multi-page document.
-The released set was exported at 150 DPI, but the original documents are also distributed, so re-exporting at a higher resolution is trivial.
-The smallest image is 532 by 532, with the largest 3336 wide by 12157 tall.
-6202 images are present in ShabbyPages, but this number could easily be increased by simply running another Augraphy pipeline to generate more; in testing, we rendered several tens of thousands of such images, with the cumulative computation time still less than one day due to Augraphy's efficiency.
+\begin{table}[]
+    \centering
+    \caption{Summary of datasets for document denoising and binarization tasks.}
+    \label{tab:datasets}
+    \begin{tabular}{lcllllllll}
+        \textbf{Dataset} &
+        \rot{80}{\textbf{Dataset Size}}
+            & \rot{80}{\textbf{Synthetic Noise}}
+            & \rot{80}{\textbf{Ground-Truths}}
+            & \rot{80}{\textbf{Diversity}}
+            & \rot{80}{\textbf{Font size}}
+            & \rot{80}{\textbf{Paper styles}}
+            & \rot{80}{\textbf{Multilingual}}
+            & \rot{80}{\textbf{Contains graphics}}
+            & \rot{80}{\textbf{Reproducible}}\\
+            \midrule
+         ShabbyPages (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & multi~ & multi~ & \cmark & \cmark & \cmark \\
+         NoisyOffice \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & 16pt & 1 & \xmark & \xmark & \xmark \\
+         DocCreator \cite{ref_DocCreator} & & \cmark & \xmark & & & & & &\cmark\\
+         DDI-100 \cite{ddi-100-2019} & & \cmark & \cmark & & & & & & \xmark\\
+         DIBCO-9 \cite{dibco-09} & & & & & & & & & n/a \\
+         DIBCO-10 \cite{dibco-10} & 10 & \xmark & \cmark & & multi & multi & \xmark & \xmark & n/a \\
+         DIBCO-11 \cite{dibco-11} & 16 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a\\
+         DIBCO-12 \cite{dibco-12} & 14 & \xmark & \cmark & & multi & multi & \xmark & \xmark & n/a \\
+         DIBCO-13 \cite{dibco-13} & 16 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
+         H-DIBCO-14 \cite{dibco-14} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
+         H-DIBCO-16 \cite{dibco-16} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
+         DIBCO-17 \cite{dibco-17} & 20 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
+         H-DIBCO-18 \cite{dibco-18} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a\\
+         DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & n/a\\
+         Bickley Diary \cite{bickley-diary} & & & & n/a & & & & & n/a\\
+         PHIBD & & & & & & & & & n/a\\
+         TQBC & & & & & & & & & n/a\\
+         %LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
+         \bottomrule
+    \end{tabular}
+\end{table}
 
@@
 
+ShabbyPages was born out of a desire to address shortcomings in the popular datasets discussed in the previous section.
+Reproducibility was a primary concern, so ShabbyPages includes not only the groundtruth images, but also the original digital documents used to produce them, and the software for fully recreating the set, allowing anyone to quickly produce a new member of the Shabby family, optionally re-exporting groundtruths at a different resolution beforehand.
+The 6202 images in the ShabbyPages release set are really just the first sample from the space of these documents; we encourage readers to build their own.
+NoisyOffice is the only other set we examined that contains its digital provenance, but the released database materials lack a means of reproducing the simulated printing method used to create the NoisyOffice training data; Augraphy's \texttt{PaperFactory} augmentation is such a tool.
+The other sets are not even theoretically extensible in this way.
+
 \subsection{Data Gathering}
-A team of workers searched the public internet for PDFs of many different kinds.
+A team of workers searched the public internet for PDFs of many different kinds, from culturally-important sources like government agencies, NGOs, and large multinational corporations.
 600 unique documents were retrieved, totaling 6202 pages.
-A similar process was completed to collect paper textures on which to "print" the documents: 300 unique textures were gathered, all of which are either in the public domain or carry CC-0, CC-BY, or CC-BY-SA licenses.
-Care was taken to retrieve freely-available and attributable documents; a CSV file containing document and paper texture links (as of time of download), with their sources, is available and distributed with the dataset.
+Care was taken to retrieve freely-available and attributable documents; a manifest is included in the dataset which contains an ordered table of the filenames, the languages present in the document, the download URL for the file, and an English name or acronym for the source organization or person.
+A similar process was completed to collect paper textures on which to "print" the documents: 300 unique textures were gathered, all of which are either in the public domain or carry CC-0, CC-BY, or CC-BY-SA licenses; metadata about these textures appears in another manifest.
 We also manually reviewed the gathered documents to verify that no personal identity information was present within the corpus.
@@
 
-The pipeline uses the following augmentations: [TODO: expand]
-BadPhotocopy
-BindingsAndfasteners
-BleedThrough
-DirtyDrum
-Dirtyrollers
-Dithering
-Faxify
-Gamma
-Geometric
-InkBleed
-Jpeg
-Letterpress
-LightingGradient
-LowInkPeriodicLines
-LowInkRandomLines
-Markup
-NoiseTexturize
-PageBorder
-PaperColor
-PaperFactory
-PencilScribbles
-SubtleNoise
+The pipeline uses 23/26 augmentations from Augraphy; we excluded augmentations that would make it hard to do pixel to pixel comparisons against groundtruths.
 
@@
 
+Augraphy by design includes a high degree of randomness: most augmentations make several calls to a pseudorandom number generator, on which several transforms depend.
+All or none of these augmentations may have applied to each input image, and only one pipeline run was completed per image.
+
+The conjunction of all these factors implies ShabbyPages is a sample from a massive space.
+Indeed, the cosine similarity computed over OpenAI's CLIP representations of each output image averages to 0.49, much higher than NoisyOffice's 0.31.
+
 \subsection{Processing Augraphy on a multicore system}
-Execution time is dependent on which augmentations are executed at runtime; an Augraphy pipeline can take several seconds to process large images.
+Execution time is dependent on which augmentations are executed at runtime; a long Augraphy pipeline can take several seconds to process large images.
 The library is under active development with performance enhancements underway, but the time cost to generate large datasets sequentially is prohibitive when dealing with thousands of files, so we use a multi-process pooling technique to distribute the workload across many processor execution threads.
-For each process, we generate a new pipeline, run the pipeline object on an image, and save the output, using the code below: [TODO: can we cut this down to just the pipeline function?]
+For each process, a new pipeline with new probability coefficients was generated, representing a nontrivially-different sequence of document operations.
+Each of the 6202 base images was passed through a unique pipeline, with the output saved to a separate directory.
+Augraphy's API design made it very easy to write the code to accomplish this; the entire ShabbyPages generation script is fewer than 30 lines long including imports, with the most critical piece represented below:
 
 \begin{lstlisting}[language=Python]
-    import os
-    import cv2
-    from multiprocessing import Pool
-    from pathlib import Path
-
-    input_path = Path("/path/to/input/images")
-    filenames = [(input_path / name)
-      for name
-      in os.listdir(input_path)]
-
-    pool = Pool(os.cpu_count())
-
   def run_pipeline(filename):
     image = cv2.imread(filename)
-        # returns the current Shabby Pages pipeline
+    # returns the current ShabbyPages pipeline
     pipeline = get_pipeline()
     data = pipeline.augment(image)
-        shabby_image = data["output"]
-        cv2.imwrite(filename.parent / f"{filename.stem}-shabby{filename.suffix}")
-
-    pool.map(run_pipeline, filenames)
-
+    shabby_image = data['output']
+    cv2.imwrite(filename + '-shabby.png',
+                shabby_image)
 \end{lstlisting}
@@
 Processing all 6202 images took less than half an hour on the 64 cores of a Graviton3 c7g.16xlarge instance on AWS.
+In testing, we rendered several tens of thousands of such images, with the cumulative computation time still less than one day due to Augraphy's efficiency.
+
+\subsection{Real Shabby Pages}
+In keeping with the spirit of NoisyOffice, our original inspiration, and to provide out-of-distribution test data for ours and other projects, we developed a separate but related dataset which we call ShabbyReal.
+To build this, we isolated reproduction steps for several physical operations, designed real-world augmentation pipelines with these, and then engaged a team of workers to use these instructions to produce several copies of printed born-digital documents with real noise.
+
+Five individuals were recruited for this task, which involved printing 40 pages of documents and manually applying various effects such as folds, wrinkles, smudges, highlighters, pencils, crayons, splatters of ink or other liquids, printing, scanning, faxing and other creative and reasonable treatments determined by these workers.
+The process continued over a period of two weeks, incurring a cost of approximately $1,000 USD.
+While there are plenty of opportunities to streamline the operation, scaling this process is expensive in terms of both time and money, and may have unpredictable results.
+
+Several challenges arose in the construction of this dataset.
+Old fax machines, faulty commercial printers, and other hardware suitable for inducing the intended effects were difficult to source, and frequently non-functional when they could be found.
+Environmental concerns like the volume of paper and ink used, and the energy expenditure both in electricity and human terms, also factored into our decision to pursue synthetic augmentations for ShabbyPages.
+Manually producing a database of noisy documents is a time-consuming and repetitive task; creating just 100 real-world documents with real noise features required the labor of several people.
+Nevertheless, despite the limited size of the resulting dataset, the scarcity of real-world datasets with ground truth images makes the ShabbyReal corpus extremely valuable.
+This type of dataset is critical for benchmark comparison with synthetically-augmented document images, and for other tasks such as denoising and binarizing: we use ShabbyReal later for a human-perception evaluation of denoising performance.
 
 \section{Experimentation with the ShabbyPages Set}
-Binarization and denoising are two important techniques for the removal of unwanted data from images.
+Denoising and binarization are two important techniques for the removal of unwanted data from images.
 Both approaches can be achieved by supervised learning of relationships between features of the input and output data.
@@
 We evaluate these models' predictions in a cross-validation test on both datasets, both by visual inspection and by metric computation.
+We then perform a similar experiment where the same NAFNets are trained to not only remove noise from the test images, but also to classify the foreground and backgorund pixels, predicting a binarized clean document.
 The model was ``off-the-shelf''; besides rigging up the training inputs and choosing a reasonable training epoch limit, we made no significant alterations to the provided hyperparameters.
 
-\subsection{Binarization} [TODO: do we want to throw this away? It's still an important part of the story]
-In this section, we discuss results obtained by training a denoiser to both restore augmented images to their ground truths and to classify pixels as foreground.
+\subsection{Denoising}
+Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it.
+Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, and perhaps most importantly, when our aesthetic sensibilities are un-challenged.
 
-We first performed an ensemble binarization preprocessing step on the clean groundtruth images.
-For each image, we computed the Niblack, Sauvola, and Otsu thresholds, using these to binarize three copies of the input.
-The average over the resulting matrices was taken elementwise, producing the final binarized groundtruth.
-
-One instance of the model was trained on the full SimulatedNoisyOffice corpus, while the other was trained on a 1050-image subset of ShabbyPages, cropped to a random 500x500 patch.
-In both cases, the prediction target was the relevant ensemble-binarized groundtruths, and each instance trained for 100 epochs.
-As a test, these models were used to denoise and binarize both the NoisyOfficeReal dataset and a testing subset taken from ShabbyPages which does not overlap the training subset.
-[TODO: Can we get the metrics for ShabbyReal instead?]
-Common image processing metrics were applied to the predictions made by each model, comparing these to the (preprocessed) groundtruths.
-The averages of each metric over all such predictions was taken; these are presented in Table 2.
+Denoising grayscale images is a challenging task, as models must determine not only which features should appear in the output, but also the 8-bit pixel intensity over the whole image.
+We randomly selected ten patches of 400x400 pixels from each page, then trained another NAFNet instance on this data for just 14 epochs (about 22 hours of compute time).
+For this task, we considered the structural similarity index (SSIM), a common image processing metric which takes into account visually-perceptible data such as luminance and contrast, appropriate for grayscale images.
+The results of the denoising cross-validation experiment are presented in the table below.
 
@@
     \centering
-    \caption{Document image *binarization* performance of a NAFNet model trained and tested on ShabbyPages and NoisyOffice.}
+    \caption{Document image denoising cross-test performance of NAFNet models trained on ShabbyPages and NoisyOffice.}
     \scalebox{0.9}{
@@
         \midrule
-        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & 0.947\\
-        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811\\
-        \bottomrule
-    \end{tabular}}
-    \label{tab:binarization_results}
-\end{table}
-
-The ShabbyPages-trained model was able to classify foreground and background pixels with a substantially higher degree of accuracy than the NoisyOffice-trained model, even with arguably worse training data.
-
-\subsection{Denoising}
-Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it.
-Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, and when our aesthetic sensibilities are un-challenged.
-
-Denoising grayscale images is a considerably harder task than binarization, as the space of possible predictions for a pixel value increases from one to eight bits (black/white to 256 shades of gray).
-To offset this increased difficulty, we randomly selected ten patches of 400x400 pixels from each page, then trained another NAFNet instance on this data for 1000 epochs.
-The results of a denoising experiment are presented in the table below.
-
-\begin{table}[]
-    \centering
-    \caption{Document image *denoising* cross-test performance of NAFNet models trained on ShabbyPages and NoisyOffice.}
-    \scalebox{0.9}{
-    \begin{tabular}{lll}
-    \toprule
-    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~}\\
-        \midrule
-        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & 0.950\\
+        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & \textbf{0.96}\\
         \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.83\\
@@
 
-\subsubsection{Interpretation} [TODO: roll this into the previous section and/or delete most of it]
-As a baseline, we first evaluated the models against test sets associated with their training databases; the model trained on SimulatedNoisyOffice was used to enhance the RealNoisyOffice set, while the ShabbyPages-trained model cleaned a testing subset drawn from the full ShabbyPages set.
+Machine learning is ultimately about getting computers to complete tasks which normally require human labor; as further validation for the efficacy of ShabbyPages in training performant denoisers, we also used our ShabbyPages-trained NAFNet model to denoise the ShabbyReal set, and present some examples of its performance below.
 
-We considered the structural similarity index, a common image processing metric.
+\begin{figure}
+\centering
+\includegraphics[width=0.98\columnwidth, frame]{figures/shabbyreal_denoising.png}
+\caption{Sample ShabbyReal images and their Shabby\_NAFNet-denoised versions.}
+\label{fig:shabbyreal_denoising}
+\end{figure}
 
-Although the ShabbyPages-trained NAFNet predicted cleaned ShabbyPages images with a lower structural similarity score than the NoisyOffice-trained model predicted cleaned RealNoisyOffice images, the ShabbyPages model achieved superior performance on RMSE and PSNR.
-The ShabbyPages corpus contains a much higher feature diversity than NoisyOffice, so the lower SSIM score was not unexpected; local relationships between pixels were easier to encode for the NoisyOffice model, possibly because there are simply fewer relationships.
-The RMSE and PSNR results on the other hand indicate that the ShabbyPages-trained model learned to remove more noise with higher fidelity, and more accurately predicted foreground pixels than the NoisyOffice model.
-This discrepancy can partly be explained by the RealNoisyOffice corpus having been physically-noised as opposed to ShabbyPages' purely synthetic noise; small-scale features in the RealNoisyOffice testing data are not quite identical to the SimulatedNoisyOffice training inputs, while both the training and testing data taken from ShabbyPages was constructed by the same means.
-In the latter case, the \textit{diversity} of the ShabbyPages data is much higher (TODO: add diversity score info), and this instance of the NAFNet may have been able to generalize over noise types better than the NoisyOffice-trained network with its lower training diversity.
+\subsection{Binarization}
+In this section, we discuss results obtained by training a NAFNet denoiser to both restore augmented images to their ground truths and to classify pixels as foreground.
 
-The second stage of the binarization experiment was to cross-validate these models by predicting cleaned images using the other testing set as inputs.
-Here, the ShabbyPages-trained model achieved all-around better performance than the NoisyOffice-trained model, with a much higher structural similarity score (0.947 vs.
-0.811), lower RMSE, and higher PSNR.
+We first performed an ensemble binarization preprocessing step on the clean groundtruth images.
+For each image, we computed the Niblack, Sauvola, and Otsu thresholds, using these to binarize three copies of the input.
+The average over the resulting matrices was taken elementwise, producing the final binarized groundtruth.
+
+One instance of the model was trained on the full SimulatedNoisyOffice corpus, while the other was trained on a 1050-image subset of ShabbyPages, cropped to a single random 500x500 patch.
+In both cases, the prediction target was the relevant ensemble-binarized groundtruths, and each instance trained for 100 epochs.
+As a test, these models were used to denoise and binarize both the full NoisyOfficeReal dataset and a 450-image testing subset taken from ShabbyPages which does not overlap the training subset.
+
+Multiple common image processing metrics were applied to the predictions made by each model, comparing these to the preprocessed groundtruths.
+In addition to the structural similarity metric from the denoising task, we add the peak signal to noise ratio (PSNR) and the root mean squared error (RMSE).
+Both of these metrics are more useful for determining the differences between binary images: together, they give some idea of the degree to which noise artifacts remain in the image after denoizing and binarization affect the visual signal, and how many such artifacts exist.
+The averages of each metric over all predictions was taken, with the results presented in Table \cite{tab:binarization_results}.
+
+\begin{table}[]
+    \centering
+    \caption{Document image binarization performance of a NAFNet model trained and tested on ShabbyPages and NoisyOffice.}
+    \scalebox{0.9}{
+    \begin{tabular}{lllll}
+    \toprule
+    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{PSNR$\downarrow$~} \textbf{RMSE$\downarrow$~}\\
+        \midrule
+        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & \textbf{0.947} & \textbf{38.098} & \textbf{3.205}\\
+        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811 & 34.562 & 5.384\\
+        \bottomrule
+    \end{tabular}}
+    \label{tab:binarization_results}
+\end{table}
+
+We cross-validate these models by predicting cleaned and binarized images using the other testing set as inputs.
+The ShabbyPages-trained model was able to classify foreground and background pixels in the NoisyOffice test set with a substantially higher degree of accuracy than the NoisyOffice-trained model could classify ShabbyPages, even with less-favorable training data.
+ShabbyPages contains a much higher feature diversity than NoisyOffice, so these results were unsurprising, although we did expect our model to achieve worse results than it did, since it only saw a single patch from each full page.
+The ShabbyPages-trained model performs well on a much wider range of features, handling tables, graphs, and even simple images quite well.
 This is a strong indicator that neural networks trained on ShabbyPages can outperform those trained on NoisyOffice when generalizing to other datasets.
 
-Interestingly, the NoisyOffice-trained model RMSE and PSNR scores were lower when cleaning RealNoisyOffice than the Shabby-trained model: we were able to achieve a 3.5 decibel improvement in peak signal-to-noise ratio over the SimulatedNoisyOffice-trained model.
-
-\section{Real Shabby Pages}
-In keeping with the spirit of NoisyOffice, our original inspiration, and to provide out-of-distribution test data for other projects, we developed a separate but related dataset which we call Real ShabbyPages.
-To build this, we isolated reproduction steps for several physical operations, designed real-world augmentation pipelines with these, and then engaged a team of workers to use these instructions to produce several copies of printed born-digital documents with real noise.
-
-Several challenges arose in the construction of this dataset.
-Manually producing a database of noisy documents is a time-consuming and repetitive task; creating just 100 real-world documents with real noise features required the labor of several people.
-Old fax machines, faulty commercial printers, and other hardware suitable for inducing the intended effects were difficult to find.
-Environmental concerns like the volume of paper and ink used, or the energy expenditure, also factored into our decision to pursue synthetic augmentations for ShabbyPages.
+\section{Conclusion}
+Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, free of noise or other degradations.
+We presented ShabbyPages, a large dataset composed of 6202 clean/noisy pairs of synthetically-noisy images taken from 600 digital documents.
+Information about the set's contents and its relation to other common datasets was explored.
+The noisy images were created from their clean origins by the application of a pipeline developed with the \texttt{Augraphy} library; the production of ShabbyPages was detailed in the third section, with all source code and input materials made openly available.
+ShabbyPages was used to train performant denoising and binarization models which generalize well to document images containing real noise.
 

### 2023-02-10 paper/paper.tex
Minor formatting updates to augraphy, shabby and noisy references

@@
 \begin{abstract}
-The ShabbyPages document image dataset is produced using the Augraphy document image augmentation tool.
+The \emph{ShabbyPages} document image dataset is produced using the \emph{Augraphy} document image augmentation tool.
 The development of the computation pipeline used to generate the corpus is discussed, and the results presented.
@@
 The release of this dataset and the recipe for its production attempts to address a growing need for labeled training document images for supervised learning tasks.
-The results of initial experiments are discussed, in which the corpus is used to train performant convolutional denoisers which remove real noise features with a high degree of human-perceptible fidelity, establishing baseline performance for a new ShabbyPages benchmark.
+The results of initial experiments are discussed, in which the corpus is used to train performant convolutional denoisers which remove real noise features with a high degree of human-perceptible fidelity, establishing baseline performance for a new \emph{ShabbyPages} benchmark.
 \end{abstract}
@@
 \item The DIBCO datasets — widely recognized as critical data for document denoising and binarization — are far too small for large-scale training; each DIBCO dataset ranges between 10-20 images total.
-\item The NoisyOffice denoising dataset \cite{ref_NoisyOfficeDatabase} is also quite small, having \emph{72} training samples, and contains only a few types of noise — primarily artificial wrinkles and stains, with little variation.
-\item The DDI-100 corpus \cite{ddi-100-2019} is larger in scale than NoisyOffice and the DIBCO datasets, but is again limited in the degree of feature diversity \cite{detection-masking-2022}.
+\item The \emph{NoisyOffice} denoising dataset \cite{ref_NoisyOfficeDatabase} is also quite small, having \emph{72} training samples, and contains only a few types of noise — primarily artificial wrinkles and stains, with little variation.
+\item The DDI-100 corpus \cite{ddi-100-2019} is larger in scale than \emph{NoisyOffice} and the DIBCO datasets, but is again limited in the degree of feature diversity \cite{detection-masking-2022}.
 \end{itemize}
@@
 This new dataset, \emph{ShabbyPages}, is large-scale, having \emph{6202} training and \emph{mmm} [TODO: do we need this?] testing samples.
-\emph{ShabbyPages} is more diverse than alternatives like NoisyOffice, as it contains documents from various language groups and contains documents with graphical elements like tables and figures.
-In the next sections, we provide motivation and context for ShabbyPages' creation, compare it at length to other important datasets in the same space, describe the corpus construction process, and finally demonstrate its utility by benchmarking document denoising models trained on the dataset.
+\emph{ShabbyPages} is more diverse than alternatives like \emph{NoisyOffice}, as it contains documents from various language groups and contains documents with graphical elements like tables and figures.
+In the next sections, we provide motivation and context for \emph{ShabbyPages}' creation, compare it at length to other important datasets in the same space, describe the corpus construction process, and finally demonstrate its utility by benchmarking document denoising models trained on the dataset.
 
@@
 \includegraphics[width=0.98\columnwidth, frame]{figures/matrix.png}
-\caption{Sample patches from ShabbyPages.} \label{fig1}
+\caption{Sample patches from \emph{ShabbyPages}.} \label{fig1}
 \end{figure}
@@
 \section{The Dataset}
-ShabbyPages joins a rapidly growing number of open-source datasets freely available online.
+\emph{ShabbyPages} joins a rapidly growing number of open-source datasets freely available online.
 Human activity today generates a tremendous amount of data, with many people choosing to publish theirs on websites like Kaggle \cite{ref_Kaggle}, Hugging Face Hub \cite{ref_HuggingFaceHub}, and many more.
@@
 Of the many image datasets available, the authors understand few to have been designed for groundtruthed supervised learning of document-specific tasks like binarization or denoising.
-In fact, we could find only one other set compiled specifically for doing so with images of \textit{modern} documents: NoisyOffice \cite{ref_NoisyOffice}.
+In fact, we could find only one other set compiled specifically for doing so with images of \textit{modern} documents: \emph{NoisyOffice} \cite{ref_NoisyOffice}.
 
@@
 For this reason, procuring a large-enough volume of robust-enough training data is paramount.
-Several sets of such images exist, many intended for processing by deep neural nets; Table \cite{tab:datasets} contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.
+Several sets of such images exist, many intended for processing by deep neural nets; Table \cite{tab:datasets} contains a comparison of some of the key hyperproperties of the \emph{ShabbyPages} set compared with other popular document image datasets.
 
@@
 \subsection{Statistics}
-ShabbyPages contains documents from multiple classes, which contain many types of information.
+\emph{ShabbyPages} contains documents from multiple classes, which contain many types of information.
 
@@
 \subsection{Other Datasets}
-By now, hundreds of datasets exist for the document denoising task (several listed in \cite{tab:datasets}), the most similar to ShabbyPages being NoisyOffice \cite{ref_NoisyOfficeDatabase}.
-NoisyOffice is very limited, however, consisting of two font weights, three font sizes, three font types, and four noise types, for a total of just 72 unique images.
-The NoisyOffice collection was created by permuting these font/size/base combinations, and the resulting set is feature-poor.
-NoisyOffice also lacks non-English and non-Latin characters, as well as graphical elements like images, logos, and tables.
+By now, hundreds of datasets exist for the document denoising task (several listed in \cite{tab:datasets}), the most similar to \emph{ShabbyPages} being \emph{NoisyOffice} \cite{ref_NoisyOfficeDatabase}.
+\emph{NoisyOffice} is very limited, however, consisting of two font weights, three font sizes, three font types, and four noise types, for a total of just 72 unique images.
+The \emph{NoisyOffice} collection was created by permuting these font/size/base combinations, and the resulting set is feature-poor.
+\emph{NoisyOffice} also lacks non-English and non-Latin characters, as well as graphical elements like images, logos, and tables.
 To add noise, the creators produced four different types of background noise (folds, wrinkles, coffee stains, and footprints), and then overlayed digitally-generated text onto these.
 
-Another dataset, DDI-100 \cite{ddi-100-2019}, was constructed in a manner similar to NoisyOffice.
-DDI-100 is far larger than NoisyOffice, but has been criticized for not containing enough diversity or noise to be an effective benchmark \cite{detection-masking-2022}.
-Additionally, the pipeline code for creating the noisy versions of both NoisyOffice and DDI-100 is not available, and thus these datasets cannot be reproduced.
+Another dataset, DDI-100 \cite{ddi-100-2019}, was constructed in a manner similar to \emph{NoisyOffice}.
+DDI-100 is far larger than \emph{NoisyOffice}, but has been criticized for not containing enough diversity or noise to be an effective benchmark \cite{detection-masking-2022}.
+Additionally, the pipeline code for creating the noisy versions of both \emph{NoisyOffice} and DDI-100 is not available, and thus these datasets cannot be reproduced.
 
@@
     \includegraphics{figures/dataset_examples.pdf}}
-    \caption{Example noisy-clean pairs from PHIBD (top row), DIBCO-13 (middle row), and NoisyOffice (bottom row).}
+    \caption{Example noisy-clean pairs from PHIBD (top row), DIBCO-13 (middle row), and \emph{NoisyOffice} (bottom row).}
     \label{fig:other-dataset-examples}
@@
 As summarized in Table~\ref{tab:datasets}, the DIBCO family of datasets is very small, ranging between 10 and 20 samples each (for a total of 106 images across DIBCO-9 through DIBCO-18).
-Similar to NoisyOffice, the DIBCO datasets do not contain graphical elements like images, tables, charts, etc.
+Similar to \emph{NoisyOffice}, the DIBCO datasets do not contain graphical elements like images, tables, charts, etc.
 The Persian Heritage Image Binarization Dataset (PHIBD) \cite{phibc-2012-nafchi,nafchi-2013-icdar} is similar to the DIBCO benchmarks, consisting of a small number of images of handwritten Persian writing.
@@
             \midrule
-         ShabbyPages (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & multi~ & multi~ & \cmark & \cmark & \cmark \\
-         NoisyOffice \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & 16pt & 1 & \xmark & \xmark & \xmark \\
+         \emph{ShabbyPages} (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & multi~ & multi~ & \cmark & \cmark & \cmark \\
+         \emph{NoisyOffice} \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & 16pt & 1 & \xmark & \xmark & \xmark \\
          DocCreator \cite{ref_DocCreator} & & \cmark & \xmark & & & & & &\cmark\\
@@
 
-ShabbyPages was born out of a desire to address shortcomings in the popular datasets discussed in the previous section.
-Reproducibility was a primary concern, so ShabbyPages includes not only the groundtruth images, but also the original digital documents used to produce them, and the software for fully recreating the set, allowing anyone to quickly produce a new member of the Shabby family, optionally re-exporting groundtruths at a different resolution beforehand.
-The 6202 images in the ShabbyPages release set are really just the first sample from the space of these documents; we encourage readers to build their own.
-NoisyOffice is the only other set we examined that contains its digital provenance, but the released database materials lack a means of reproducing the simulated printing method used to create the NoisyOffice training data; Augraphy's \texttt{PaperFactory} augmentation is such a tool.
+\emph{ShabbyPages} was born out of a desire to address shortcomings in the popular datasets discussed in the previous section.
+Reproducibility was a primary concern, so \emph{ShabbyPages} includes not only the groundtruth images, but also the original digital documents used to produce them, and the software for fully recreating the set, allowing anyone to quickly produce a new member of the Shabby family, optionally re-exporting groundtruths at a different resolution beforehand.
+The 6202 images in the \emph{ShabbyPages} release set are really just the first sample from the space of these documents; we encourage readers to build their own.
+\emph{NoisyOffice} is the only other set we examined that contains its digital provenance, but the released database materials lack a means of reproducing the simulated printing method used to create the \emph{NoisyOffice} training data; \emph{Augraphy}'s \texttt{PaperFactory} augmentation is such a tool.
 The other sets are not even theoretically extensible in this way.
@@
 \subsection{Developing the Pipeline}
-The Augraphy library presents an easy-to-use API for constructing feature pipelines, which has been designed for interoperability with other augmentation tools, and within the broader data ecosystem.
-While Augraphy's default pipeline has what we believe to be quite realistic defaults, we wanted a broader range of features from this dataset than those the default pipeline could produce.
+The \emph{Augraphy} library presents an easy-to-use API for constructing feature pipelines, which has been designed for interoperability with other augmentation tools, and within the broader data ecosystem.
+While \emph{Augraphy}'s default pipeline has what we believe to be quite realistic defaults, we wanted a broader range of features from this dataset than those the default pipeline could produce.
 To address this, we broke all of the parameters for every augmentation constructor out into separate variables, tweaking these and committing the new pipeline to GitHub.
@@
 
-The pipeline uses 23/26 augmentations from Augraphy; we excluded augmentations that would make it hard to do pixel to pixel comparisons against groundtruths.
+The pipeline uses 23/26 augmentations from \emph{Augraphy}; we excluded augmentations that would make it hard to do pixel to pixel comparisons against groundtruths.
 
@@
 
-Augraphy by design includes a high degree of randomness: most augmentations make several calls to a pseudorandom number generator, on which several transforms depend.
+\emph{Augraphy} by design includes a high degree of randomness: most augmentations make several calls to a pseudorandom number generator, on which several transforms depend.
 All or none of these augmentations may have applied to each input image, and only one pipeline run was completed per image.
 
-The conjunction of all these factors implies ShabbyPages is a sample from a massive space.
-Indeed, the cosine similarity computed over OpenAI's CLIP representations of each output image averages to 0.49, much higher than NoisyOffice's 0.31.
+The conjunction of all these factors implies \emph{ShabbyPages} is a sample from a massive space.
+Indeed, the cosine similarity computed over OpenAI's CLIP representations of each output image averages to 0.49, much higher than \emph{NoisyOffice}'s 0.31.
 
-\subsection{Processing Augraphy on a multicore system}
-Execution time is dependent on which augmentations are executed at runtime; a long Augraphy pipeline can take several seconds to process large images.
+\subsection{Processing \emph{Augraphy} on a multicore system}
+Execution time is dependent on which augmentations are executed at runtime; a long \emph{Augraphy} pipeline can take several seconds to process large images.
 The library is under active development with performance enhancements underway, but the time cost to generate large datasets sequentially is prohibitive when dealing with thousands of files, so we use a multi-process pooling technique to distribute the workload across many processor execution threads.
@@
 Each of the 6202 base images was passed through a unique pipeline, with the output saved to a separate directory.
-Augraphy's API design made it very easy to write the code to accomplish this; the entire ShabbyPages generation script is fewer than 30 lines long including imports, with the most critical piece represented below:
+\emph{Augraphy}'s API design made it very easy to write the code to accomplish this; the entire \emph{ShabbyPages} generation script is fewer than 30 lines long including imports, with the most critical piece represented below:
 
@@
 Processing all 6202 images took less than half an hour on the 64 cores of a Graviton3 c7g.16xlarge instance on AWS.
-In testing, we rendered several tens of thousands of such images, with the cumulative computation time still less than one day due to Augraphy's efficiency.
+In testing, we rendered several tens of thousands of such images, with the cumulative computation time still less than one day due to \emph{Augraphy}'s efficiency.
 
-\subsection{Real Shabby Pages}
-In keeping with the spirit of NoisyOffice, our original inspiration, and to provide out-of-distribution test data for ours and other projects, we developed a separate but related dataset which we call ShabbyReal.
+\subsection{\emph{ShabbyPages}}
+In keeping with the spirit of \emph{NoisyOffice}, our original inspiration, and to provide out-of-distribution test data for ours and other projects, we developed a separate but related dataset which we call \emph{ShabbyPages}.
 To build this, we isolated reproduction steps for several physical operations, designed real-world augmentation pipelines with these, and then engaged a team of workers to use these instructions to produce several copies of printed born-digital documents with real noise.
@@
 Old fax machines, faulty commercial printers, and other hardware suitable for inducing the intended effects were difficult to source, and frequently non-functional when they could be found.
-Environmental concerns like the volume of paper and ink used, and the energy expenditure both in electricity and human terms, also factored into our decision to pursue synthetic augmentations for ShabbyPages.
+Environmental concerns like the volume of paper and ink used, and the energy expenditure both in electricity and human terms, also factored into our decision to pursue synthetic augmentations for \emph{ShabbyPages}.
 Manually producing a database of noisy documents is a time-consuming and repetitive task; creating just 100 real-world documents with real noise features required the labor of several people.
-Nevertheless, despite the limited size of the resulting dataset, the scarcity of real-world datasets with ground truth images makes the ShabbyReal corpus extremely valuable.
-This type of dataset is critical for benchmark comparison with synthetically-augmented document images, and for other tasks such as denoising and binarizing: we use ShabbyReal later for a human-perception evaluation of denoising performance.
+Nevertheless, despite the limited size of the resulting dataset, the scarcity of real-world datasets with ground truth images makes the \emph{ShabbyPages} corpus extremely valuable.
+This type of dataset is critical for benchmark comparison with synthetically-augmented document images, and for other tasks such as denoising and binarizing: we use \emph{ShabbyPages} later for a human-perception evaluation of denoising performance.
 
-\section{Experimentation with the ShabbyPages Set}
+\section{Experimentation with the \emph{ShabbyPages} Set}
 Denoising and binarization are two important techniques for the removal of unwanted data from images.
 Both approaches can be achieved by supervised learning of relationships between features of the input and output data.
-In this section, we train two NAFNet \cite{ref_nafnet} instances as denoisers on both the NoisyOffice and the ShabbyPages datasets.
+In this section, we train two NAFNet \cite{ref_nafnet} instances as denoisers on both the \emph{NoisyOffice} and the \emph{ShabbyPages} datasets.
 We evaluate these models' predictions in a cross-validation test on both datasets, both by visual inspection and by metric computation.
@@
     \centering
-    \caption{Document image denoising cross-test performance of NAFNet models trained on ShabbyPages and NoisyOffice.}
+    \caption{Document image denoising cross-test performance of NAFNet models trained on \emph{ShabbyPages} and \emph{NoisyOffice}.}
     \scalebox{0.9}{
@@
 
-As can be seen from Table \cite{tab:denoising_results}, the ShabbyPages-trained denoiser generalized to NoisyOffice far better than the NoisyOffice-trained model generalized to ShabbyPages.
-This result is consistent with the much higher diversity present within the ShabbyPages set, relative to features found in the NoisyOffice database.
+As can be seen from Table \cite{tab:denoising_results}, the \emph{ShabbyPages}-trained denoiser generalized to \emph{NoisyOffice} far better than the \emph{NoisyOffice}-trained model generalized to \emph{ShabbyPages}.
+This result is consistent with the much higher diversity present within the \emph{ShabbyPages} set, relative to features found in the \emph{NoisyOffice} database.
 
-Machine learning is ultimately about getting computers to complete tasks which normally require human labor; as further validation for the efficacy of ShabbyPages in training performant denoisers, we also used our ShabbyPages-trained NAFNet model to denoise the ShabbyReal set, and present some examples of its performance below.
+Machine learning is ultimately about getting computers to complete tasks which normally require human labor; as further validation for the efficacy of \emph{ShabbyPages} in training performant denoisers, we also used our \emph{ShabbyPages}-trained NAFNet model to denoise the \emph{ShabbyPages} set, and present some examples of its performance below.
 
@@
 \includegraphics[width=0.98\columnwidth, frame]{figures/shabbyreal_denoising.png}
-\caption{Sample ShabbyReal images and their Shabby\_NAFNet-denoised versions.}
+\caption{Sample \emph{ShabbyPages} images and their Shabby\_NAFNet-denoised versions.}
 \label{fig:shabbyreal_denoising}
@@
 
-One instance of the model was trained on the full SimulatedNoisyOffice corpus, while the other was trained on a 1050-image subset of ShabbyPages, cropped to a single random 500x500 patch.
+One instance of the model was trained on the full SimulatedNoisyOffice corpus, while the other was trained on a 1050-image subset of \emph{ShabbyPages}, cropped to a single random 500x500 patch.
 In both cases, the prediction target was the relevant ensemble-binarized groundtruths, and each instance trained for 100 epochs.
-As a test, these models were used to denoise and binarize both the full NoisyOfficeReal dataset and a 450-image testing subset taken from ShabbyPages which does not overlap the training subset.
+As a test, these models were used to denoise and binarize both the full NoisyOfficeReal dataset and a 450-image testing subset taken from \emph{ShabbyPages} which does not overlap the training subset.
 
@@
     \centering
-    \caption{Document image binarization performance of a NAFNet model trained and tested on ShabbyPages and NoisyOffice.}
+    \caption{Document image binarization performance of a NAFNet model trained and tested on \emph{ShabbyPages} and \emph{NoisyOffice}.}
     \scalebox{0.9}{
@@
 We cross-validate these models by predicting cleaned and binarized images using the other testing set as inputs.
-The ShabbyPages-trained model was able to classify foreground and background pixels in the NoisyOffice test set with a substantially higher degree of accuracy than the NoisyOffice-trained model could classify ShabbyPages, even with less-favorable training data.
-ShabbyPages contains a much higher feature diversity than NoisyOffice, so these results were unsurprising, although we did expect our model to achieve worse results than it did, since it only saw a single patch from each full page.
-The ShabbyPages-trained model performs well on a much wider range of features, handling tables, graphs, and even simple images quite well.
-This is a strong indicator that neural networks trained on ShabbyPages can outperform those trained on NoisyOffice when generalizing to other datasets.
+The \emph{ShabbyPages}-trained model was able to classify foreground and background pixels in the \emph{NoisyOffice} test set with a substantially higher degree of accuracy than the \emph{NoisyOffice}-trained model could classify \emph{ShabbyPages}, even with less-favorable training data.
+\emph{ShabbyPages} contains a much higher feature diversity than \emph{NoisyOffice}, so these results were unsurprising, although we did expect our model to achieve worse results than it did, since it only saw a single patch from each full page.
+The \emph{ShabbyPages}-trained model performs well on a much wider range of features, handling tables, graphs, and even simple images quite well.
+This is a strong indicator that neural networks trained on \emph{ShabbyPages} can outperform those trained on \emph{NoisyOffice} when generalizing to other datasets.
 
@@
 Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, free of noise or other degradations.
-We presented ShabbyPages, a large dataset composed of 6202 clean/noisy pairs of synthetically-noisy images taken from 600 digital documents.
+We presented \emph{ShabbyPages}, a large dataset composed of 6202 clean/noisy pairs of synthetically-noisy images taken from 600 digital documents.
 Information about the set's contents and its relation to other common datasets was explored.
-The noisy images were created from their clean origins by the application of a pipeline developed with the \texttt{Augraphy} library; the production of ShabbyPages was detailed in the third section, with all source code and input materials made openly available.
-ShabbyPages was used to train performant denoising and binarization models which generalize well to document images containing real noise.
+The noisy images were created from their clean origins by the application of a pipeline developed with the \emph{Augraphy} library; the production of \emph{ShabbyPages} was detailed in the third section, with all source code and input materials made openly available.
+\emph{ShabbyPages} was used to train performant denoising and binarization models which generalize well to document images containing real noise.
 

### 2023-02-11 paper/paper.tex
revert table, fix PSNR arrow pointing wrong direction

@@
     \centering
-    \caption{Summary of datasets for document denoising and binarization tasks.}
+    \caption{Summary of datasets for document binarization (above line) and document denoising (below line) tasks.}
     \label{tab:datasets}
@@
             \midrule
-         \emph{ShabbyPages} (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & multi~ & multi~ & \cmark & \cmark & \cmark \\
-         \emph{NoisyOffice} \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & 16pt & 1 & \xmark & \xmark & \xmark \\
-         DocCreator \cite{ref_DocCreator} & & \cmark & \xmark & & & & & &\cmark\\
-         DDI-100 \cite{ddi-100-2019} & & \cmark & \cmark & & & & & & \xmark\\
-         DIBCO-9 \cite{dibco-09} & & & & & & & & & n/a \\
-         DIBCO-10 \cite{dibco-10} & 10 & \xmark & \cmark & & multi & multi & \xmark & \xmark & n/a \\
-         DIBCO-11 \cite{dibco-11} & 16 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a\\
-         DIBCO-12 \cite{dibco-12} & 14 & \xmark & \cmark & & multi & multi & \xmark & \xmark & n/a \\
-         DIBCO-13 \cite{dibco-13} & 16 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
-         H-DIBCO-14 \cite{dibco-14} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
-         H-DIBCO-16 \cite{dibco-16} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
-         DIBCO-17 \cite{dibco-17} & 20 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
-         H-DIBCO-18 \cite{dibco-18} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a\\
-         DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & n/a\\
-         Bickley Diary \cite{bickley-diary} & & & & n/a & & & & & n/a\\
-         PHIBD & & & & & & & & & n/a\\
-         TQBC & & & & & & & & & n/a\\
+         DIBCO-9 \cite{dibco-09} & 10 & \xmark & \cmark &  & \cmark & \cmark & \cmark & \xmark & n/a \\
+         DIBCO-10 \cite{dibco-10} & 10 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
+         DIBCO-11 \cite{dibco-11} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
+         DIBCO-12 \cite{dibco-12} & 14 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
+         DIBCO-13 \cite{dibco-13} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         H-DIBCO-14 \cite{dibco-14} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         H-DIBCO-16 \cite{dibco-16} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         DIBCO-17 \cite{dibco-17} & 20 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         H-DIBCO-18 \cite{dibco-18} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
+         %DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & n/a\\ % SL: I can't find this dataset online
+         Bickley Diary \cite{bickley-diary} & 7 & \xmark & \cmark &  & \xmark & \xmark & \xmark & \xmark & n/a\\
+         PHIBD \cite{nafchi-2013-icdar} & 15 & \xmark & \cmark &  & \cmark & \cmark & \xmark & \xmark & n/a\\
+         %TQBC & & & & & & & & & n/a\\ % SL: I can't find this dataset online
+         \midrule
+         NoisyOffice \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & \cmark & \xmark & \xmark & \xmark & \xmark \\
+         DocCreator \cite{ref_DocCreator} & 6,059 & \cmark & \cmark & & \cmark & \cmark & \cmark & \xmark &\cmark\\
          %LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
+         DDI-100 \cite{ddi-100-2019} & 100k+~ & \cmark & \cmark & & & & & & \xmark\\
+         ShabbyPages (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & \cmark~ & \cmark~ & \cmark & \cmark & \cmark \\
          \bottomrule
@@
     \toprule
-    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{PSNR$\downarrow$~} \textbf{RMSE$\downarrow$~}\\
+    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{PSNR$\uparrow$~} \textbf{RMSE$\downarrow$~}\\
         \midrule

### 2023-02-11 paper/paper.tex
remove final todo
adding ddi-100 figure

@@
 \begin{itemize}
-\item The DIBCO datasets — widely recognized as critical data for document denoising and binarization — are far too small for large-scale training; each DIBCO dataset ranges between 10-20 images total.
+\item The \emph{DIBCO} datasets — widely recognized as critical data for document denoising and binarization — are far too small for large-scale training; each \emph{DIBCO} dataset ranges between 10-20 images total.
 \item The \emph{NoisyOffice} denoising dataset \cite{ref_NoisyOfficeDatabase} is also quite small, having \emph{72} training samples, and contains only a few types of noise — primarily artificial wrinkles and stains, with little variation.
-\item The DDI-100 corpus \cite{ddi-100-2019} is larger in scale than \emph{NoisyOffice} and the DIBCO datasets, but is again limited in the degree of feature diversity \cite{detection-masking-2022}.
+\item The \emph{DDI-100} corpus \cite{ddi-100-2019} is larger in scale than \emph{NoisyOffice} and the \emph{DIBCO} datasets, but is again limited in the degree of feature diversity \cite{detection-masking-2022}.
 \end{itemize}
@@
 In this paper, we introduce a new dataset designed primarily for the document denoising task, which addresses each of the concerns listed above.
-This new dataset, \emph{ShabbyPages}, is large-scale, having \emph{6202} training and \emph{mmm} [TODO: do we need this?] testing samples.
+This new dataset, \emph{ShabbyPages}, is large-scale, having \emph{6202} synthetic training images and \emph{200} real testing images.
 \emph{ShabbyPages} is more diverse than alternatives like \emph{NoisyOffice}, as it contains documents from various language groups and contains documents with graphical elements like tables and figures.
@@
 
-Another dataset, DDI-100 \cite{ddi-100-2019}, was constructed in a manner similar to \emph{NoisyOffice}.
-DDI-100 is far larger than \emph{NoisyOffice}, but has been criticized for not containing enough diversity or noise to be an effective benchmark \cite{detection-masking-2022}.
-Additionally, the pipeline code for creating the noisy versions of both \emph{NoisyOffice} and DDI-100 is not available, and thus these datasets cannot be reproduced.
+\begin{figure}
+    \centering\scalebox{0.365}{
+    \includegraphics{figures/ddi-100-samples-1.pdf}}
+    \caption{Example noisy-clean pairs from DDI-100.
+Geometric transformations are required to map the noisy samples to their corresponding clean ground-truth images, making DDI-100 unsuitable for binarization and denoising.}
+    \label{fig:ddi-100-samples}
+\end{figure}
+
+Another dataset, \emph{DDI-100} \cite{ddi-100-2019}, was constructed in a manner similar to \emph{NoisyOffice}.
+\emph{DDI-100} is far larger than \emph{NoisyOffice}, but has been criticized for not containing enough diversity or noise to be an effective benchmark \cite{detection-masking-2022}.
+Additionally, the pipeline code for creating the noisy versions of both \emph{NoisyOffice} and \emph{DDI-100} is not available, and thus these datasets cannot be reproduced.
+Moreover, while DDI-100 has noise-free document images with noisy counterparts, the noisy images also exhibit geometric transformations --- as seen in Figure~\ref{fig:ddi-100-samples} --- making it unsuitable for benchmarking document binarizers or denoisers using standard metrics like SSIM, PSNR, or MSE, which require clean-noisy correspondences to be free of geometric transformations.
 
@@
     \includegraphics{figures/dataset_examples.pdf}}
-    \caption{Example noisy-clean pairs from PHIBD (top row), DIBCO-13 (middle row), and \emph{NoisyOffice} (bottom row).}
+    \caption{Example noisy-clean pairs from PHIBD (top row), \emph{DIBCO-13} (middle row), and \emph{NoisyOffice} (bottom row).}
     \label{fig:other-dataset-examples}
@@
 Other prior work includes several datasets for the related task of document image binarization, which seeks to convert a document image into a binary image, where foreground text is black and background pixels are white.
-Among the most important in this class are the DIBCO collections \cite{dibco-09,dibco-10,dibco-11,dibco-12,dibco-13,dibco-14,dibco-16,dibco-17,dibco-18}.
-As summarized in Table~\ref{tab:datasets}, the DIBCO family of datasets is very small, ranging between 10 and 20 samples each (for a total of 106 images across DIBCO-9 through DIBCO-18).
-Similar to \emph{NoisyOffice}, the DIBCO datasets do not contain graphical elements like images, tables, charts, etc.
-The Persian Heritage Image Binarization Dataset (PHIBD) \cite{phibc-2012-nafchi,nafchi-2013-icdar} is similar to the DIBCO benchmarks, consisting of a small number of images of handwritten Persian writing.
+Among the most important in this class are the \emph{DIBCO} collections \cite{dibco-09,dibco-10,dibco-11,dibco-12,dibco-13,dibco-14,dibco-16,dibco-17,dibco-18}.
+As summarized in Table~\ref{tab:datasets}, the \emph{DIBCO} family of datasets is very small, ranging between 10 and 20 samples each (for a total of 106 images across \emph{DIBCO-9} through \emph{DIBCO-18}).
+Similar to \emph{NoisyOffice}, the \emph{DIBCO} datasets do not contain graphical elements like images, tables, charts, etc.
+The Persian Heritage Image Binarization Dataset (PHIBD) \cite{phibc-2012-nafchi,nafchi-2013-icdar} is similar to the \emph{DIBCO} benchmarks, consisting of a small number of images of handwritten Persian writing.
 Others, like the Bickley Diary set \cite{bickley-diary} and the 2019 Time-Quality Binarization Competition set \cite{2019-time-quality-competition} have also been used for benchmarking document binarization approaches, but these do not appear to be publicly available \cite{tensmeyer-binarization-review-2020}.
@@
             & \rot{80}{\textbf{Diversity}}
-            & \rot{80}{\textbf{Mult. font sizes}}
-            & \rot{80}{\textbf{Mult. paper styles}}
+            & \rot{80}{\textbf{Varied fonts/sizes}}
+            & \rot{80}{\textbf{Varied paper styles}}
             & \rot{80}{\textbf{Multilingual}}
@@
             \midrule
-         DIBCO-9 \cite{dibco-09} & 10 & \xmark & \cmark &  & \cmark & \cmark & \cmark & \xmark & n/a \\
-         DIBCO-10 \cite{dibco-10} & 10 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
-         DIBCO-11 \cite{dibco-11} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
-         DIBCO-12 \cite{dibco-12} & 14 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
-         DIBCO-13 \cite{dibco-13} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
-         H-DIBCO-14 \cite{dibco-14} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
-         H-DIBCO-16 \cite{dibco-16} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
-         DIBCO-17 \cite{dibco-17} & 20 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
-         H-DIBCO-18 \cite{dibco-18} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
-         %DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & n/a\\ % SL: I can't find this dataset online
+         \emph{DIBCO-9} \cite{dibco-09} & 10 & \xmark & \cmark &  & \cmark & \cmark & \cmark & \xmark & n/a \\
+         \emph{DIBCO-10} \cite{dibco-10} & 10 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
+         \emph{DIBCO-11} \cite{dibco-11} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
+         \emph{DIBCO-12} \cite{dibco-12} & 14 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
+         \emph{DIBCO-13} \cite{dibco-13} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         \emph{H-DIBCO-14} \cite{dibco-14} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         \emph{H-DIBCO-16} \cite{dibco-16} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         \emph{DIBCO-17} \cite{dibco-17} & 20 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
+         \emph{H-DIBCO-18} \cite{dibco-18} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
+         %\emph{DIBCO-19} \cite{dibco-19} & & \xmark & & & & & & & n/a\\ % SL: I can't find this dataset online
          Bickley Diary \cite{bickley-diary} & 7 & \xmark & \cmark &  & \xmark & \xmark & \xmark & \xmark & n/a\\
@@
          \midrule
-         NoisyOffice \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & \cmark & \xmark & \xmark & \xmark & \xmark \\
-         DocCreator \cite{ref_DocCreator} & 6,059 & \cmark & \cmark & & \cmark & \cmark & \cmark & \xmark &\cmark\\
+         \emph{NoisyOffice} \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & \cmark & \xmark & \xmark & \xmark & \xmark \\
+         \emph{DocCreator} \cite{ref_DocCreator} & 6,059 & \cmark & \cmark & & \cmark & \cmark & \cmark & \xmark &\cmark\\
          %LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
-         DDI-100 \cite{ddi-100-2019} & 100k+~ & \cmark & \cmark & & & & & & \xmark\\
-         ShabbyPages (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & \cmark~ & \cmark~ & \cmark & \cmark & \cmark \\
+         \emph{DDI-100} \cite{ddi-100-2019} & 100k+~ & \cmark & \cmark & & & & & & \xmark\\
+         \emph{ShabbyPages} (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & \cmark~ & \cmark~ & \cmark & \cmark & \cmark \\
          \bottomrule

### 2023-02-11 paper/paper.tex

@@
 
-\begin{figure}
-    \centering\scalebox{0.365}{
-    \includegraphics{figures/ddi-100-samples-1.pdf}}
-    \caption{Example noisy-clean pairs from DDI-100.
-Geometric transformations are required to map the noisy samples to their corresponding clean ground-truth images, making DDI-100 unsuitable for binarization and denoising.}
-    \label{fig:ddi-100-samples}
-\end{figure}
-
 Another dataset, \emph{DDI-100} \cite{ddi-100-2019}, was constructed in a manner similar to \emph{NoisyOffice}.
@@
 Additionally, the pipeline code for creating the noisy versions of both \emph{NoisyOffice} and \emph{DDI-100} is not available, and thus these datasets cannot be reproduced.
-Moreover, while DDI-100 has noise-free document images with noisy counterparts, the noisy images also exhibit geometric transformations --- as seen in Figure~\ref{fig:ddi-100-samples} --- making it unsuitable for benchmarking document binarizers or denoisers using standard metrics like SSIM, PSNR, or MSE, which require clean-noisy correspondences to be free of geometric transformations.
 

### 2023-02-11 paper/paper.tex
Updates from Overleaf
Merging in change from Stefan to resolve merge conflict

@@
 
+\begin{figure}
+    \centering\scalebox{0.365}{
+    \includegraphics{figures/ddi-100-samples-1.pdf}}
+    \caption{Example noisy-clean pairs from DDI-100.
+Geometric transformations are required to map the noisy samples to their corresponding clean ground-truth images, making DDI-100 unsuitable for binarization and denoising.}
+    \label{fig:ddi-100-samples}
+\end{figure}
+
 Another dataset, \emph{DDI-100} \cite{ddi-100-2019}, was constructed in a manner similar to \emph{NoisyOffice}.
@@
 Additionally, the pipeline code for creating the noisy versions of both \emph{NoisyOffice} and \emph{DDI-100} is not available, and thus these datasets cannot be reproduced.
+Moreover, while \emph{DDI-100} has noise-free document images with noisy counterparts, the noisy images also exhibit geometric transformations --- as seen in Figure~\ref{fig:ddi-100-samples} --- making it unsuitable for benchmarking document binarizers or denoisers using standard metrics like SSIM, PSNR, or MSE, which require clean-noisy correspondences to be free of geometric transformations.
 

### 2023-02-11 paper/paper.tex
Fixed image reference
fix mathmode issue

@@
 The development of the computation pipeline used to generate the corpus is discussed, and the results presented.
-The final corpus contains over 6000 "born-digital" ground truth document images, sourced on the Web, with synthetically-noised counterparts (``shabby pages'') that appear to have been printed and faxed, photocopied, or otherwise altered through physical processes.
+The final corpus contains over 6000 ``born-digital'' ground truth document images, sourced on the Web, with synthetically-noised counterparts (``shabby pages'') that appear to have been printed and faxed, photocopied, or otherwise altered through physical processes.
 The release of this dataset and the recipe for its production attempts to address a growing need for labeled training document images for supervised learning tasks.
@@
 \begin{itemize}
-\item The \emph{DIBCO} datasets — widely recognized as critical data for document denoising and binarization — are far too small for large-scale training; each \emph{DIBCO} dataset ranges between 10-20 images total.
-\item The \emph{NoisyOffice} denoising dataset \cite{ref_NoisyOfficeDatabase} is also quite small, having \emph{72} training samples, and contains only a few types of noise — primarily artificial wrinkles and stains, with little variation.
-\item The \emph{DDI-100} corpus \cite{ddi-100-2019} is larger in scale than \emph{NoisyOffice} and the \emph{DIBCO} datasets, but is again limited in the degree of feature diversity \cite{detection-masking-2022}.
+\item \emph{DIBCO} datasets, which are widely recognized as critical data for document denoising and binarization, are far too small for large-scale training since each \emph{DIBCO} dataset ranges between 10-20 images total.
+\item \emph{NoisyOffice} \cite{ref_NoisyOfficeDatabase} is a denoising dataset that is also quite small, having \emph{72} training samples, and contains only a few types of noise — primarily artificial wrinkles and stains, with little variation.
+\item \emph{DDI-100} \cite{ddi-100-2019} is larger corpus in scale than \emph{NoisyOffice} and the \emph{DIBCO} datasets, but is again limited in the degree of feature diversity \cite{detection-masking-2022}.
 \end{itemize}
@@
     \centering\scalebox{0.365}{
-    \includegraphics{figures/ddi-100-samples-1.pdf}}
+    \includegraphics{figures/ddi-100-samples.pdf}}
     \caption{Example noisy-clean pairs from DDI-100.

### 2023-02-11 paper/paper.tex
minor formatting fixes

@@
 \subsection{Developing the Pipeline}
-The \emph{Augraphy} library presents an easy-to-use API for constructing feature pipelines, which has been designed for interoperability with other augmentation tools, and within the broader data ecosystem.
+The \emph{Augraphy} library presents an easy-to-use API for constructing data augmentation pipelines for document images, which has been designed for interoperability with other augmentation tools, and within the broader data ecosystem.
 While \emph{Augraphy}'s default pipeline has what we believe to be quite realistic defaults, we wanted a broader range of features from this dataset than those the default pipeline could produce.
@@
 Five individuals were recruited for this task, which involved printing 40 pages of documents and manually applying various effects such as folds, wrinkles, smudges, highlighters, pencils, crayons, splatters of ink or other liquids, printing, scanning, faxing and other creative and reasonable treatments determined by these workers.
-The process continued over a period of two weeks, incurring a cost of approximately $1,000 USD.
+The process continued over a period of two weeks, incurring a cost of approximately \$1,000 USD.
 While there are plenty of opportunities to streamline the operation, scaling this process is expensive in terms of both time and money, and may have unpredictable results.
@@
     \centering
-    \caption{Document image denoising cross-test performance of NAFNet models trained on \emph{ShabbyPages} and \emph{NoisyOffice}.}
+    \caption{Document image denoising cross-test performance of NAFNet models trained on \emph{ShabbyPages} and \emph{NoisyOffice}.} \label{tab:denoising_results}
     \scalebox{0.9}{
@@
     \end{tabular}}
-    \label{tab:denoising_results}
 \end{table}
 
-As can be seen from Table \cite{tab:denoising_results}, the \emph{ShabbyPages}-trained denoiser generalized to \emph{NoisyOffice} far better than the \emph{NoisyOffice}-trained model generalized to \emph{ShabbyPages}.
+As can be seen from Table~\ref{tab:denoising_results}, the \emph{ShabbyPages}-trained denoiser generalized to \emph{NoisyOffice} far better than the \emph{NoisyOffice}-trained model generalized to \emph{ShabbyPages}.
 This result is consistent with the much higher diversity present within the \emph{ShabbyPages} set, relative to features found in the \emph{NoisyOffice} database.
@@
 Both of these metrics are more useful for determining the differences between binary images: together, they give some idea of the degree to which noise artifacts remain in the image after denoizing and binarization affect the visual signal, and how many such artifacts exist.
-The averages of each metric over all predictions was taken, with the results presented in Table \cite{tab:binarization_results}.
+The averages of each metric over all predictions was taken, with the results presented in Table~\ref{tab:binarization_results}.
 
@@
     \toprule
-    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{PSNR$\uparrow$~} \textbf{RMSE$\downarrow$~}\\
+    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{PSNR$\uparrow$~} & \textbf{RMSE$\downarrow$~}\\
         \midrule

### 2023-02-11 paper/paper.tex
update sample patch images, update subsection title

--- 2023-02-11 paper/paper.tex
@@
 \centering
-\includegraphics[width=0.98\columnwidth, frame]{figures/matrix.png}
+\includegraphics[width=0.98\columnwidth, frame]{figures/quad.png}
 \caption{Sample patches from \emph{ShabbyPages}.} \label{fig1}
@@
 
+\begin{figure}
+    \includegraphics[width=1.0\textwidth]{figures/matrix_tall1.png}
+    \caption{Sample noisy patches from ShabbyPages.}
+    \label{fig:matrix_tall1}
+\end{figure}
+
 \subsection{Data Gathering}
@@
 
-\subsection{Processing \emph{Augraphy} on a multicore system}
+\begin{figure}
+    \includegraphics[width=1.0\textwidth]{figures/matrix_tall2.png}
+    \caption{Sample noisy patches from ShabbyPages.}
+    \label{fig:matrix_tall2}
+\end{figure}
+
+\subsection{Processing \emph{Augraphy} Pipelines}
 Execution time is dependent on which augmentations are executed at runtime; a long \emph{Augraphy} pipeline can take several seconds to process large images.

### 2023-02-11 paper/paper.tex
add shabbyreal sample, fix references to shabbyreal

@@
 
-\subsection{\emph{ShabbyPages}}
-In keeping with the spirit of \emph{NoisyOffice}, our original inspiration, and to provide out-of-distribution test data for ours and other projects, we developed a separate but related dataset which we call \emph{ShabbyPages}.
+\subsection{\emph{ShabbyReal}}
+In keeping with the spirit of \emph{NoisyOffice}, our original inspiration, and to provide out-of-distribution test data for ours and other projects, we developed a separate but related dataset which we call \emph{ShabbyReal}.
 To build this, we isolated reproduction steps for several physical operations, designed real-world augmentation pipelines with these, and then engaged a team of workers to use these instructions to produce several copies of printed born-digital documents with real noise.
@@
 Manually producing a database of noisy documents is a time-consuming and repetitive task; creating just 100 real-world documents with real noise features required the labor of several people.
-Nevertheless, despite the limited size of the resulting dataset, the scarcity of real-world datasets with ground truth images makes the \emph{ShabbyPages} corpus extremely valuable.
-This type of dataset is critical for benchmark comparison with synthetically-augmented document images, and for other tasks such as denoising and binarizing: we use \emph{ShabbyPages} later for a human-perception evaluation of denoising performance.
+Nevertheless, despite the limited size of the resulting dataset, the scarcity of real-world datasets with ground truth images makes the \emph{ShabbyReal} corpus extremely valuable; its inclusion in \emph{ShabbyPages} even moreso.
+This type of dataset is critical for benchmark comparison with synthetically-augmented document images, and for other tasks such as denoising and binarizing: we use \emph{ShabbyReal} later for a human-perception evaluation of denoising performance.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.98\columnwidth, frame]{figures/shabbyreal_figure1.png}
+\caption{Example \emph{ShabbyReal} images and their clean counterparts.}
+\label{fig:shabbyreal_sample}
+\end{figure}
 
@@
 
-Machine learning is ultimately about getting computers to complete tasks which normally require human labor; as further validation for the efficacy of \emph{ShabbyPages} in training performant denoisers, we also used our \emph{ShabbyPages}-trained NAFNet model to denoise the \emph{ShabbyPages} set, and present some examples of its performance below.
+Machine learning is ultimately about getting computers to complete tasks which normally require human labor; as further validation for the efficacy of \emph{ShabbyPages} in training performant denoisers, we also used our \emph{ShabbyPages}-trained NAFNet model to denoise the \emph{ShabbyReal} set, and present some examples of its performance below.
 
@@
 \includegraphics[width=0.98\columnwidth, frame]{figures/shabbyreal_denoising.png}
-\caption{Sample \emph{ShabbyPages} images and their Shabby\_NAFNet-denoised versions.}
+\caption{Sample \emph{ShabbyReal} images and their Shabby\_NAFNet-denoised versions.}
 \label{fig:shabbyreal_denoising}

### 2023-02-11 paper/paper.tex
refactor dataset sections

@@
 
-\section{The Dataset}
-\emph{ShabbyPages} joins a rapidly growing number of open-source datasets freely available online.
-Human activity today generates a tremendous amount of data, with many people choosing to publish theirs on websites like Kaggle \cite{ref_Kaggle}, Hugging Face Hub \cite{ref_HuggingFaceHub}, and many more.
-All of this data is arranged into categories: sets exist which contain text, images, audio, and data from other modalities, with each set often collected and designed for a purpose.
-Of the many image datasets available, the authors understand few to have been designed for groundtruthed supervised learning of document-specific tasks like binarization or denoising.
-In fact, we could find only one other set compiled specifically for doing so with images of \textit{modern} documents: \emph{NoisyOffice} \cite{ref_NoisyOffice}.
+\section{Related Datasets}
+This section discusses datasets used for the tasks of document denoising and document binarization.
+These datasets are listed in Table~\ref{tab:datasets}.
+%By now, hundreds of datasets exist for the document denoising task (several listed in \cite{tab:datasets}), 
+The most similar to \emph{ShabbyPages} being \emph{NoisyOffice} \cite{ref_NoisyOfficeDatabase}.
+\emph{NoisyOffice} is very limited, however, consisting of two font weights, three font sizes, three font types, and four noise types, for a total of just 72 unique images.
+The \emph{NoisyOffice} collection was created by permuting these font/size/base combinations, and the resulting set is feature-poor.
+\emph{NoisyOffice} also lacks non-English and non-Latin characters, as well as graphical elements like images, logos, and tables.
+To add noise, the creators produced four different types of background noise (folds, wrinkles, coffee stains, and footprints), and then overlayed digitally-generated text onto these.
 
-\subsection{Features}
-Modern artificial neural networks produce a latent representation of their training data, a space from which outputs are sampled.
-In deep networks, these representations live within multiple layers, each of which corresponds to a feature of the input data.
-Document images are a particularly interesting category, as the data within the documents each picture represents is itself frequently multi-modal; the document may contain an image and its description, a table with statistics, multiple regions of structured and formatted text, and even other documents, making their internal representations by neural networks often quite complicated.
+\begin{table}[]
+    \centering
+    \caption{Summary of datasets for document binarization (above line) and document denoising (below line) tasks. Datasets listed below the line contain synthetic noise.}
+    \label{tab:datasets}
+    \begin{tabular}{lclllllll}
+        \textbf{Dataset} &
+        \rot{80}{\textbf{Dataset Size}}
+            & \rot{80}{\textbf{Synthetic Noise}}
+            & \rot{80}{\textbf{Ground-Truths}}
+            %& \rot{80}{\textbf{Diversity}}
+            & \rot{80}{\textbf{Varied fonts/sizes}}
+            & \rot{80}{\textbf{Varied paper styles}}
+            & \rot{80}{\textbf{Multilingual}}
+            & \rot{80}{\textbf{Contains graphics}}
+            & \rot{80}{\textbf{Reproducible}}\\
+            \midrule
+         \emph{DIBCO-9} \cite{dibco-09} & 10 & \xmark & \cmark &   \cmark & \cmark & \cmark & \xmark & n/a \\
+         \emph{DIBCO-10} \cite{dibco-10} & 10 & \xmark & \cmark &  \cmark & \cmark & \xmark & \xmark & n/a \\
+         \emph{DIBCO-11} \cite{dibco-11} & 16 & \xmark & \cmark &  \cmark & \cmark & \cmark & \xmark & n/a\\
+         \emph{DIBCO-12} \cite{dibco-12} & 14 & \xmark & \cmark &  \cmark & \cmark & \xmark & \xmark & n/a \\
+         \emph{DIBCO-13} \cite{dibco-13} & 16 & \xmark & \cmark &  \cmark & \cmark & \cmark & \xmark & n/a \\
+         \emph{H-DIBCO-14} \cite{dibco-14} & 10 & \xmark & \cmark & \cmark & \cmark & \cmark & \xmark & n/a \\
+         \emph{H-DIBCO-16} \cite{dibco-16} & 10 & \xmark & \cmark & \cmark & \cmark & \cmark & \xmark & n/a \\
+         \emph{DIBCO-17} \cite{dibco-17} & 20 & \xmark & \cmark & \cmark & \cmark & \cmark & \xmark & n/a \\
+         \emph{H-DIBCO-18} \cite{dibco-18} & 10 & \xmark & \cmark  & \cmark & \cmark & \cmark & \xmark & n/a\\
+         %\emph{DIBCO-19} \cite{dibco-19} & & \xmark & & & & & & & n/a\\ % SL: I can't find this dataset online
+         Bickley Diary \cite{bickley-diary} & 7 & \xmark & \cmark   & \xmark & \xmark & \xmark & \xmark & n/a\\
+         PHIBD \cite{nafchi-2013-icdar} & 15 & \xmark & \cmark &   \cmark & \cmark & \xmark & \xmark & n/a\\
+         %TQBC & & & & & & & & & n/a\\ % SL: I can't find this dataset online
+         \midrule
+         \emph{NoisyOffice} \cite{ref_NoisyOffice} & 72  & \cmark & \cmark &  \cmark & \xmark & \xmark & \xmark & \xmark \\ % div: 0.317
+         \emph{DocCreator} \cite{ref_DocCreator} & 6,059 & \cmark & \cmark & \cmark & \cmark & \cmark & \xmark &\cmark\\
+         %LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
+         \emph{DDI-100} \cite{ddi-100-2019} & 100k+~ & \cmark & \cmark & \cmark & \xmark & \xmark & \cmark & \xmark\\
+         \emph{ShabbyPages} (ours)~ & 6,202~ & \cmark & \cmark  & \cmark~ & \cmark~ & \cmark & \cmark & \cmark \\ % div: 0.488
+         \bottomrule
+    \end{tabular}
+\end{table}
 
-Networks with a wider variety of latent representations frequently perform better when generalizing their learned functions to other tasks.
-For this reason, procuring a large-enough volume of robust-enough training data is paramount.
-Several sets of such images exist, many intended for processing by deep neural nets; Table \cite{tab:datasets} contains a comparison of some of the key hyperproperties of the \emph{ShabbyPages} set compared with other popular document image datasets.
+Another dataset, \emph{DDI-100} \cite{ddi-100-2019}, was constructed in a manner similar to \emph{NoisyOffice}.
+\emph{DDI-100} is far larger than \emph{NoisyOffice}, but has been criticized for not containing enough diversity or noise to be an effective benchmark \cite{detection-masking-2022}.
+Additionally, the pipeline code for creating the noisy versions of both \emph{NoisyOffice} and \emph{DDI-100} is not available, and thus these datasets cannot be reproduced.
+Moreover, while \emph{DDI-100} has noise-free document images with noisy counterparts, the noisy images also exhibit geometric transformations --- as seen in Figure~\ref{fig:ddi-100-samples} --- making it unsuitable for benchmarking document binarizers or denoisers using standard metrics like SSIM, PSNR, or MSE, which require clean-noisy correspondences to be free of geometric transformations.
 
-\textbf{Diversity.} We use the diversity metric as defined in \cite{kang-etal-2018-data,larson-etal-2019-outlier} to help us measure intra-dataset variety.
-This metric is defined as
-$$
-Diversity(X) = \frac{1}{|X|^2} \sum_{a\in X} \sum_{b\in X} \|f(a)-f(b)\|_2
-$$
-where $f(\cdot)$ is an embedding function mapping the input image into an \emph{n}-dimensional vector space.
-Here, we use CLIP's ViT model \cite{clip}, which embeds each image into a 512-dimensional space.
-The intuition behind the diversity metric is that datasets where images are highly similar will have lower diversity scores, and datasets where images share less visual similarity will have higher diversity scores.
-A dataset with low diversity might not be representative enough of the real world, and low diversity may further correlate with task easiness.
+\begin{figure}
+    \centering\scalebox{0.365}{
+    \includegraphics{figures/ddi-100-samples-1.pdf}}
+    \caption{Example noisy-clean pairs from DDI-100.
+Geometric transformations are required to map the noisy samples to their corresponding clean ground-truth images, making DDI-100 unsuitable for binarization and denoising.}
+    \label{fig:ddi-100-samples}
+\end{figure}
 
-\subsection{Statistics}
-\emph{ShabbyPages} contains documents from multiple classes, which contain many types of information.
+Other prior work includes several datasets for the related task of document image binarization, which seeks to convert a document image into a binary image, where foreground text is black and background pixels are white.
+Among the most important in this class are the \emph{DIBCO} collections \cite{dibco-09,dibco-10,dibco-11,dibco-12,dibco-13,dibco-14,dibco-16,dibco-17,dibco-18}.
+As summarized in Table~\ref{tab:datasets}, the \emph{DIBCO} family of datasets is very small, ranging between 10 and 20 samples each (for a total of 106 images across \emph{DIBCO-9} through \emph{DIBCO-18}).
+Similar to \emph{NoisyOffice}, the \emph{DIBCO} datasets do not contain graphical elements like images, tables, charts, etc.
+The Persian Heritage Image Binarization Dataset (PHIBD) \cite{phibc-2012-nafchi,nafchi-2013-icdar} is similar to the \emph{DIBCO} benchmarks, consisting of a small number of images of handwritten Persian writing.
+Others, like the Bickley Diary set \cite{bickley-diary} and the 2019 Time-Quality Binarization Competition set \cite{2019-time-quality-competition} have also been used for benchmarking document binarization approaches, but these do not appear to be publicly available \cite{tensmeyer-binarization-review-2020}.
+Ultimately, the sizes of these document binarization corpora severly limit the types of algorithms and models that can be used.
+Examples of noisy-clean image pairs from some of these collections are displayed in Figure~\ref{fig:other-dataset-examples}.
 
-Table \cite{ref:tab1} contains some statistics for the dataset, in grayscale, at a standard resolution of 150 ppi.
+\begin{figure}
+    \centering\scalebox{0.4}{
+    \includegraphics{figures/dataset_examples.pdf}}
+    \caption{Example noisy-clean pairs from PHIBD (top row), \emph{DIBCO-13} (middle row), and \emph{NoisyOffice} (bottom row).}
+    \label{fig:other-dataset-examples}
+\end{figure}
+
+Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean ground-truth document images to train or evaluate document denoisiers and binarizers.
 
@@
     \caption{ShabbyPages dataset statistics.}
-    \label{tab1}
+    \label{tab:summary-statistics}
     \begin{tabular}{@{\hspace{2em}}l@{\qquad}@{\hspace{2em}}l@{\qquad}}
@@
 
-\subsection{Other Datasets}
-By now, hundreds of datasets exist for the document denoising task (several listed in \cite{tab:datasets}), the most similar to \emph{ShabbyPages} being \emph{NoisyOffice} \cite{ref_NoisyOfficeDatabase}.
-\emph{NoisyOffice} is very limited, however, consisting of two font weights, three font sizes, three font types, and four noise types, for a total of just 72 unique images.
-The \emph{NoisyOffice} collection was created by permuting these font/size/base combinations, and the resulting set is feature-poor.
-\emph{NoisyOffice} also lacks non-English and non-Latin characters, as well as graphical elements like images, logos, and tables.
-To add noise, the creators produced four different types of background noise (folds, wrinkles, coffee stains, and footprints), and then overlayed digitally-generated text onto these.
+\section{The \emph{ShabbyPages} Dataset}
+This section provides an overview of the finer details of the \emph{ShabbyPages} dataset, as well as the processes we used to create it.
 
-\begin{figure}
-    \centering\scalebox{0.365}{
-    \includegraphics{figures/ddi-100-samples.pdf}}
-    \caption{Example noisy-clean pairs from DDI-100.
-Geometric transformations are required to map the noisy samples to their corresponding clean ground-truth images, making DDI-100 unsuitable for binarization and denoising.}
-    \label{fig:ddi-100-samples}
-\end{figure}
+\subsection{Overview of \emph{ShabbyPages}}
+\emph{ShabbyPages} consists of 6,202 full-page document images.
+The text in the images is varied: \emph{ShabbyPages} encompasses multiple languages (including English, Japanese, Chinese), and font styles and sizes.
+Some other summary statistics for \emph{ShabbyPages} are displayed in Table~\ref{tab:summary-statistics}.
+\emph{ShabbyPages} contains many more samples than the document binarization datasets surveyed in Table~\ref{tab:datasets}.
+While \emph{ShabbyPages} has fewer samples than \emph{DDI-100}, we again point out that the use of \emph{DDI-100} for benchmarking document denoisers and binarizers is problematic due to the presence of geometric transformations in \emph{DDI-100}.
+Our dataset contains more samples than \emph{NoisyOffice} and \emph{DocCreator},
+and in contrast to \emph{NoisyOffice}, the \emph{ShabbyPages} dataset also contains graphical elements like figures, tables, logos, etc.
 
-Another dataset, \emph{DDI-100} \cite{ddi-100-2019}, was constructed in a manner similar to \emph{NoisyOffice}.
-\emph{DDI-100} is far larger than \emph{NoisyOffice}, but has been criticized for not containing enough diversity or noise to be an effective benchmark \cite{detection-masking-2022}.
-Additionally, the pipeline code for creating the noisy versions of both \emph{NoisyOffice} and \emph{DDI-100} is not available, and thus these datasets cannot be reproduced.
-Moreover, while \emph{DDI-100} has noise-free document images with noisy counterparts, the noisy images also exhibit geometric transformations --- as seen in Figure~\ref{fig:ddi-100-samples} --- making it unsuitable for benchmarking document binarizers or denoisers using standard metrics like SSIM, PSNR, or MSE, which require clean-noisy correspondences to be free of geometric transformations.
+We can also measure the "diversity" of our dataset as a way to compare the richness of various features against an alternative like \emph{NoisyOffice}.
+To do this, we use a diversity metric \cite{larson-etal-2019-outlier} defined as
+$$
+Diversity(X) = \frac{1}{|X|^2} \sum_{a\in X} \sum_{b\in X} \|f(a)-f(b)\|_2
+$$
+where $f(\cdot)$ is an embedding function that maps the input image 
+into an \emph{n}-dimensional vector space.
+Here, we use CLIP's ViT model \cite{clip}, which embeds each image into a 512-dimensional space.
+The intuition behind the diversity metric is that datasets where images are highly similar will have lower diversity scores, and datasets where images share less visual similarity will have higher diversity scores.
+A dataset with low diversity might not be representative enough of the real world, and low diversity may further correlate with task easiness.
+Using this metric, we find that the diversity of \emph{NoisyOffice} is 0.317, while the diversity score for \emph{ShabbyPages} is 0.488.
 
-\begin{figure}
-    \centering\scalebox{0.4}{
-    \includegraphics{figures/dataset_examples.pdf}}
-    \caption{Example noisy-clean pairs from PHIBD (top row), \emph{DIBCO-13} (middle row), and \emph{NoisyOffice} (bottom row).}
-    \label{fig:other-dataset-examples}
-\end{figure}
-
-Other prior work includes several datasets for the related task of document image binarization, which seeks to convert a document image into a binary image, where foreground text is black and background pixels are white.
-Among the most important in this class are the \emph{DIBCO} collections \cite{dibco-09,dibco-10,dibco-11,dibco-12,dibco-13,dibco-14,dibco-16,dibco-17,dibco-18}.
-As summarized in Table~\ref{tab:datasets}, the \emph{DIBCO} family of datasets is very small, ranging between 10 and 20 samples each (for a total of 106 images across \emph{DIBCO-9} through \emph{DIBCO-18}).
-Similar to \emph{NoisyOffice}, the \emph{DIBCO} datasets do not contain graphical elements like images, tables, charts, etc.
-The Persian Heritage Image Binarization Dataset (PHIBD) \cite{phibc-2012-nafchi,nafchi-2013-icdar} is similar to the \emph{DIBCO} benchmarks, consisting of a small number of images of handwritten Persian writing.
-Others, like the Bickley Diary set \cite{bickley-diary} and the 2019 Time-Quality Binarization Competition set \cite{2019-time-quality-competition} have also been used for benchmarking document binarization approaches, but these do not appear to be publicly available \cite{tensmeyer-binarization-review-2020}.
-Ultimately, the sizes of these document binarization corpora severly limit the types of algorithms and models that can be used.
-Examples of noisy-clean image pairs from some of these collections are displayed in Figure~\ref{fig:other-dataset-examples}.
-
-Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean ground-truth document images to train or evaluate document denoisiers and binarizers.
-
-\begin{table}[]
-    \centering
-    \caption{Summary of datasets for document binarization (above line) and document denoising (below line) tasks.}
-    \label{tab:datasets}
-    \begin{tabular}{lcllllllll}
-        \textbf{Dataset} &
-        \rot{80}{\textbf{Dataset Size}}
-            & \rot{80}{\textbf{Synthetic Noise}}
-            & \rot{80}{\textbf{Ground-Truths}}
-            & \rot{80}{\textbf{Diversity}}
-            & \rot{80}{\textbf{Varied fonts/sizes}}
-            & \rot{80}{\textbf{Varied paper styles}}
-            & \rot{80}{\textbf{Multilingual}}
-            & \rot{80}{\textbf{Contains graphics}}
-            & \rot{80}{\textbf{Reproducible}}\\
-            \midrule
-         \emph{DIBCO-9} \cite{dibco-09} & 10 & \xmark & \cmark &  & \cmark & \cmark & \cmark & \xmark & n/a \\
-         \emph{DIBCO-10} \cite{dibco-10} & 10 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
-         \emph{DIBCO-11} \cite{dibco-11} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
-         \emph{DIBCO-12} \cite{dibco-12} & 14 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
-         \emph{DIBCO-13} \cite{dibco-13} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
-         \emph{H-DIBCO-14} \cite{dibco-14} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
-         \emph{H-DIBCO-16} \cite{dibco-16} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
-         \emph{DIBCO-17} \cite{dibco-17} & 20 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
-         \emph{H-DIBCO-18} \cite{dibco-18} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
-         %\emph{DIBCO-19} \cite{dibco-19} & & \xmark & & & & & & & n/a\\ % SL: I can't find this dataset online
-         Bickley Diary \cite{bickley-diary} & 7 & \xmark & \cmark &  & \xmark & \xmark & \xmark & \xmark & n/a\\
-         PHIBD \cite{nafchi-2013-icdar} & 15 & \xmark & \cmark &  & \cmark & \cmark & \xmark & \xmark & n/a\\
-         %TQBC & & & & & & & & & n/a\\ % SL: I can't find this dataset online
-         \midrule
-         \emph{NoisyOffice} \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & \cmark & \xmark & \xmark & \xmark & \xmark \\
-         \emph{DocCreator} \cite{ref_DocCreator} & 6,059 & \cmark & \cmark & & \cmark & \cmark & \cmark & \xmark &\cmark\\
-         %LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
-         \emph{DDI-100} \cite{ddi-100-2019} & 100k+~ & \cmark & \cmark & & & & & & \xmark\\
-         \emph{ShabbyPages} (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & \cmark~ & \cmark~ & \cmark & \cmark & \cmark \\
-         \bottomrule
-    \end{tabular}
-\end{table}
-
-\section{Construction}
+\subsection{\emph{ShabbyPages} Construction}
 This section describes the dataset generation methodology; code for all of this is available on GitHub.
@@
 
-\subsection{Data Gathering}
+\subsubsection{Data Gathering.}
 A team of workers searched the public internet for PDFs of many different kinds, from culturally-important sources like government agencies, NGOs, and large multinational corporations.
@@
 
-\subsection{PDF to PNG}
+\subsubsection{PDF to PNG Conversion.}
 The ~pdftoppm~ tool from the ~poppler-utils~ package was used to split the PDF documents into individual pages.
@@
 
-\subsection{Developing the Pipeline}
+\ubsubsection{Developing the Pipeline.}
 The \emph{Augraphy} library presents an easy-to-use API for constructing data augmentation pipelines for document images, which has been designed for interoperability with other augmentation tools, and within the broader data ecosystem.
@@
 
-\subsection{Processing \emph{Augraphy} Pipelines}
+\subsubsection{Processing \emph{Augraphy} Pipelines.}
 Execution time is dependent on which augmentations are executed at runtime; a long \emph{Augraphy} pipeline can take several seconds to process large images.

### 2023-02-11 paper/paper.tex
one line with exposition

@@
 
-\title{ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images}
+\title{ShabbyPages: A Reproducible Document Denoising and Binarization Dataset}
 %\author{Alexander Groleau\inst{1,2} \and
@@
 \begin{abstract}
-The \emph{ShabbyPages} document image dataset is produced using the \emph{Augraphy} document image augmentation tool.
-The development of the computation pipeline used to generate the corpus is discussed, and the results presented.
-The final corpus contains over 6000 ``born-digital'' ground truth document images, sourced on the Web, with synthetically-noised counterparts (``shabby pages'') that appear to have been printed and faxed, photocopied, or otherwise altered through physical processes.
-The release of this dataset and the recipe for its production attempts to address a growing need for labeled training document images for supervised learning tasks.
-The results of initial experiments are discussed, in which the corpus is used to train performant convolutional denoisers which remove real noise features with a high degree of human-perceptible fidelity, establishing baseline performance for a new \emph{ShabbyPages} benchmark.
+Document denoising and binarization are fundamental problems in the document processing space, but current datasets are often too small and lack sufficient complexity to effectively train and benchmark modern data-driven machine learning models.
+To fill this gap, we introduce \emph{ShabbyPages}, a new document image dataset designed for training and benchmarking document denoisers and binarizers.
+\emph{ShabbyPages} contains over 6,000 clean ``born digital" images with synthetically-noised counterparts (``shabby pages") that were augmented using the \emph{Augraphy} document augmentation tool to appear as if they have been printed and faxed, photocopied, or otherwise altered through physical processes.
+In this paper, we disucss the creation process of \emph{ShabbyPages} and demonstrate the utility of \emph{ShabbyPages} by training convolutional denoisers which remove real noise features with a high degree of human-perceptible fidelity, establishing baseline performance for a new \emph{ShabbyPages} benchmark.
 \end{abstract}

### 2023-02-11 paper/paper.tex

@@
 \usepackage{courier}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+\definecolor{superlightgray}{RGB}{242,242,242}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=false,
+    breaklines=true,
+    captionpos=b,
+    keepspaces=true,
+    numbers=left,
+    numbersep=5pt,
+    showspaces=false,
+    showstringspaces=false,
+    showtabs=false,
+    tabsize=2
+}
+\lstset{style=mystyle}
 
@@
 This section discusses datasets used for the tasks of document denoising and document binarization.
-These datasets are listed in Table~\ref{tab:datasets}.
-%By now, hundreds of datasets exist for the document denoising task (several listed in \cite{tab:datasets}), 
+These datasets are listed in Table~\ref{tab:datasets}, where we pay particular attention to dataset size, diversity of documents/texts (i.e., font sizes and styles, languages, paper styles, and graphics).
 The most similar to \emph{ShabbyPages} being \emph{NoisyOffice} \cite{ref_NoisyOfficeDatabase}.
@@
 Because the majority of these documents were created with the standard US Letter dimensions, this resulted in the most common image dimension being 1275 pixels wide by 1650 pixels tall.
-
-\begin{lstlisting}[language=bash]
-  pdftoppm document_name.pdf document_name -png -r 150
-\end{lstlisting}
 

### 2023-02-11 paper/paper.tex
Updates from Overleaf

--- 2023-02-11 paper/paper.tex
@@
 \usepackage{courier}
+
+\definecolor{superlightgray}{RGB}{242,242,242}
 
@@
          %\emph{DIBCO-19} \cite{dibco-19} & & \xmark & & & & & & & n/a\\ % SL: I can't find this dataset online
-         Bickley Diary \cite{bickley-diary} & 7 & \xmark & \cmark   & \xmark & \xmark & \xmark & \xmark & n/a\\
-         PHIBD \cite{nafchi-2013-icdar} & 15 & \xmark & \cmark &   \cmark & \cmark & \xmark & \xmark & n/a\\
+         \emph{Bickley Diary} \cite{bickley-diary} & 7 & \xmark & \cmark   & \xmark & \xmark & \xmark & \xmark & n/a\\
+         \emph{PHIBD} \cite{nafchi-2013-icdar} & 15 & \xmark & \cmark &   \cmark & \cmark & \xmark & \xmark & n/a\\
          %TQBC & & & & & & & & & n/a\\ % SL: I can't find this dataset online
@@
 The 6202 images in the \emph{ShabbyPages} release set are really just the first sample from the space of these documents; we encourage readers to build their own.
-\emph{NoisyOffice} is the only other set we examined that contains its digital provenance, but the released database materials lack a means of reproducing the simulated printing method used to create the \emph{NoisyOffice} training data; \emph{Augraphy}'s \texttt{PaperFactory} augmentation is such a tool.
+\emph{NoisyOffice} and \emph{DDI-100} are the only other datasets we examined that contain its digital provenance, but the released database materials lack a means of reproducing the simulated printing method used to create the \emph{NoisyOffice} training data; \emph{Augraphy}'s \texttt{PaperFactory} augmentation is such a tool.
 The other sets are not even theoretically extensible in this way.
@@
 \subsubsection{Data Gathering.}
-A team of workers searched the public internet for PDFs of many different kinds, from culturally-important sources like government agencies, NGOs, and large multinational corporations.
+A team of crowdworkers searched the public internet for PDFs of many different kinds, from culturally-important sources like government agencies, NGOs, and large multinational corporations.
 600 unique documents were retrieved, totaling 6202 pages.
 Care was taken to retrieve freely-available and attributable documents; a manifest is included in the dataset which contains an ordered table of the filenames, the languages present in the document, the download URL for the file, and an English name or acronym for the source organization or person.
-A similar process was completed to collect paper textures on which to "print" the documents: 300 unique textures were gathered, all of which are either in the public domain or carry CC-0, CC-BY, or CC-BY-SA licenses; metadata about these textures appears in another manifest.
+A similar process was completed to collect paper textures on which to ``print'' the documents: 300 unique textures were gathered, all of which are either in the public domain or carry CC-0, CC-BY, or CC-BY-SA licenses; metadata about these textures appears in another manifest.
 We also manually reviewed the gathered documents to verify that no personal identity information was present within the corpus.
@@
 
-The pipeline uses 23/26 augmentations from \emph{Augraphy}; we excluded augmentations that would make it hard to do pixel to pixel comparisons against groundtruths.
+The pipeline uses 23 of the augmentations from \emph{Augraphy}.
+Augmentations such as \texttt{"BookBinding"} and \texttt{"Folding"} were excluded since these spatial transformations alter the document image geometry by shifting pixel placement from their original position.
+Such transforms would render images unsuitable for supervised training and analysis by many common metrics that rely on pixel-to-pixel comparisons against groundtruths.
 
-PaperFactory was used with 300 textures, dramatically increasing the possible variations in the final dataset.
-We did not use Brightness or BrightnessTexturize, because these can interact poorly with some of the paper textures we chose.
-We also omitted the BookBinding augmentation, which can alter the document image geometry by adding additional pixels, making the result unsuitable for analysis by many common metrics.
+\texttt{"PaperFactory"} was used with 300 textures, dramatically increasing the possible variations in the final dataset.
 
@@
 In keeping with the spirit of \emph{NoisyOffice}, our original inspiration, and to provide out-of-distribution test data for ours and other projects, we developed a separate but related dataset which we call \emph{ShabbyReal}.
-To build this, we isolated reproduction steps for several physical operations, designed real-world augmentation pipelines with these, and then engaged a team of workers to use these instructions to produce several copies of printed born-digital documents with real noise.
+To build this, we isolated reproduction steps for several physical operations, designed real-world augmentation pipelines with these, and then engaged a team of crowdworkers to use these instructions to produce several copies of printed born-digital documents with real noise.
 
@@
     \scalebox{0.9}{
-    \begin{tabular}{lll}
+    \begin{tabular}{llll}
     \toprule
-    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~}\\
+    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{Model} & \textbf{SSIM$\uparrow$~}\\
         \midrule
-        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & \textbf{0.96}\\
-        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.83\\
+        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & NAFNet & \textbf{0.96}\\
+        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & NAFNet & 0.83\\
         \bottomrule
@@
     \scalebox{0.9}{
-    \begin{tabular}{lllll}
+    \begin{tabular}{llllll}
     \toprule
-    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{PSNR$\uparrow$~} & \textbf{RMSE$\downarrow$~}\\
+    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{Model} & \textbf{SSIM$\uparrow$~} & \textbf{PSNR$\uparrow$~} & \textbf{RMSE$\downarrow$~}\\
         \midrule
-        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & \textbf{0.947} & \textbf{38.098} & \textbf{3.205}\\
-        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811 & 34.562 & 5.384\\
+        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & NAFNet & \textbf{0.947} & \textbf{38.098} & \textbf{3.205}\\
+        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & NAFNet & 0.811 & 34.562 & 5.384\\
         \bottomrule

### 2023-02-11 paper/paper.tex

@@
 
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
 \definecolor{superlightgray}{RGB}{242,242,242}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=false,
+    breaklines=true,
+    captionpos=b,
+    keepspaces=true,
+    numbers=left,
+    numbersep=5pt,
+    showspaces=false,
+    showstringspaces=false,
+    showtabs=false,
+    tabsize=2
+}
+\lstset{style=mystyle}
 

### 2023-02-11 paper/paper.tex
Updates from Overleaf

@@
 
-We can also measure the "diversity" of our dataset as a way to compare the richness of various features against an alternative like \emph{NoisyOffice}.
+We can also measure the ``diversity'' of our dataset as a way to compare the richness of various features against an alternative like \emph{NoisyOffice}.
 To do this, we use a diversity metric \cite{larson-etal-2019-outlier} defined as
@@
 \emph{ShabbyPages} was born out of a desire to address shortcomings in the popular datasets discussed in the previous section.
-Reproducibility was a primary concern, so \emph{ShabbyPages} includes not only the groundtruth images, but also the original digital documents used to produce them, and the software for fully recreating the set, allowing anyone to quickly produce a new member of the Shabby family, optionally re-exporting groundtruths at a different resolution beforehand.
+Reproducibility was a primary concern, so \emph{ShabbyPages} includes not only the groundtruth images, but also the original digital documents used to produce them, and the software for fully recreating the set, allowing anyone to quickly produce a new member of the \emph{Shabby} family, optionally re-exporting groundtruths at a different resolution beforehand.
 The 6202 images in the \emph{ShabbyPages} release set are really just the first sample from the space of these documents; we encourage readers to build their own.
@@
     \includegraphics[width=1.0\textwidth]{figures/matrix_tall1.png}
-    \caption{Sample noisy patches from ShabbyPages.}
+    \caption{Sample noisy patches from \emph{ShabbyPages}.}
     \label{fig:matrix_tall1}
@@
 A team of crowdworkers searched the public internet for PDFs of many different kinds, from culturally-important sources like government agencies, NGOs, and large multinational corporations.
-600 unique documents were retrieved, totaling 6202 pages.
+A set of 600 unique documents were retrieved, totaling 6202 pages.
 Care was taken to retrieve freely-available and attributable documents; a manifest is included in the dataset which contains an ordered table of the filenames, the languages present in the document, the download URL for the file, and an English name or acronym for the source organization or person.
-A similar process was completed to collect paper textures on which to ``print'' the documents: 300 unique textures were gathered, all of which are either in the public domain or carry CC-0, CC-BY, or CC-BY-SA licenses; metadata about these textures appears in another manifest.
+A similar process was completed to collect paper textures on which to ``print'' the documents: 300 unique textures were gathered, all of which are either in the public domain or carry permissive Creative Commons licenses (\texttt{CC-0}, \texttt{CC-BY}, or \texttt{CC-BY-SA}); metadata about these textures appears in another manifest.
 We also manually reviewed the gathered documents to verify that no personal identity information was present within the corpus.
@@
 \subsubsection{PDF to PNG Conversion.}
-The ~pdftoppm~ tool from the ~poppler-utils~ package was used to split the PDF documents into individual pages.
-Each page was converted to a PNG image at 150dpi, a common printing resolution.
+The \texttt{pdftoppm} tool from the \texttt{poppler-utils} package was used to split the PDF documents into individual pages.
+Each page was converted to a PNG image at 150dpi.
 Because the majority of these documents were created with the standard US Letter dimensions, this resulted in the most common image dimension being 1275 pixels wide by 1650 pixels tall.
 
-\ubsubsection{Developing the Pipeline.}
+\subsubsection{Developing the Pipeline.}
 The \emph{Augraphy} library presents an easy-to-use API for constructing data augmentation pipelines for document images, which has been designed for interoperability with other augmentation tools, and within the broader data ecosystem.
@@
     \includegraphics[width=1.0\textwidth]{figures/matrix_tall2.png}
-    \caption{Sample noisy patches from ShabbyPages.}
+    \caption{Sample noisy patches from \emph{ShabbyPages}.}
     \label{fig:matrix_tall2}
@@
 Execution time is dependent on which augmentations are executed at runtime; a long \emph{Augraphy} pipeline can take several seconds to process large images.
-The library is under active development with performance enhancements underway, but the time cost to generate large datasets sequentially is prohibitive when dealing with thousands of files, so we use a multi-process pooling technique to distribute the workload across many processor execution threads.
+The library is under active development with performance enhancements underway, but generating large datasets sequentially can be unnecessarily time consuming when dealing with thousands of files, so we use a multi-process pooling technique to distribute the workload across many processor execution threads.
 For each process, a new pipeline with new probability coefficients was generated, representing a nontrivially-different sequence of document operations.
@@
 \subsection{\emph{ShabbyReal}}
-In keeping with the spirit of \emph{NoisyOffice}, our original inspiration, and to provide out-of-distribution test data for ours and other projects, we developed a separate but related dataset which we call \emph{ShabbyReal}.
+In keeping with the spirit of \emph{NoisyOffice}, our original inspiration, and to provide out-of-distribution test data for ours and other projects, we developed a separate but related dataset which we call \emph{ShabbyReal} that contains 200 real-world clean/dirty document image pairs.
 To build this, we isolated reproduction steps for several physical operations, designed real-world augmentation pipelines with these, and then engaged a team of crowdworkers to use these instructions to produce several copies of printed born-digital documents with real noise.
@@
 Five individuals were recruited for this task, which involved printing 40 pages of documents and manually applying various effects such as folds, wrinkles, smudges, highlighters, pencils, crayons, splatters of ink or other liquids, printing, scanning, faxing and other creative and reasonable treatments determined by these workers.
-The process continued over a period of two weeks, incurring a cost of approximately \$1,000 USD.
+Post processing was also required to align scanned dirty images to their original groundtruths to make them suitable for denoising or binarization tasks, effectively doubling the product cost of the dataset.
+The process continued over a period of two weeks, incurring a cost of approximately \$2,000 USD.
 While there are plenty of opportunities to streamline the operation, scaling this process is expensive in terms of both time and money, and may have unpredictable results.
@@
 Environmental concerns like the volume of paper and ink used, and the energy expenditure both in electricity and human terms, also factored into our decision to pursue synthetic augmentations for \emph{ShabbyPages}.
-Manually producing a database of noisy documents is a time-consuming and repetitive task; creating just 100 real-world documents with real noise features required the labor of several people.
+Manually producing a database of noisy documents is a time-consuming and repetitive task; creating just 200 real-world documents with real noise features required the labor of several people.
 Nevertheless, despite the limited size of the resulting dataset, the scarcity of real-world datasets with ground truth images makes the \emph{ShabbyReal} corpus extremely valuable; its inclusion in \emph{ShabbyPages} even moreso.
@@
 Both approaches can be achieved by supervised learning of relationships between features of the input and output data.
-In this section, we train two NAFNet \cite{ref_nafnet} instances as denoisers on both the \emph{NoisyOffice} and the \emph{ShabbyPages} datasets.
+In this section, we train two NAFNet \cite{ref_nafnet} instances as denoisers on both the \mbox{\emph{NoisyOffice}} and the \mbox{\emph{ShabbyPages}} datasets.
 We evaluate these models' predictions in a cross-validation test on both datasets, both by visual inspection and by metric computation.
@@
         \midrule
-        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & NAFNet & \textbf{0.96}\\
-        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & NAFNet & 0.83\\
+        \textsf{\emph{ShabbyPages}} & \textsf{\emph{NoisyOffice-real}} & NAFNet & \textbf{0.96}\\
+        \textsf{\emph{NoisyOffice-sim}} & \textsf{\emph{ShabbyPages}} & NAFNet & 0.83\\
         \bottomrule
@@
 
-One instance of the model was trained on the full SimulatedNoisyOffice corpus, while the other was trained on a 1050-image subset of \emph{ShabbyPages}, cropped to a single random 500x500 patch.
+One instance of the model was trained on the full \emph{SimulatedNoisyOffice} corpus, while the other was trained on a 1050-image subset of \emph{ShabbyPages}, cropped to a single random 500x500 patch.
 In both cases, the prediction target was the relevant ensemble-binarized groundtruths, and each instance trained for 100 epochs.
-As a test, these models were used to denoise and binarize both the full NoisyOfficeReal dataset and a 450-image testing subset taken from \emph{ShabbyPages} which does not overlap the training subset.
+As a test, these models were used to denoise and binarize both the full \emph{NoisyOfficeReal} dataset and a 450-image testing subset taken from \emph{ShabbyPages} which does not overlap the training subset.
 
@@
 In addition to the structural similarity metric from the denoising task, we add the peak signal to noise ratio (PSNR) and the root mean squared error (RMSE).
-Both of these metrics are more useful for determining the differences between binary images: together, they give some idea of the degree to which noise artifacts remain in the image after denoizing and binarization affect the visual signal, and how many such artifacts exist.
+Both of these metrics are more useful for determining the differences between binary images: together, they give some idea of the degree to which noise artifacts remain in the image after denoising and binarization affect the visual signal, and how many such artifacts exist.
 The averages of each metric over all predictions was taken, with the results presented in Table~\ref{tab:binarization_results}.
@@
         \midrule
-        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & NAFNet & \textbf{0.947} & \textbf{38.098} & \textbf{3.205}\\
-        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & NAFNet & 0.811 & 34.562 & 5.384\\
+        \textsf{\emph{ShabbyPages}} & \textsf{\emph{NoisyOffice-real}} & NAFNet & \textbf{0.947} & \textbf{38.098} & \textbf{3.205}\\
+        \textsf{\emph{NoisyOffice-sim}} & \textsf{\emph{ShabbyPages}} & NAFNet & 0.811 & 34.562 & 5.384\\
         \bottomrule

### 2023-02-11 paper/paper.tex

@@
 Others, like the Bickley Diary set \cite{bickley-diary} and the 2019 Time-Quality Binarization Competition set \cite{2019-time-quality-competition} have also been used for benchmarking document binarization approaches, but these do not appear to be publicly available \cite{tensmeyer-binarization-review-2020}.
-Ultimately, the sizes of these document binarization corpora severly limit the types of algorithms and models that can be used.
+Ultimately, the sizes of these document binarization corpora severely limit the types of algorithms and models that can be used.
 Examples of noisy-clean image pairs from some of these collections are displayed in Figure~\ref{fig:other-dataset-examples}.
@@
 
-Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean ground-truth document images to train or evaluate document denoisiers and binarizers.
+Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean ground-truth document images to train or evaluate document denoisers and binarizers.
 

### 2023-02-11 paper/paper.tex
Updated spellings

@@
             & \rot{80}{\textbf{Synthetic Noise}}
-            & \rot{80}{\textbf{Ground-Truths}}
+            & \rot{80}{\textbf{Groundtruths}}
             %& \rot{80}{\textbf{Diversity}}
@@
     \caption{Example noisy-clean pairs from DDI-100.
-Geometric transformations are required to map the noisy samples to their corresponding clean ground-truth images, making DDI-100 unsuitable for binarization and denoising.}
+Geometric transformations are required to map the noisy samples to their corresponding clean groundtruth images, making DDI-100 unsuitable for binarization and denoising.}
     \label{fig:ddi-100-samples}
@@
 
-Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean ground-truth document images to train or evaluate document denoisers and binarizers.
+Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean groundtruth document images to train or evaluate document denoisers and binarizers.
 
@@
 To address this, we broke all of the parameters for every augmentation constructor out into separate variables, tweaking these and committing the new pipeline to GitHub.
-We created an automated daily build in GitHub Actions to render a random selection of ground-truth images with the updated pipeline, then our team met frequently to discuss the output and make adjustments to the augmentation parameters, until we were consistently satisfied with the results.
+We created an automated daily build in GitHub Actions to render a random selection of groundtruth images with the updated pipeline, then our team met frequently to discuss the output and make adjustments to the augmentation parameters, until we were consistently satisfied with the results.
 
@@
 Manually producing a database of noisy documents is a time-consuming and repetitive task; creating just 200 real-world documents with real noise features required the labor of several people.
-Nevertheless, despite the limited size of the resulting dataset, the scarcity of real-world datasets with ground truth images makes the \emph{ShabbyReal} corpus extremely valuable; its inclusion in \emph{ShabbyPages} even moreso.
+Nevertheless, despite the limited size of the resulting dataset, the scarcity of real-world datasets with ground truth images makes the \emph{ShabbyReal} corpus extremely valuable; its inclusion in \emph{ShabbyPages} even more so.
 This type of dataset is critical for benchmark comparison with synthetically-augmented document images, and for other tasks such as denoising and binarizing: we use \emph{ShabbyReal} later for a human-perception evaluation of denoising performance.
@@
 We evaluate these models' predictions in a cross-validation test on both datasets, both by visual inspection and by metric computation.
-We then perform a similar experiment where the same NAFNets are trained to not only remove noise from the test images, but also to classify the foreground and backgorund pixels, predicting a binarized clean document.
+We then perform a similar experiment where the same NAFNets are trained to not only remove noise from the test images, but also to classify the foreground and background pixels, predicting a binarized clean document.
 The model was ``off-the-shelf''; besides rigging up the training inputs and choosing a reasonable training epoch limit, we made no significant alterations to the provided hyperparameters.
@@
 Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it.
-Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, and perhaps most importantly, when our aesthetic sensibilities are un-challenged.
+Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, and perhaps most importantly, when our aesthetic sensibilities are unchallenged.
 

### 2023-02-11 paper/paper.tex
add missing citations

@@
 Denoising is a fundamental concern for many document processing workflows, wherein unwanted artifacts introduced to a document image via noisy processes like scanning are removed.
-The effectiveness of the denoising stage of document processing pipelines has implications for downstream tasks like optical character recognition (OCR) and layout parsing [need to cite].
-Recent work in supervised machine learning has yielded promising results at the denoising task [need to cite], increasing the importance of access to large volumes of high-quality training and evaluation data.
+The effectiveness of the denoising stage of document processing pipelines has implications for downstream tasks like optical character recognition (OCR) and layout parsing \cite{Mustafa_2018-wan,blind-denoising-iccv-2021,patch-based-document-denoising,character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
+Recent work in supervised machine learning has yielded promising results at the denoising task \cite{tensmeyer-cnn-binarization-2017,blind-denoising-iccv-2021}, increasing the importance of access to large volumes of high-quality training and evaluation data.
 
@@
 
-Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean groundtruth document images to train or evaluate document denoisers and binarizers.
+Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 \cite{tobacco-3482}, Tobacco-800 \cite{ref_Tobacco800}, and FUNSD \cite{jaume2019-funsd} --- include large amounts of real noise, but none of these have corresponding clean groundtruth document images to train or evaluate document denoisers and binarizers.
 

### 2023-02-11 paper/paper.tex
Minor edits

@@
 \centering
-\includegraphics[width=0.98\columnwidth, frame]{figures/quad.png}
-\caption{Sample patches from \emph{ShabbyPages}.} \label{fig1}
+\includegraphics[width=0.98\columnwidth]{figures/what_causes_corruption.png}
+\caption{Sample clean and corresponding dirty patch from \emph{ShabbyPages}.} \label{fig1}
 \end{figure}
@@
 The pipeline uses 23 of the augmentations from \emph{Augraphy}.
-Augmentations such as \texttt{"BookBinding"} and \texttt{"Folding"} were excluded since these spatial transformations alter the document image geometry by shifting pixel placement from their original position.
+Augmentations such as \texttt{BookBinding} and \texttt{Folding} were excluded since these spatial transformations alter the document image geometry by shifting pixel placement from their original position.
 Such transforms would render images unsuitable for supervised training and analysis by many common metrics that rely on pixel-to-pixel comparisons against groundtruths.
 
-\texttt{"PaperFactory"} was used with 300 textures, dramatically increasing the possible variations in the final dataset.
+\texttt{PaperFactory} was used with 300 textures, dramatically increasing the possible variations in the final dataset.
 
@@
 \centering
-\includegraphics[width=0.98\columnwidth, frame]{figures/shabbyreal_denoising.png}
-\caption{Sample \emph{ShabbyReal} images and their Shabby\_NAFNet-denoised versions.}
+\includegraphics[width=0.98\columnwidth]{figures/quad.png}
+\caption{Sample patches from \emph{ShabbyPages} dataset.}
 \label{fig:shabbyreal_denoising}
